\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Ted Lasso\\\Large S01E04: For the Children}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:00:06]{You're hearing AFC Richmond being booed lustily by their home fans.}{你会听到主场球迷对AFC里士满 不间断的嘘声}{
    \Word{boo}{v.}{发出嘘声}
    \Word{lustily}{adv.}{强烈地}
}
\SentenceBlock[0:01:18]{Gaffer saved you, old man.}{教练救了你 老家伙}{
    \Word{gaffer}{n.}{教练（英式俚语）}
}
\SentenceBlock[0:02:30]{You think these fellas,}{你觉得这些家伙}{
    \Word{fella}{n.}{家伙}
}
\SentenceBlock[0:02:31]{could solve their problems with a dance-off at a gymnasium?}{在体育馆跳跳舞就能化解矛盾了吗}{
    \Word{gymnasium}{n.}{体育馆}
}
\SentenceBlock[0:02:36]{Riff and Bernardo ended up getting knifed to death at that particular event.}{里弗和贝纳多当场被刺身亡}{
    \Word{knife}{v.}{用刀刺}
}
\SentenceBlock[0:02:40]{No, they didn't die until the rumble afterwards.}{不是 他们是在后面打架时死的}{
    \Word{rumble}{n.}{斗殴}
}
\SentenceBlock[0:03:02]{Busted.}{败露了}{
    \Word{busted}{adj.}{被揭穿的}
}
\SentenceBlock[0:03:45]{before you tell me a folksy anecdote about you and pajamas.}{不然你就要跟我讲你和睡衣的土味趣闻了}{
    \Word{folksy}{adj.}{亲切的}
    \Word{anecdote}{n.}{轶事}
}
\SentenceBlock[0:03:49]{'cause this one is a doozy.}{因为这是个好故事}{
    \Word{doozy}{n.}{特别出色的事物}
}
\SentenceBlock[0:03:58]{Great! 'Cause I got some fences I need to mend, and I think that might do the trick.}{好极了因为我得让俩人冰释前嫌 我觉得应该可以}{
    \Word{mend}{v.}{修补}
}
\SentenceBlock[0:04:11]{If I didn't have any confidence, I never would've worn pajamas to my prom}{如果我不自信 我是绝不会 穿睡衣参加毕业舞会的}{
    \Word{prom}{n.}{毕业舞会}
}
\SentenceBlock[0:04:19]{You're probably all revved up because of the big shindig, right?}{你肯定为这次盛大的舞会 感到紧张吧 对吗}{
    \Word{revved}{adj.}{兴奋的}
    \Word{shindig}{n.}{盛会}
}
\SentenceBlock[0:04:29]{I'm actually, really, feeling quite mellow.}{其实 我现在情绪很平稳}{
    \Word{mellow}{adj.}{平和的}
}
\SentenceBlock[0:05:18]{It's just not me. There's no hood, no zips.}{这不是我的风格 没有兜帽 没有拉链}{
    \Word{hood}{n.}{帽兜}
}
\SentenceBlock[0:05:21]{There's no graffiti.}{没有涂鸦}{
    \Word{graffiti}{n.}{涂鸦}
}
\SentenceBlock[0:05:29]{Not with trousers that tight around the crotch, you don't.}{裤裆那么紧 才不像呢}{
    \Word{crotch}{n.}{胯部}
}
\SentenceBlock[0:05:57]{-Are you? -Yeah, I'm like a progeny.}{-是吗 -对 时尚血统}{
    \Word{progeny}{n.}{后代}
}
\SentenceBlock[0:06:37]{Gotta love a troubadour.}{我喜欢吟游诗人}{
    \Word{troubadour}{n.}{吟游诗人}
}
\SentenceBlock[0:06:41]{Holy moly, look at you.}{我的妈呀 看看你}{
    \Word{moly}{int.}{天哪}
}
\SentenceBlock[0:08:10]{It's the most flattering.}{这是最上相的姿势}{
    \Word{flattering}{adj.}{使人显得更漂亮的}
}
\SentenceBlock[0:08:34]{Don't strut. Let the suit do the work.}{别扭来扭去的 大方展示你的西装}{
    \Word{strut}{v.}{昂首阔步}
}
\SentenceBlock[0:08:45]{I had a hunch you were gonna pick this dress.}{我当时就有预感你会选这件}{
    \Word{hunch}{n.}{预感}
}
\SentenceBlock[0:08:50]{Check out Nate. Looking pretty dapper himself, huh?}{看看内特 挺帅的吧}{
    \Word{dapper}{adj.}{整洁帅气的}
}
\SentenceBlock[0:09:03]{That's his new gal, Jane.}{那是他的新欢 简}{
    \Word{gal}{n.}{女孩}
}
\SentenceBlock[0:09:38]{Now, listen. You two knuckleheads have split our locker room in half.}{听着 你们两个傻小子让更衣室分成两派}{
    \Word{knucklehead}{n.}{笨蛋}
}
\SentenceBlock[0:10:16]{Nate, that's a very nice suit. I think you look chic.}{内特 你的西服很好看 我觉得你很帅}{
    \Word{chic}{adj.}{时髦的}
}

\SentenceBlock[0:11:47]{Queen to rook four.}{后走车四}{
    \Word{rook}{n.}{车（国际象棋）}
}
\SentenceBlock[0:11:57]{Knight to king five.}{骑士走王五}{
    \Word{knight}{n.}{马（国际象棋）}
}
\SentenceBlock[0:12:21]{Now, I do hope you've all brought your checkbooks with you for our auction later.}{稍候是我们的竞拍环节 我希望大家都把支票本带在了身上}{
    \Word{checkbook}{n.}{支票簿}
}
\SentenceBlock[0:13:57]{He fucking headbutted me. I'm still dizzy half the time.}{他居然撞了我的头 我有一半时间都是晕着的}{
    \Word{headbutt}{v.}{用头撞}
    \Word{dizzy}{adj.}{头晕的}
}
\SentenceBlock[0:14:10]{Shut up, it's not funny. Burned my nipple.}{闭嘴 一点都不好笑 烫到了我的乳头}{
    \Word{nipple}{n.}{乳头}
}
\SentenceBlock[0:14:55]{Just the usual. Jamie being a little bitch prima donna.}{一如往常 杰米那个戏精又作天作地了}{
    \Word{prima donna}{n.}{主角；爱出风头的人}
}
\SentenceBlock[0:15:36]{Well, my initial plan was to hug you, but I just chickened out just now.}{我一开始的计划是拥抱你 但我临阵退缩了}{
    \Word{chicken out}{v.}{临阵退缩}
}
\SentenceBlock[0:16:11]{If you're ever in Kansas City and come across a fella named Tom Dineen,}{如果你去了堪萨斯城 遇到一个叫汤姆迪宁的人}{
    \Word{fella}{n.}{小伙子}
}
\SentenceBlock[0:17:42]{I'll go track her down and run it up the flagpole, huh?}{我去找她 先把旗子升起来 好吗}{
    \Word{flagpole}{n.}{旗杆}
}
\SentenceBlock[0:18:03]{I have been cajoled into being your auctioneer for this evening.}{我禁不住哄骗 成了今晚的拍卖人}{
    \Word{cajole}{v.}{哄骗}
    \Word{auctioneer}{n.}{拍卖人}
}
\SentenceBlock[0:18:25]{Look at him, folks. Young, gorgeous, charming. The bastard.}{看看他 各位 年轻帅气、魅力四射 真是个混蛋}{
    \Word{bastard}{n.}{混蛋}
}
\SentenceBlock[0:18:37]{Richmond's premier breeder of Shetland ponies.}{里士满设得兰矮种马的养殖大户}{
    \Word{breeder}{n.}{饲养者}
    \Word{pony}{n.}{小马}
}
\SentenceBlock[0:18:53]{Stunning.}{漂亮}{
    \Word{stunning}{adj.}{令人惊艳的}
}
\SentenceBlock[0:18:54]{And that applies to the bid and the bidder.}{不论是竞价还是竞价人}{
    \Word{bidder}{n.}{出价人}
}
\SentenceBlock[0:19:33]{Yeah. Those rickshaw bike things are so silly, but they do look like fun.}{对 那些人力车真蠢 但看上去还挺有趣的}{
    \Word{rickshaw}{n.}{人力车}
}
\SentenceBlock[0:19:40]{My wife and I once rented one of those tandem bikes on vacation a while back.}{很久之前 我和我妻子度假的时候 租过那种自行车}{
    \Word{tandem}{n.}{双人自行车}
}
\SentenceBlock[0:19:48]{Well, I chipped a tooth, and I bruised my perineum.}{我嗑到了牙 还伤到了会阴处}{
    \Word{bruise}{v.}{擦伤}
    \Word{perineum}{n.}{会阴}
}
\SentenceBlock[0:20:00]{I used to think his blunt honesty was noble rather than what it really is.}{我之前觉得即使他做了那些事 但他的坦诚算是高尚}{
    \Word{blunt}{adj.}{直率的}
}
\SentenceBlock[0:20:52]{You wanna hop on this thing and get the heck outta Dodge? Come on.}{你想坐上去离开这里吗来吧}{
    \Word{Dodge}{n.}{道奇城（俚指逃离现场）}
}
\SentenceBlock[0:21:21]{I need to freshen up.}{我得缓一缓}{
    \Word{freshen up}{v.}{恢复精神}
}
\SentenceBlock[0:21:44]{there was this old geezer at the club, Doug Stashwick.}{俱乐部有个老家伙叫道格拉斯斯塔谢维克}{
    \Word{geezer}{n.}{老家伙}
}

\SentenceBlock[0:21:52]{It was the same shit Yankee Doodle was peddling.}{就是美国佬教练那一套}{
    \Word{Doodle}{n.}{涂鸦（此处指代“Yankee Doodle”歌曲人物，代指美国人）}
    \Word{peddle}{v.}{兜售}
}
\SentenceBlock[0:22:02]{-You're a nasty bastard-- -No, I'm going first.}{-你是个可恶的混蛋… -不 我先来}{
    \Word{bastard}{n.}{混蛋}
}
\SentenceBlock[0:22:11]{Every time I do, it makes me want to fucking puke.}{每次我传给你 都让我他妈想吐}{
    \Word{puke}{v.}{呕吐}
}
\SentenceBlock[0:22:28]{and just because you won a few trophies,}{你赢了几个奖杯}{
    \Word{trophy}{n.}{奖杯}
}
\SentenceBlock[0:23:01]{You and that Doug bloke, you ever become friends?}{你和那个叫道格的 你们最后成了朋友吗}{
    \Word{bloke}{n.}{家伙}
}
\SentenceBlock[0:24:34]{Cheeky little prick.}{那个不要脸的小王八蛋}{
    \Word{cheeky}{adj.}{厚脸皮的}
    \Word{prick}{n.}{蠢货}
}
\SentenceBlock[0:24:46]{I think the little, like, orange clitoris thing is really freaky.}{我觉得这个橘黄色的阴蒂一样的东西 真的很诡异}{
    \Word{clitoris}{n.}{阴蒂}
    \Word{freaky}{adj.}{怪异的}
}
\SentenceBlock[0:24:58]{I shouldn't laugh. It sounds... judgy.}{我不该笑的 听上去…有评判的嫌疑}{
    \Word{judgy}{adj.}{爱评头论足的}
}
\SentenceBlock[0:26:01]{Relax, babe. It's all part of the branding plan, innit?}{别激动 宝贝 这都是品牌计划的一部分 不是吗}{
    \Word{innit}{adv.}{不是吗（英俚，isn't it的缩写）}
}
\SentenceBlock[0:26:21]{And the highest bidder gets to spend a day at a swanky hotel by the pool,}{出价最高者将有机会在豪华酒店度过一天}{
    \Word{swanky}{adj.}{豪华的}
}
\SentenceBlock[0:26:26]{drinking frozen daiquiris and soaking up the rays--}{在泳池边喝冰冻黛可丽 晒着日光浴…}{
    \Word{daiquiri}{n.}{黛可丽（鸡尾酒）}
}
\SentenceBlock[0:26:40]{You think jealousy is cool, do you?}{你觉得嫉妒有意思 是吗}{
    \Word{jealousy}{n.}{嫉妒}
}
\SentenceBlock[0:26:43]{Well, can we have 100 quid for what's turning out to be a very boring date?}{有人出价一百英镑竞拍这个 突然间变得很无趣的约会吗}{
    \Word{quid}{n.}{英镑（口语）}
}
\SentenceBlock[0:28:54]{Bollocks.}{特么的}{
    \Word{bollocks}{n.}{胡说；狗屁}
}
\SentenceBlock[0:29:36]{And her wrath has begun.}{她大发雷霆}{
    \Word{wrath}{n.}{愤怒}
}
\SentenceBlock[0:30:45]{What a charmer, huh?}{真是个万人迷啊 是吧}{
    \Word{charmer}{n.}{迷人的人}
}
\SentenceBlock[0:31:34]{Don't use me as a prop in your little fights.}{你们两口子吵架别拿我当道具}{
    \Word{prop}{n.}{道具}
}
\SentenceBlock[0:32:51]{-Put the game before the dame, huh? -Yup.}{-更在乎输赢而不是对方 -对}{
    \Word{dame}{n.}{女士（此处贬义，指女人）}
}


\end{document}