\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Ted Lasso\\\Large S01E06: Two Aces}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:00:45]{Ended up getting lost but, you know, then I got unlost,}{最后我迷路了 但是之后 我又迷路了}{
    \Word{unlost}{adj.}{不再迷路的}
}
\SentenceBlock[0:01:09]{It's just got a negative connotation to it, don't it?}{听上去就不是很吉利 对吧?}{
    \Word{connotation}{n.}{含义；内涵意义}
}
\SentenceBlock[0:01:17]{So that's what I'll say. I'll say, ``I'm gonna bathe myself in work.''}{我就用这个词好了 我要说 “我要把自己泡在工作里”}{
    \Word{bathe}{v.}{洗澡；沉浸}
}
\SentenceBlock[0:01:24]{No, I just don't really enjoy baths, just 'cause my skin gets really wrinkly,}{没有 我不是很喜欢泡澡 因为皮肤会泡得皱皱的}{
    \Word{wrinkly}{adj.}{起皱的；有皱纹的}
}
\SentenceBlock[0:02:29]{Well, Sarah, I believe you can outscore your opponent and still lose.}{萨拉 我相信有时即使比分赢过对手 但依然是输家}{
    \Word{outscore}{v.}{比分超过}
}
\SentenceBlock[0:02:34]{But last week we definitely won, which is pretty darn fun.}{但上周我们确实赢了 非常令人开心}{
    \Word{darn}{adv.}{非常；极其}
}
\SentenceBlock[0:02:50]{You make an arse outta you and me. Yeah?}{你把咱俩都变成了傻子}{
    \Word{arse}{n.}{蠢人；屁股}
}
\SentenceBlock[0:02:56]{of how our English and y'all's English sometimes do not jive, innit?}{我们的英语和你们的英语 有时候并不兼容 对吗?}{
    \Word{jive}{v.}{一致；配合}
}
\SentenceBlock[0:03:17]{-Thank you. -I mean, a masterstroke.}{-谢谢 -这是一招妙棋}{
    \Word{masterstroke}{n.}{妙举；高招}
}
\SentenceBlock[0:04:02]{Flan? That dessert?}{果酱馅饼?那道甜品吗?}{
    \Word{Flan}{n.}{果酱馅饼；蛋奶冻}
}
\SentenceBlock[0:04:14]{-Semantic satiation. -Yeah.}{-语义饱和 -对}{
    \Word{satiation}{n.}{饱和；满足}
}
\SentenceBlock[0:05:47]{You're just shoving that all aside.}{你把这些都抛在脑后了}{
    \Word{shoving}{v.}{推开；乱塞}
}
\SentenceBlock[0:06:21]{set up the cones so the other reserves can do a little passing drill.}{把锥形道具放好 这样其他人还能做一些传球练习}{
    \Word{drill}{n.}{训练；练习}
}
\SentenceBlock[0:07:01]{This is a no schadenfreude zone, all right?}{不要幸灾乐祸 好吗?}{
    \Word{schadenfreude}{n.}{幸灾乐祸}
}
\SentenceBlock[0:07:02]{-Nein schadenfreude. -All right.}{-不准幸灾乐祸 -好的}{
    \Word{Nein}{interj.}{不（德语）}
    \Word{schadenfreude}{n.}{幸灾乐祸}
}
\SentenceBlock[0:07:42]{-Thank you for the opportunity. -Yeah. You are a spirited fella, Dani.}{-感谢你们给我这个机会 -你是一个很有活力的年轻人 丹尼}{
    \Word{spirited}{adj.}{有精神的；活力充沛的}
}
\SentenceBlock[0:07:45]{Just go on out there, and get the striker spot for us, okay?}{你去场上踢前锋看看 好吗?}{
    \Word{striker}{n.}{前锋}
}
\SentenceBlock[0:08:03]{Chipper dickheads like that can never back it up on the pitch.}{那种笨蛋一上场准露馅}{
    \Word{Chipper}{adj.}{活泼的；快活的}
}
\SentenceBlock[0:08:45]{And some unemployed gaffers are asking if we'll have an opening soon.}{一些待业的教练问我们近期有没有空缺}{
    \Word{gaffers}{n.}{主教练；老头（口语）}
}
\SentenceBlock[0:09:48]{Okay, well. That hideous cow, whose name's Bex,}{好吧 那个丑八怪 她叫贝克丝}{
    \Word{hideous}{adj.}{丑陋的；可怕的}
}
\SentenceBlock[0:12:20]{-I hope it's not contagious. -Aces.}{-希望别传染给别人 -王牌}{
    \Word{contagious}{adj.}{传染性的}
}
\SentenceBlock[0:12:28]{Okay, what if we cloned the lead guitarist from Kiss?}{好吧 如果我们克隆了KISS乐队 的主音吉他手会怎样?}{
    \Word{guitarist}{n.}{吉他手}
}
\SentenceBlock[0:13:21]{How do you know all this anyway? What are you doing now? Stalking me?}{你怎么知道这些事的? 你这是在干吗?跟踪我吗?}{
    \Word{Stalking}{v.}{跟踪；潜行接近}
}
\SentenceBlock[0:13:33]{You wear a number, trot around while people clap,}{你有属于自己的号码 人们鼓掌时你绕着场地走}{
    \Word{trot}{v.}{小跑；慢跑}, \Word{clap}{v.}{鼓掌}
}
\SentenceBlock[0:13:37]{so I wouldn't be too high and mighty about it.}{所以也不是很离谱}{
    \Word{mighty}{adj.}{强大的；伟大的}
}
\SentenceBlock[0:14:35]{I'm gonna have one of my son's classic temper tantrums.}{我就要像我儿子那样发脾气了}{
    \Word{tantrums}{n.}{发脾气；大发脾气}
}
\SentenceBlock[0:15:19]{like a joyous raven-haired golden retriever.}{像一只欢快的、皮毛发亮的金毛猎犬}{
    \Word{joyous}{adj.}{快乐的；高兴的}, \Word{retriever}{n.}{猎犬；寻回犬}
}
\SentenceBlock[0:16:25]{Chicago Cubs, over.}{芝加哥小熊队 结束了}{
    \Word{Cubs}{n.}{小熊队（美国职业棒球队）}
}
\SentenceBlock[0:16:43]{-Cape Fear. -Silence!}{-《恐怖角》 -安静!}{
    \Word{Cape}{n.}{海角；斗篷}
}
\SentenceBlock[0:17:02]{That's solid alliteration right there.}{这个头韵押得好}{
    \Word{alliteration}{n.}{头韵}
}
\SentenceBlock[0:17:21]{In 1914, the war was raging. There was no tryout.}{1914年 战争肆虐 根本就没有选拔赛}{
    \Word{tryout}{n.}{选拔；试镜}
}
\SentenceBlock[0:17:26]{Just recruiters, waiting to encourage those boys to fight the fight.}{只有征兵人员 等着鼓励男孩们参战}{
    \Word{recruiters}{n.}{征兵者；招聘人员}
}
\SentenceBlock[0:17:32]{They enlisted 400 lads that day.}{他们那天征召了四百人}{
    \Word{enlisted}{v.}{征募；应募入伍}
}
\SentenceBlock[0:19:02]{I've had three glasses of wine. It's Pavlovian.}{我已经喝了三杯酒 这是巴甫洛夫条件反射}{
    \Word{Pavlovian}{adj.}{巴甫洛夫式的；条件反射的}
}
\SentenceBlock[0:19:12]{No. You don't remember how many times we shagged in this thing?}{不行 你不记得我们车震过多少次了?}{
    \Word{shagged}{v.}{性交；疲惫不堪}
}
\SentenceBlock[0:19:24]{He's really gotten up your bum, hasn't he?}{他真的让你很头疼 是吧?}{
    \Word{bum}{n.}{屁股；游民}
}
\SentenceBlock[0:20:38]{Sam, I am very flattered, but--}{山姆 你的心意我了解 但是...}{
    \Word{flattered}{v.}{感到荣幸；受宠若惊}
}
\SentenceBlock[0:24:27]{This is my cat's collar. She was a faithful companion for 20 years.}{这是我家猫的项圈 它忠诚地陪伴了我20年}{
    \Word{collar}{n.}{项圈}, \Word{faithful}{adj.}{忠诚的}
}
\SentenceBlock[0:26:03]{So, I made a vow to be so tough that he could never call me ``soft'' again.}{所以 我发誓我一定要变得很强 让他再也没法叫我“软蛋”}{
    \Word{vow}{n.}{誓言}
}
\SentenceBlock[0:27:23]{I brought a bottle of mezcal to throw into the curse fire.}{我带了一瓶麦斯卡尔酒丢进诅咒之火}{
    \Word{mezcal}{n.}{麦斯卡尔酒（一种墨西哥烈酒）}
}
\SentenceBlock[0:27:52]{I just never had you pegged as a gambler, Ted.}{我从来不认为你是个赌徒 泰德}{
    \Word{pegged}{v.}{认为；限定}
}
\SentenceBlock[0:29:26]{Interception. Easy, gentlemen, easy.}{拦截 轻点 先生们}{
    \Word{Interception}{n.}{拦截}
}
\SentenceBlock[0:30:13]{But dang it, they're the best batch yet. I finally cracked the recipe!}{但是该死的 他们是我带过的最好的球员 我原本已经搞定了!}{
    \Word{dang}{interj.}{该死的；讨厌的}
}


\end{document}