\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Ted Lasso\\\Large S01E05: Tan Lines}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:00:52]{but Michelle and I, we've been having some marital issues.}{但是米歇尔和我 我们的婚姻出了点问题}{
    \Word{marital}{adj.}{婚姻的}
}
\SentenceBlock[0:01:22]{or... what-- ``Surrey with the Fringe on Top,'' or--}{或是…《带花边顶蓬的四轮马车》 或是…}{
    \Word{Surrey}{n.}{四轮马车}
    \Word{fringe}{n.}{穗状物；边缘}
}
\SentenceBlock[0:05:22]{Not a surprise. We've lost four matches in a row, and we're facing relegation.}{我并不意外 我们已经连续输了四场比赛 现在面临降级}{
    \Word{relegation}{n.}{降级}
}
\SentenceBlock[0:05:27]{I think it's all going rather smashingly.}{这不是进展地很顺利嘛}{
    \Word{smashingly}{adv.}{极好地}
}
\SentenceBlock[0:05:41]{Wait, wait, wait. Get my tats.}{等下 把我的纹身拍进去}{
    \Word{tat}{n.}{纹身}
}
\SentenceBlock[0:05:53]{No judgment, but are you back with that twat?}{我不做评价 你和那傻蛋和好了吗}{
    \Word{twat}{n.}{蠢货}
}
\SentenceBlock[0:06:07]{Hey, do you like mythology?}{嘿 你们喜欢神话故事吗}{
    \Word{mythology}{n.}{神话}
}
\SentenceBlock[0:06:29]{just 'cause I was nice to you in the loo the other night.}{只是因为之前那晚 我在卫生间对你的善意}{
    \Word{loo}{n.}{厕所}
}
\SentenceBlock[0:07:11]{And ``bangers'' aren't great songs,}{“香肠”不是让你跟着晃脑袋的好歌}{
    \Word{banger}{n.}{热门歌曲}
}
\SentenceBlock[0:07:13]{but they do make you feel like dancing 'cause they're so darn tasty.}{但吃一口就让你想跳舞 因为实在是太美味了}{
    \Word{darn}{adv.}{非常}
}
\SentenceBlock[0:07:16]{When you gonna win a game, you fucking wanker?}{你什么时候能赢比赛 你这该死的傻屌}{
    \Word{wanker}{n.}{蠢货}
}
\SentenceBlock[0:07:31]{Here are the darts. There's the board. Try not to hit any regulars.}{这是飞镖 那是靶子 尽量不要伤到常客}{
    \Word{dart}{n.}{飞镖}
}
\SentenceBlock[0:07:40]{-Three fish-and-chips? -Yes, please. And two pints.}{-三份炸鱼薯条 -好的 谢谢 再来两品脱啤酒}{
    \Word{pint}{n.}{品脱}
}
\SentenceBlock[0:10:47]{That right there, that's a scone, okay?}{这叫司康 好吗}{
    \Word{scone}{n.}{司康饼}
}
\SentenceBlock[0:11:49]{-I mean, you're gonna need pants, kiddo. -Yeah.}{-你得穿上裤子 孩子 -是啊}{
    \Word{kiddo}{n.}{小家伙}
}
\SentenceBlock[0:12:19]{are not too dissimilar from his views on cooking steak.}{和对煎牛排的看法没有太多不同}{
    \Word{dissimilar}{adj.}{不同的}
}
\SentenceBlock[0:12:38]{Well, my dad used to be a cartographer.}{我爸爸以前是制图员}{
    \Word{cartographer}{n.}{地图绘制者}
}
\SentenceBlock[0:13:47]{Very exciting to be invited into the inner sanctum.}{很开心能受邀加入核心集团}{
    \Word{sanctum}{n.}{密室；圣所}
}
\SentenceBlock[0:13:55]{You and the missus. Y'all been together a while, yeah?}{你和你老婆结婚很多年了吧}{
    \Word{missus}{n.}{太太}
}

\SentenceBlock[0:14:03]{one 20-year-old cat whose impending death will wreck me emotionally,}{一只20岁的猫 它要是哪天死了 我会伤心死的}{
    \Word{impending}{adj.}{即将来临的}
    \Word{wreck}{v.}{使崩溃}
}
\SentenceBlock[0:14:41]{Boy, that seems troublesome to me.}{天呐 我觉得这样很容易出麻烦}{
    \Word{troublesome}{adj.}{麻烦的}
}
\SentenceBlock[0:14:43]{You know, toddlers and, just, butt dials and--}{比如说刚学步的小孩 一屁股坐在手机上…}{
    \Word{toddler}{n.}{学步儿童}
}
\SentenceBlock[0:15:21]{Jamie, you a germophobe?}{杰米 你有细菌恐惧症吗}{
    \Word{germophobe}{n.}{有细菌恐惧症的人}
}
\SentenceBlock[0:15:29]{I gotta say, man, sometimes you remind me of my grandma with the channel hopper.}{我得说 伙计 有时候你会让我想起 我外婆和她的遥控器}{
    \Word{hopper}{n.}{遥控器（俚语）}
}
\SentenceBlock[0:15:40]{You get to keep on preaching all of your yeehaw bullshit,}{你可以继续鼓吹你那些打鸡血式的狗屁}{
    \Word{yeehaw}{interj.}{呦呼（美国西部牛仔的欢呼声）}
}
\SentenceBlock[0:15:57]{You know, I'd love to hash out some of the nuances there,}{你知道 我很想跟你掰扯清楚一些事情}{
    \Word{hash}{v.}{细谈}
    \Word{nuance}{n.}{细微差别}
}
\SentenceBlock[0:16:12]{As undeniably catchy as that tune is, I need you to cut the crap right now--}{虽然这旋律挺上头的 但现在不是胡闹的时候…}{
    \Word{undeniably}{adv.}{不可否认地}
    \Word{catchy}{adj.}{朗朗上口的}
    \Word{crap}{n.}{废话}
}
\SentenceBlock[0:16:57]{-Come on, goalie! -Link finds space.}{-快点 守门员 -林克发现了机会}{
    \Word{goalie}{n.}{守门员}
}
\SentenceBlock[0:17:00]{A stunning goal by the Canadian midfielder!}{加拿大中场球员漂亮的进球}{
    \Word{stunning}{adj.}{令人震惊的}
    \Word{midfielder}{n.}{中场球员}
}
\SentenceBlock[0:17:02]{-Fuck's sake! -I hate that poxy wanker! Fucking Lasso!}{-搞什么呢 -我讨厌那个没用的傻屌该死的拉索}{
    \Word{poxy}{adj.}{蹩脚的}
}
\SentenceBlock[0:17:06]{-Nice family though. -Damn it, Paul! Don't humanize him!}{-不过他家人不错 -该死的 保罗别帮他说话}{
    \Word{humanize}{v.}{使人性化}
}
\SentenceBlock[0:18:07]{Come on, ref! They gotta knock that off!}{拜托 裁判他们必须停止这种行为}{
    \Word{ref}{n.}{裁判}
}
\SentenceBlock[0:18:25]{The captain dispensing some wisdom to the young superstar.}{队长在教育这个年轻的超级明星}{
    \Word{dispense}{v.}{传授}
}
\SentenceBlock[0:19:05]{But everyone was making such a fuss, I thought I should just stay down.}{但所有人都大动肝火 我觉得我应该继续趴着}{
    \Word{fuss}{n.}{大惊小怪}
}
\SentenceBlock[0:19:11]{I'm gonna pull you up, you're gonna pretend to limp very badly,}{我拉你起来 你要假装瘸得很厉害}{
    \Word{limp}{v.}{瘸行}
}
\SentenceBlock[0:19:31]{Attaboy, Sam!}{好样的 山姆}{
    \Word{attaboy}{interj.}{好样的}
}
\SentenceBlock[0:19:41]{With Tartt, that's usually a rhetorical question.}{对塔特而言 这通常是一个反问句}{
    \Word{rhetorical}{adj.}{反问的}
}
\SentenceBlock[0:20:22]{That's some real impressive cardio from Ted Lasso there.}{泰德拉索的心肺功能真是令人刮目相看}{
    \Word{cardio}{n.}{有氧运动}
}
\SentenceBlock[0:20:44]{Thanks, boss. All right. Later, alligators.}{谢谢 老板 好了 一会见}{
    \Word{alligator}{n.}{鳄鱼（此处为俚语再见）}
}
\SentenceBlock[0:20:57]{Hey, highlighter. We got ourselves a sub.}{嘿 荧光男 我们要换人}{
    \Word{sub}{n.}{替补队员}
}
\SentenceBlock[0:21:40]{Shut up. Fucking stupid twat.}{闭嘴吧 该死的蠢蛋}{
    \Word{twat}{n.}{蠢货}
}
\SentenceBlock[0:21:45]{The referee looks at his watch, and that's halftime.}{裁判看了看表 上半场结束}{
    \Word{halftime}{n.}{中场休息}
}
\SentenceBlock[0:22:25]{One minute, you're playing freeze tag out there at recess with all your buddies.}{上一秒 你还在课间休息时 跟朋友们一起玩“一二三木头人”}{
    \Word{recess}{n.}{课间休息}
}
\SentenceBlock[0:22:29]{Next thing you know, you're getting zits, your voice gets low.}{下一秒 你就长了青春痘 声音变得沙哑}{
    \Word{zit}{n.}{青春痘}
}
\SentenceBlock[0:22:36]{to check and see how your project's going, you feel all squiggly inside.}{查看你的作业进度 你内心都小鹿乱撞}{
    \Word{squiggly}{adj.}{弯弯曲曲的}
}
\SentenceBlock[0:22:50]{First time I ever saw tan lines.}{那是我第一次看到晒痕}{
    \Word{tan}{n.}{晒痕}
}
\SentenceBlock[0:23:58]{Still level at two goals apiece.}{双方依然是二比二平}{
    \Word{apiece}{adv.}{每人；各自}
}
\SentenceBlock[0:24:30]{Richmond take the lead with barely a minute of stoppage time left.}{里士满领先 此时补时仅剩下不到一分钟}{
    \Word{stoppage}{n.}{补时}
}
\SentenceBlock[0:24:41]{Scorer for Richmond's third goal, number 24, Sam Obisanya.}{里士满第三个进球的球员 是24号山姆奥比桑亚}{
    \Word{scorer}{n.}{得分者}
}
\SentenceBlock[0:26:57]{You snuck up on a woman in a parking lot at night.}{你大晚上的在停车场里悄悄靠近一个女人}{
    \Word{sneak}{v.}{偷偷靠近}
}


\end{document}