\documentclass[11pt,a4paper]{article}
%% =========================================================
%% Theme options (default: Blue)
%% Usage: \usepackage[Indigo]{aiwordbook}
%% Available: Blue, Orange, Cyan, Indigo, Amber, Green, BlueGrey
%% =========================================================
\usepackage[Cyan]{aiwordbook}

\title{Slow Horses}
\subtitle{S05E05: Circus}


\date{}
\author{}

\begin{document}

\maketitle

\SentenceBlock[0:02:59]{And that he was pronounced dead at the scene by paramedics.}{急救人员宣布 该男子当场死亡}{
    \Word{paramedic}{n.}{护理人员，急救医务人员}[ˌpærəˈmedɪk]
}

\SentenceBlock[0:03:30]{Her parents fled Tripoli in the 2011 coup}{2011年政变里她的父母逃离了的黎波里}{
    \Word{flee}{v.}{逃离，逃跑}[fliː]
    \Word{coup}{n.}{政变}[kuː]
}

\SentenceBlock[0:03:51]{Usual activism for an educated woman of her age.}{其激进程度于此群体属常态}{
    \Word{activism}{n.}{激进主义，社会活动}[ˈæktɪvɪzəm]
}

\SentenceBlock[0:04:14]{What I mean to say is, I'm just glad there was no foul play.}{我想说的是 我只是庆幸没有人为的阴谋诡计}{
    \Word{foul}{adj.}{不正当的，恶意的}[faʊl]
}

\SentenceBlock[0:04:24]{Catnip for conspiracy theorists, isn't it?}{这简直是阴谋论者的兴奋剂 不是吗？}{
    \Word{catnip}{n.}{极具吸引力的事物}[ˈkætnɪp]
}

\SentenceBlock[0:05:20]{and threatened to skin you alive if you don't seduce Roddy Ho,}{威胁说如果不去勾引罗迪何 就把你活剥了皮}{
    \Word{seduce}{v.}{勾引，引诱}[sɪˈdjuːs]
}

\SentenceBlock[0:07:38]{you can always say you got stuck in a bondage club.}{自己被困在一家束缚俱乐部里了}{
    \Word{bondage}{n.}{束缚，奴役}[ˈbɒndɪdʒ]
}

\SentenceBlock[0:08:09]{I spotted some guy heading backstage who didn't need to be there,}{我看到有个家伙往后台走 他根本没必要去那里}{
    \Word{backstage}{adv.}{在后台}[ˌbækˈsteɪdʒ]
}

\SentenceBlock[0:08:11]{he smuggled in a rifle.}{还偷带了一支步枪}{
    \Word{smuggle}{v.}{走私，偷运}[ˈsmʌɡl]
}

\SentenceBlock[0:08:21]{I thought your tipple was coke, not LSD.}{我以为你喜欢白粉 而不是致幻剂}{
    \Word{tipple}{n.}{常喝的酒}[ˈtɪpl]
}

\SentenceBlock[0:09:21]{I'm okay with solitude.}{我不介意单独囚禁}{
    \Word{solitude}{n.}{独处，孤独}[ˈsɒlɪtjuːd]
}

\SentenceBlock[0:10:38]{Why did they want you to seduce Roddy?}{他们为什么要你勾引罗迪？}{
    \Word{seduce}{v.}{勾引，引诱}[sɪˈdjuːs]
}

\SentenceBlock[0:11:02]{I thought they might burgle him or bug him or threaten him.}{我以为他们会入室盗窃 窃听甚至威胁他}{
    \Word{burgle}{v.}{入室盗窃}[ˈbɜːɡl]
}

\SentenceBlock[0:11:55]{They've already combed the system and didn't detect any anomalies.}{他们已经筛查了系统 没有发现任何异常}{
    \Word{comb}{v.}{彻底搜查}[kəʊm]
    \Word{anomaly}{n.}{异常情况}[əˈnɒməli]
}

\SentenceBlock[0:12:35]{They blew up a fucking penguin enclosure.}{他们炸了一个企鹅馆}{
    \Word{enclosure}{n.}{围栏，围场}[ɪnˈkləʊʒə]
}

\SentenceBlock[0:12:48]{Name me one person who's got a grudge against penguins.}{给我举个例子 说说谁会对企鹅心怀怨恨}{
    \Word{grudge}{n.}{怨恨，积怨}[ɡrʌdʒ]
}

\SentenceBlock[0:13:19]{you have never once taken responsibility for your litany of fuck-ups.}{你从未为自己搞出的一堆烂事担过责}{
    \Word{litany}{n.}{一连串（坏事）}[ˈlɪtəni]
}

\SentenceBlock[0:13:38]{And he's got some color in his He looks positively post-coital.}{看起来就像刚做完爱似的}{
    \Word{postcoital}{adj.}{性交后的}[ˌpəʊstkəʊˈɪtl]
}

\SentenceBlock[0:13:48]{You're telling me that Gimball's swivel-eyed supporters,}{你是说 金博尔那些狂热的信徒}{
    \Word{swivel-eyed}{adj.}{狂热的，极端的}[ˈswɪvəl aɪd]
}

\SentenceBlock[0:15:39]{What, is he psychic now?}{怎么 他有通灵能力了？}{
    \Word{psychic}{adj.}{通灵的，有超感能力的}[ˈsaɪkɪk]
}

\SentenceBlock[0:15:42]{We should ascertain who these men are}{我们得弄清楚这些人是谁}{
    \Word{ascertain}{v.}{查明，弄清}[ˌæsəˈteɪn]
}

\SentenceBlock[0:16:02]{We can kill and plunder and blackmail}{我们可以杀人越货、敲诈勒索}{
    \Word{plunder}{v.}{掠夺，抢劫}[ˈplʌndə]
}

\SentenceBlock[0:16:49]{Well, someone must've groomed him, gave him a gun.}{一定是有人引导他、操控他 给了他一把枪}{
    \Word{groom}{v.}{引导，培养（用于不良目的）}[ɡruːm]
}

\SentenceBlock[0:17:02]{Jaffrey was the target, but my guys foiled it.}{贾弗里才是目标 但我的人阻止了暗杀}{
    \Word{foil}{v.}{挫败，阻止}[fɔɪl]
}

\SentenceBlock[0:17:15]{Well, the Libyans are the most likely perpetrators.}{利比亚人最有可能是凶手}{
    \Word{perpetrator}{n.}{行凶者，肇事者}[ˈpɜːpətreɪtə]
}

\SentenceBlock[0:17:23]{And judging by the books on her shelves,}{而且从她书架上的书来看}{
    \Word{shelf}{n.}{书架}[ʃelf]
}

\SentenceBlock[0:17:29]{She is Libyan, fled after the coup.}{她是利比亚人 政变后逃走的}{
    \Word{flee}{v.}{逃离}[fliː]
    \Word{coup}{n.}{政变}[kuː]
}

\SentenceBlock[0:18:34]{have long-harbored beef with Britain.}{有谁一直对英国心怀不满}{
    \Word{harbor}{v.}{心怀，怀有}[ˈhɑːbə]
}

\SentenceBlock[0:18:44]{dispersed, I mean… in a recent rationalization.}{我是说遣散 是最近的结构整合}{
    \Word{disperse}{v.}{遣散，驱散}[dɪˈspɜːs]
    \Word{rationalization}{n.}{合理化，重组}[ˌræʃnəlaɪˈzeɪʃn]
}

\SentenceBlock[0:19:42]{You know, he's sending Wells off on a wild-goose chase.}{他在让特工去做一件注定徒劳无功的事}{
    \Word{wild-goose}{adj.}{徒劳的，白费力气的}[ˈwaɪld ɡuːs]
}

\SentenceBlock[0:21:06]{Britain owed me sanctuary.}{庇护是英国欠我的}{
    \Word{sanctuary}{n.}{庇护，避难所}[ˈsæŋktʃuəri]
}

\SentenceBlock[0:21:22]{I met some activists that were looking for people to take part in some stunt}{我遇见过活动人士在招人搞事}{
    \Word{stunt}{n.}{噱头，哗众取宠的行为}[stʌnt]
}

\SentenceBlock[0:21:31]{We were going to throw red confetti in a village,}{我们本来要往一个村子里撒红色的彩纸屑}{
    \Word{confetti}{n.}{彩纸屑}[kənˈfeti]
}

\SentenceBlock[0:21:55]{Although there was a Libyan proverb they all laughed about.}{不过他们都嘲笑一个利比亚谚语}{
    \Word{proverb}{n.}{谚语}[ˈprɒvɜːb]
}

\SentenceBlock[0:22:23]{Shit's the fucking apocalypse.}{这简直是末日啊}{
    \Word{apocalypse}{n.}{世界末日，大灾难}[əˈpɒkəlɪps]
}

\SentenceBlock[0:23:08]{From the wraparound and the triple-layering,}{从封装方式和三层结构来看}{
    \Word{wraparound}{n.}{环绕式封装}[ˈræpəraʊnd]
}

\SentenceBlock[0:23:36]{You're needed. And don't gloat.}{需要你了 别得意}{
    \Word{gloat}{v.}{幸灾乐祸，得意}[ɡləʊt]
}

\SentenceBlock[0:23:40]{Look who came crawling back to papa.}{看看是谁爬回爸爸身边了}{
    \Word{crawl}{v.}{卑躬屈膝地回来}[krɔːl]
}

\SentenceBlock[0:24:32]{and that appalling business at… What's it called?}{还有那个可怕的事件 就在那地方叫什么来着？}{
    \Word{appalling}{adj.}{骇人的，令人震惊的}[əˈpɔːlɪŋ]
}

\SentenceBlock[0:24:40]{It's a memory box. Keepsakes from Ho's dates with Tara.}{是回忆盒 何和塔拉约会的纪念品}{
    \Word{keepsake}{n.}{纪念品}[ˈkiːpseɪk]
}

\SentenceBlock[0:33:19]{about our strategies hitherto.}{并未抱有太大信心}{
    \Word{hitherto}{adv.}{迄今为止}[ˌhɪðəˈtuː]
}

\SentenceBlock[0:35:14]{First sign of trouble and they will swoop.}{一旦有麻烦 他们会立刻冲上去}{
    \Word{swoop}{v.}{猛扑，突然行动}[swuːp]
}

\SentenceBlock[0:36:56]{Team one, move to perimeter.}{第一队 前往任务周边}{
    \Word{perimeter}{n.}{外围，周界}[pəˈrɪmɪtə]
}

\SentenceBlock[0:37:02]{I'm using the ``Ho-dron'' Collider to hack into your system}{我用``何子''对撞机黑入你们系统的速度}{
    \Word{collider}{n.}{对撞机}[kəˈlaɪdə]
}

\SentenceBlock[0:37:51]{He's an even creepier fucker than we imagined.}{他比我们想象中更加变态}{
    \Word{creepy}{adj.}{令人不安的，变态的}[ˈkriːpi]
}

\SentenceBlock[0:38:05]{Pretty girl handing out canapés.}{漂亮女孩在分发小点心}{
    \Word{canapé}{n.}{小点心}[ˈkænəpeɪ]
}

\SentenceBlock[0:40:27]{They might've intercepted her early. We don't wanna spook them.}{对方或已截住她 切忌打草惊蛇}{
    \Word{intercept}{v.}{拦截}[ˌɪntəˈsept]
    \Word{spook}{v.}{惊动，吓着}[spuːk]
}

\SentenceBlock[0:40:50]{Check CCTV on the concourse}{检查大厅的监控}{
    \Word{concourse}{n.}{大厅，公共通道}[ˈkɒŋkɔːs]
}


\end{document}
