\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Slow Horses\\\Large S05E02: Incommunicado}


\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:02:43]{I thought you were a burglar.}{我以为你是入室盗窃的贼。}{
    \Word{burglar}{n.}{入室盗贼}
}

\SentenceBlock[0:03:08]{For losing your virginity?}{留着庆祝失去童子身吗？}{
    \Word{virginity}{n.}{童贞}
}

\SentenceBlock[0:03:10]{It'd be vintage by then.}{到时候已经成古董酒了。}{
    \Word{vintage}{adj.}{经典的；老式的}
}

\SentenceBlock[0:03:48]{you know, due diligence and all.}{不过总得谨慎点嘛。}{
    \Word{diligence}{n.}{勤勉；尽职调查}
}

\SentenceBlock[0:04:00]{It's dodgy,}{很可疑。}{
    \Word{dodgy}{adj.}{可疑的；狡猾的}
}

\SentenceBlock[0:04:01]{but none of it raises my spidey senses}{但真正让我提高警惕的是……}{
    \Word{spidey}{n.}{蜘蛛侠的第六感（非正式用语，表示警觉）}
}

\SentenceBlock[0:04:12]{Now, I'm not a conspiracy theorist, but something's going on.}{我不信阴谋论，但这事绝对有问题。}{
    \Word{theorist}{n.}{理论家；支持某理论的人}
}

\SentenceBlock[0:09:31]{Meet you at the rendezvous.}{碰头的地方见。}{
    \Word{rendezvous}{n.}{会面地点；约会}
}

\SentenceBlock[0:13:42]{Could be some lunatic out there being manipulated as we speak.}{也许此时此刻正有个疯子被人操纵呢。}{
    \Word{lunatic}{n.}{疯子}
}

\SentenceBlock[0:14:45]{The house red. A pint of Red Bull please.}{请来一杯招牌红葡萄酒 和一品脱红牛饮料。}{
    \Word{pint}{n.}{一品脱（容量单位，约为473毫升）}
}

\SentenceBlock[0:15:58]{Look, 15 quid for porridge.}{看，一碗粥要15英镑。}{
    \Word{quid}{n.}{英镑（口语）}
}

\SentenceBlock[0:16:20]{I'm off to the bog. Quick fag.}{我去洗手间，得来一根。}{
    \Word{bog}{n.}{厕所（俚语）}
    \Word{fag}{n.}{香烟（英式俚语）}
}

\SentenceBlock[0:19:15]{And a little respect wouldn't go amiss.}{起码请你表现出一点尊重。}{
    \Word{amiss}{adj.}{不恰当的；出错的}
}

\SentenceBlock[0:19:23]{It went missing from a consignment on display}{上个月在达克兰举行的安全设备军火展上。}{
    \Word{consignment}{n.}{托运货物；批量}
}

\SentenceBlock[0:19:36]{You work for the arms company that lost the assault rifle}{你为那家军火公司工作？ 丢了那把突击步枪。}{
    \Word{rifle}{n.}{步枪}
}

\SentenceBlock[0:19:54]{but I can give you a list of the roving ordnance.}{但我可以给你一份丢失的武器清单。}{
    \Word{roving}{adj.}{流动的；游走的}
    \Word{ordnance}{n.}{军械；武器}
}

\SentenceBlock[0:19:59]{from any accusations of negligence}{在此次事件。}{
    \Word{negligence}{n.}{疏忽；失职}
}

\SentenceBlock[0:20:09]{How is that not negligent?}{这还不算疏忽？}{
    \Word{negligent}{adj.}{疏忽的；失职的}
}

\SentenceBlock[0:20:14]{I don't think you want to tarnish the industry over a stock taking error.}{你不想因一次盘点失误就毁掉整个行业声誉吧。}{
    \Word{tarnish}{v.}{玷污；败坏}
}

\SentenceBlock[0:20:49]{And there's a Libyan conglomerate who would like compensation}{还有一家利比亚财团想要我们赔偿。}{
    \Word{conglomerate}{n.}{企业集团}
}

\SentenceBlock[0:21:03]{Diana, I know you've been putting out feelers for work in the private sector…}{戴安娜，我知道你一直在找机会去私营领域。}{
    \Word{feelers}{n.}{探询；试探}
}

\SentenceBlock[0:25:03]{at least it means Roddy's still repulsive to women.}{那至少意味着罗迪依然令女人反感。}{
    \Word{repulsive}{adj.}{令人厌恶的；令人反感的}
}

\SentenceBlock[0:25:37]{- She could have been coerced. - She was dating Roddy Ho,}{- 可能遭到了胁迫 - 她跟罗迪何约会。}{
    \Word{coerced}{v.}{胁迫（coerce 的过去分词）}
}

\SentenceBlock[0:25:39]{obviously it involved some kind of coercion.}{显然是受到了某种胁迫。}{
    \Word{coercion}{n.}{强迫；胁迫}
}

\SentenceBlock[0:26:03]{I'm not your decoy.}{我不是你的诱饵。}{
    \Word{decoy}{n.}{诱饵；圈套}
}

\SentenceBlock[0:26:39]{playing pranks.}{搞恶作剧。}{
    \Word{pranks}{n.}{恶作剧（prank 的复数）}
}

\SentenceBlock[0:31:21]{turning up like you're some kind of cavalry}{一出现就一副救世主的样子。}{
    \Word{cavalry}{n.}{骑兵；救援部队（比喻）}
}

\SentenceBlock[0:31:05]{It turns out she's my only functioning joe}{我发现原来她才是唯一有实力的特工。}{
    \Word{joe}{n.}{普通人；（此处为俚语，指“特工”或“人”）}
}

\SentenceBlock[0:31:24]{rather than a flood of shit cresting a hill.}{其实就是一股从山头涌下来的屎流。}{
    \Word{cresting}{v.}{达到顶点；形成顶部波浪（crest 的现在分词）}
}

\SentenceBlock[0:31:39]{Not before I stuck a used syringe in his thigh though,}{不过我用一个旧注射器扎了他的大腿。}{
    \Word{syringe}{n.}{注射器}
}

\SentenceBlock[0:31:41]{so now, he's got a limp in both legs.}{现在他两条腿都跛了。}{
    \Word{limp}{n.}{跛行}
}

\SentenceBlock[0:31:46]{Distinguishing marks include glass lacerations}{明显外貌特征有玻璃伤口。}{
    \Word{lacerations}{n.}{撕裂伤（laceration 的复数）}
}

\SentenceBlock[0:31:49]{and blistering from whatever you threw in his face.}{还有你给他脸上弄出的水泡。}{
    \Word{blistering}{n.}{起泡；水泡形成}
}

\SentenceBlock[0:31:57]{'Cause she sticks to the salient points.}{因为她只说重点。}{
    \Word{salient}{adj.}{突出的；重要的}
}

\SentenceBlock[0:32:02]{and headbutt the table.}{然后一头撞死在桌子上。}{
    \Word{headbutt}{v.}{用头撞击}
}

\SentenceBlock[0:32:10]{He got through your cordon.}{他突破了你的警戒线。}{
    \Word{cordon}{n.}{警戒线}
}

\SentenceBlock[0:32:33]{as are other rifles, pistols, hand grenades.}{还有其他步枪、手枪、手雷。}{
    \Word{grenades}{n.}{手榴弹（grenade 的复数）}
}

\SentenceBlock[0:34:00]{and the preamble thing that you keep doing is getting really, really fucking tedious.}{你总是这样兜圈子，真的很无聊。}{
    \Word{tedious}{adj.}{冗长乏味的；沉闷的}
}

\SentenceBlock[0:34:11]{A crack up, a drunk, a psychopath}{一个毒虫、一个酒鬼、一个精神病。}{
    \Word{psychopath}{n.}{精神病患者；变态}
}

\SentenceBlock[0:34:45]{some muscly men in suits}{一些穿着西装的肌肉男。}{
    \Word{muscly}{adj.}{肌肉发达的}
}

\SentenceBlock[0:35:06]{Our resident pillock has been compromised.}{我们这位窝里的大傻蛋已经暴露了。}{
    \Word{pillock}{n.}{蠢货；傻瓜（英式俚语）}
}

\SentenceBlock[0:35:30]{Sure, just say that. That'll buy me a shitload of time.}{好啊，就这么说，能为我争取很多时间呢。}{
    \Word{shitload}{n.}{大量（粗俗用语）}
}

\SentenceBlock[0:35:35]{but this is where we diverge.}{但到此为止了。}{
    \Word{diverge}{v.}{分歧；分开}
}

\SentenceBlock[0:37:14]{And they don't want Gimball to win, right, so they smear him.}{他们不希望金博尔赢，就抹黑他。}{
    \Word{smear}{v.}{诽谤；抹黑}
}

\SentenceBlock[0:37:25]{More calls, hopefully less conspiratorial after the…}{我们继续接听，希望少一些阴谋论，请先听…}{
    \Word{conspiratorial}{adj.}{阴谋的；密谋的}
}

\SentenceBlock[0:38:34]{Is it true you quashed a caution for kerb-crawling?}{你真的摆平过“嫖妓被抓”的警告记录？}{
    \Word{quashed}{v.}{撤销；压制（quash 的过去式）}
    \Word{kerb-crawling}{n.}{沿街招妓行为（英式）}
}

\SentenceBlock[0:43:43]{I don't care if it's in Sanskrit. It is there for a reason.}{就是梵文写的也无所谓，该条款是有道理的。}{
    \Word{Sanskrit}{n.}{梵文}
}

\SentenceBlock[0:43:55]{I couldn't be arsed.}{我懒得报告。}{
    \Word{arsed}{adj.}{懒得（做某事）（英式俚语）}
}

\SentenceBlock[0:44:05]{I've got so much dirt on you, I could start an allotment.}{我掌握你那么多黑料，都够我开个菜园子了。}{
    \Word{allotment}{n.}{分配；菜园（英式，常指租赁的小块菜地）}
}


\end{document}
