\documentclass[11pt,a4paper]{article}
%% =========================================================
%% Theme options (default: Blue)
%% Usage: \usepackage[Indigo]{aiwordbook}
%% Available: Blue, Orange, Cyan, Indigo, Amber, Green, BlueGrey
%% =========================================================
\usepackage[Indigo]{aiwordbook}

\title{Slow Horses}
\subtitle{S05E06: Scars}


\date{}
\author{}

\begin{document}

\maketitle

\SentenceBlock[0:00:20]{Well, that's rather defeatist, isn't it?}{这未免太悲观了，不是吗？}{
    \Word{defeatist}{defeatist}{adj.}{失败主义的；过于悲观的}[dɪˈfiːtɪst]
}

\SentenceBlock[0:00:22]{We're supposed to be impregnable.}{我们应该是刀枪不入的。}{
    \Word{impregnable}{impregnable}{adj.}{坚不可摧的；攻不破的}[ɪmˈprɛɡnəb(ə)l]
}

\SentenceBlock[0:01:24]{I was only trying to stop Libyan terrorists from rampaging through the fucking capital.}{我只是想阻止利比亚恐怖分子在首都横冲直撞而已。}{
    \Word{rampaging}{rampage}{v.}{横冲直撞；肆虐}[ˈræmpeɪdʒ]
}

\SentenceBlock[0:02:28]{I have just been made aware that a dissident group of security operatives are responsible for the terrible events of the last few days.}{我刚刚得知，是一支持异议的安全行动小组，对过去几天发生的可怕事件负有责任。}{
    \Word{dissident}{dissident}{adj.}{持不同政见的；反对派的}[ˈdɪsɪd(ə)nt]
}

\SentenceBlock[0:03:12]{Nothing can justify your slaughter of 11 people.}{无论你怎么说，你们杀害11人都是错的。}{
    \Word{slaughter}{slaughter}{n.}{屠杀；杀戮}[ˈslɔːtə]
}

\SentenceBlock[0:06:31]{His psych profile screams ``daddy savior complex.''}{从他的心理画像来看，“我是救世主爸爸”的执念都写在脸上了。}{
    \Word{psych}{psych}{adj.}{心理的；精神的（*psychological* 的口语缩写）}[saɪk]
    \Word{savior}{savior}{n.}{救世主；救星}[ˈseɪvjə]
}

\SentenceBlock[0:06:39]{I'd have given you a call, but I thought you'd enjoy watching him make a complete and utter fucking tit of himself.}{我本来想给你打电话的，但我觉得你会喜欢看他出尽洋相、丢人现眼，当个彻头彻尾的蠢货。}{
    \Word{tit}{tit}{n.}{（英，粗口）蠢货；笨蛋}[tɪt]
    \Word{utter}{utter}{adj.}{完全的；彻底的}[ˈʌtə]
}

\SentenceBlock[0:06:55]{Well, they might have a point about our behavior, but they trousered most of their oil money and spent the change keeping their people down.}{或许他们对我们行为的控诉有些道理，但他们把大部分石油收入装进自己口袋，剩下那点零钱还用来压制本国人民。}{
    \Word{trousered}{trouser}{v.}{（非正式）装进（自己）口袋；侵吞}[ˈtraʊzə]
}

\SentenceBlock[0:07:28]{If you add in mosques, synagogues, temples and multifaith centers, we're looking at over 5,000 potential targets.}{如果把清真寺、犹太教堂、庙宇和多元宗教中心都算上，我们要面对的潜在目标超过五千个。}{
    \Word{multifaith}{multifaith}{adj.}{多信仰的；跨宗教的}[ˌmʌltiˈfeɪθ]
    \Word{synagogues}{synagogue}{n.}{犹太会堂；犹太教堂}[ˈsɪnəɡɒɡ]
}

\SentenceBlock[0:08:15]{Ma'am, the Treasury have verified the Cayman Island trust where the money's to be paid.}{长官，财政部确认了那笔钱将汇入的开曼群岛信托账户。}{
    \Word{Treasury}{Treasury}{n.}{财政部；国库}[ˈtrɛʒəri]
}

\SentenceBlock[0:08:50]{If this goes without bloodshed, we shall escort her and her team to the airport.}{如果没有流血事件，我们要护送她和她的团队去机场。}{
    \Word{bloodshed}{bloodshed}{n.}{流血；杀戮}[ˈblʌdʃɛd]
}

\SentenceBlock[0:09:08]{What, so it was a state-sanctioned op?}{什么，竟然是国家批准的行动吗？}{
    \Word{state-sanctioned}{state-sanctioned}{adj.}{国家批准的；官方认可的}[ˌsteɪt ˈsæŋkʃənd]
}

\SentenceBlock[0:09:38]{He's picking up on what's happening from the news, but he's getting it slightly jumbled.}{他从新闻上得知了当前的时事，但他有点搞混了。}{
    \Word{jumbled}{jumble}{v.}{把……搞乱；把……搞混}[ˈdʒʌmb(ə)l]
}

\SentenceBlock[0:09:50]{Something unutterably vile about him being an embarrassing shadow of his former self.}{说他变得多么可耻、恶心，成了自己昔日辉煌的羞耻残影。}{
    \Word{vile}{vile}{adj.}{卑劣的；恶心的}[vaɪl]
    \Word{unutterably}{unutterably}{adv.}{难以形容地；极其}[ʌnˈʌtərəbli]
}

\SentenceBlock[0:10:04]{These guys are bloody good and they're fucking ruthless.}{这些人很厉害，而且冷血无情。}{
    \Word{ruthless}{ruthless}{adj.}{冷酷无情的；残忍的}[ˈruːθləs]
}

\SentenceBlock[0:10:22]{Although, it would only occur to a complete and utter fucking psychopath.}{不过，只有彻头彻尾的神经病能想到。}{
    \Word{psychopath}{psychopath}{n.}{精神变态者；反社会人格者}[ˈsaɪkəpæθ]
}

\SentenceBlock[0:10:44]{Which they are commemorating at a multifaith center shortly.}{所以人们即将在一个多信仰中心举办悼念活动。}{
    \Word{commemorating}{commemorate}{v.}{纪念；悼念}[kəˈmɛməreɪt]
}

\SentenceBlock[0:11:07]{May I ask why I've been summoned here then made to wait on the stairs like a member of staff?}{请问为什么叫我过来，却让我像员工一样在楼梯上等着？}{
    \Word{summoned}{summon}{v.}{召唤；传唤}[ˈsʌmən]
}

\SentenceBlock[0:11:30]{It's an extremely fractured country, and in my limited experience, every fucker you meet is on the take.}{这个国家极度分裂；以我有限的经验来看，你遇到的人人都在中饱私囊。}{
    \Word{fractured}{fractured}{adj.}{分裂的；四分五裂的}[ˈfræktʃəd]
}

\SentenceBlock[0:11:49]{They love to haggle, and they have a tendency to go completely fucking crackers.}{他们喜欢讨价还价，还有完全疯掉的倾向。}{
    \Word{haggle}{haggle}{v.}{讨价还价}[ˈhæɡ(ə)l]
    \Word{crackers}{crackers}{adj.}{（英，口）疯了的；发神经的}[ˈkrækəz]
}

\SentenceBlock[0:12:06]{They've paid me a nominal fee for the last three years.}{他们这三年来就象征性地给了我一点点钱。}{
    \Word{nominal}{nominal}{adj.}{象征性的；名义上的}[ˈnɒmɪn(ə)l]
}

\SentenceBlock[0:12:20]{Why are they dragging me into this insanity?}{他们为什么要拖我下水？}{
    \Word{insanity}{insanity}{n.}{疯狂；荒唐至极的事}[ɪnˈsænɪti]
}

\SentenceBlock[0:12:25]{Because you took their money and did nothing and they want to show what a corrupt mess this country is.}{因为你拿了他们的钱却什么都没做；他们想借此揭露，这个国家有多腐败、多混乱。}{
    \Word{corrupt}{corrupt}{adj.}{腐败的；贪污的}[kəˈrʌpt]
}

\SentenceBlock[0:13:08]{We have been outplayed.}{我们被彻底算计了。}{
    \Word{outplayed}{outplay}{v.}{以更高明手段击败；算计过}[ˌaʊtˈpleɪ]
}

\SentenceBlock[0:17:33]{I think she's sitting in there realizing she never was in control of her band of psychos.}{我觉得她坐在那里，意识到自己从来都没能掌控那帮疯子。}{
    \Word{psychos}{psycho}{n.}{（口）疯子；精神不正常的人}[ˈsaɪkəʊ]
}

\SentenceBlock[0:17:42]{And I don't think money is gonna quell their rage.}{我觉得钱也无法熄灭他们的怒火。}{
    \Word{quell}{quell}{v.}{平息；镇压；压制}[kwɛl]
}

\SentenceBlock[0:18:18]{I don't know why you're getting your knickers in a twist about knocking on a door.}{搞不懂你现在为什么紧张兮兮，不就是敲敲门嘛。}{
    \Word{knickers}{knickers}{n.}{（英）女式内裤；（口）裤衩}[ˈnɪkəz]
}

\SentenceBlock[0:18:30]{Probably it reminds you of the rush you used to get when you got absolutely arseholed.}{可能让你想起了酩酊大醉时的那种刺激。}{
    \Word{arseholed}{arseholed}{adj.}{（英，粗口）烂醉如泥的}[ˈɑːshəʊld]
}

\SentenceBlock[0:21:38]{Lima, Golf 5-7 to control. We've apprehended the suspect.}{LG57呼叫指挥：我们已逮捕嫌犯。}{
    \Word{apprehended}{apprehend}{v.}{逮捕；拘捕}[ˌæprɪˈhɛnd]
}

\SentenceBlock[0:22:39]{They might already be inside dressed as mourners.}{他们可能已经混进去了，装扮成悼念者的样子。}{
    \Word{mourners}{mourner}{n.}{哀悼者；送葬者}[ˈmɔːnə]
}

\SentenceBlock[0:23:22]{But for more contemporary wisdom that might give solace to our younger mourners, I reach for the words of Dominic Toretto in Furious 7.}{但若要寻求更贴近当代、也许能安慰在场年轻悼念者的智慧，那我会引用《速度与激情7》中多米尼克·托雷托的一句话。}{
    \Word{solace}{solace}{n.}{安慰；慰藉}[ˈsɒləs]
}

\SentenceBlock[0:23:39]{The lesson I take from both those sages, separated though they are by centuries, is that while London might not be ``Londerful'' today, it will be ``Londerful'' tomorrow if we channel-- Yeah, right. Everyone, up.}{尽管两位智者生活的年代相差数世纪，我从他们身上学到：今天的伦敦也许不算充满“美好活力”，但它明天会的——只要我们集中……好了，所有人，都起来。}{
    \Word{sages}{sage}{n.}{智者；贤人}[seɪdʒ]
}

\SentenceBlock[0:24:22]{Hang on. What the hell is going on? I'd only just started my eulogy.}{等等。到底是怎么回事？我的悼词才刚开头呢。}{
    \Word{eulogy}{eulogy}{n.}{悼词；颂词}[ˈjuːlədʒi]
}

\SentenceBlock[0:24:37]{Libyan operatives are extorting the government for £100 million.}{利比亚人向政府勒索一亿英镑。}{
    \Word{extorting}{extort}{v.}{勒索；敲诈}[ɪkˈstɔːt]
}

\SentenceBlock[0:25:58]{Claude, I'm here with River Cartwright, who's crashed into the memorial service babbling something about a Libyan attack that none of my agents seem to know anything about.}{克劳德，我和瑞弗·卡特怀特在一起；他冲进追悼会现场，胡言乱语说什么利比亚人袭击的事，可我的手下似乎对此一无所知。}{
    \Word{babbling}{babble}{v.}{胡言乱语；喋喋不休}[ˈbæb(ə)l]
}

\SentenceBlock[0:28:29]{Can you stop fucking contradicting me?}{你能别跟我唱反调了吗？}{
    \Word{contradicting}{contradict}{v.}{反驳；与……矛盾}[ˌkɒntrəˈdɪkt]
}

\SentenceBlock[0:29:06]{It's unorthodox, yeah.}{是非正统手段，对。}{
    \Word{unorthodox}{unorthodox}{adj.}{非传统的；不按常规的}[ʌnˈɔːθədɒks]
}

\SentenceBlock[0:29:40]{When they pick over the bones of this you'll be exonerated, ma'am.}{等他们把这事翻来覆去地调查清楚，你一定会被还以清白，长官。}{
    \Word{exonerated}{exonerate}{v.}{为……洗清罪名；开脱}[ɪɡˈzɒnəreɪt]
}

\SentenceBlock[0:31:05]{Who was it? The Russkies up to their old tricks?}{是谁干的？俄国佬又来老一套？}{
    \Word{Russkies}{Russky}{n.}{（蔑称）俄国佬；俄罗斯人}[ˈrʌski]
}

\SentenceBlock[0:31:21]{I think that's what they wanted to instill.}{我想他们就是想制造混乱。}{
    \Word{instill}{instill}{v.}{灌输；逐步植入}[ɪnˈstɪl]
}

\SentenceBlock[0:31:23]{As a way of ransoming us.}{作为勒索我们的手段。}{
    \Word{ransoming}{ransom}{v.}{索要赎金；勒索}[ˈrɑːnsəm]
}

\SentenceBlock[0:32:16]{Yes, you see, if ever we were dealing with some really tricky buggers, we… we'd hit them when they thought it was over.}{对，你看：如果我们要对付某些很难缠的混蛋，我们……就会在对方以为一切都结束时动手。}{
    \Word{buggers}{bugger}{n.}{（英，粗口）混蛋；讨厌鬼}[ˈbʌɡə]
}

\SentenceBlock[0:36:24]{Because of a keystroke you made.}{就因为你敲了一下键盘。}{
    \Word{keystroke}{keystroke}{n.}{键击；按键动作}[ˈkiːstrəʊk]
}

\SentenceBlock[0:36:36]{You left us to gangsters and militias, and you did not arm us against them.}{你们把我们丢给了黑帮和民兵，却没有给我们配备武器来对抗他们。}{
    \Word{gangsters}{gangster}{n.}{匪徒；黑帮成员}[ˈɡæŋstə]
}

\SentenceBlock[0:42:11]{We gotta get that fucking lift mended.}{我们得把那台该死的电梯修好。}{
    \Word{mended}{mend}{v.}{修理；修补}[mɛnd]
}

\SentenceBlock[0:42:38]{Fuck MI5. My gaff, my rules.}{去他的军情五处：我的地盘我说了算。}{
    \Word{gaff}{gaff}{n.}{（英，口）住所；地盘}[ɡæf]
}

\SentenceBlock[0:42:55]{One understands that you've been allowed to run this place under sufferance because of… Well, because of what you've done for the Service.}{据说你之所以还能勉强掌管这个地方，是因为……嗯，因为你曾为情报处立过一些功劳。}{
    \Word{sufferance}{sufferance}{n.}{容忍；默许（常用于短语 *under sufferance*）}[ˈsʌfərəns]
}

\SentenceBlock[0:43:14]{I'm beginning to regret giving him the tip-off.}{我开始后悔给他情报了。}{
    \Word{tip-off}{tip-off}{n.}{密报；线报}[ˈtɪpɒf]
}

\SentenceBlock[0:43:18]{- …another member of your delinquent te-- - Also in the ledger of things that Slough House has not fucked up, which, I grant you, is a little thin in the grand scheme, is that I caught the femme fatale behind this week's fucking bloodshed and chaos without your goons having a firefight in an embassy.}{- 你的另一个手下失职…… - 另外，在斯劳部门“没搞砸事件簿”里——我承认，这本事件簿放在大局里确实有点薄——有一条是：我抓到了那个制造这一周流血事件和混乱的蛇蝎女子，还避免了你的人在使馆里开枪。}{
    \Word{ledger}{ledger}{n.}{账本；登记册；（喻）记录簿}[ˈlɛdʒə]
    \Word{delinquent}{delinquent}{adj.}{失职的；不守规矩的}[dɪˈlɪŋkwənt]
    \Word{femme}{femme}{n.}{（法语）女人；常用于短语 femme fatale（蛇蝎美人）}[fɛm]
    \Word{fatale}{fatale}{adj.}{（法语）致命的；（在 femme fatale 中）蛇蝎的}[fəˈtɑːl]
    \Word{bloodshed}{bloodshed}{n.}{流血；杀戮}[ˈblʌdʃɛd]
    \Word{goons}{goon}{n.}{打手；走狗}[ɡuːn]
}

\SentenceBlock[0:43:38]{Yeah, you wanna bury the fact that she… she batted her eyelids and you let her walk out of the building and fuck up the MI5 mainframe all at the same time.}{对，你想掩盖事实：她……她对你眨眨眼，你就放她走了；同时还把军情五处的主机给弄坏了。}{
    \Word{eyelids}{eyelid}{n.}{眼睑；眼皮}[ˈaɪlɪd]
}

\SentenceBlock[0:45:01]{Now, anymore crap from either of you two and I will see to it the security services destroys you and your god-awful livelihoods in public.}{你们两个再耍花招，我会确保情报部门在公众面前彻底摧毁你们，以及你们那可憎至极的营生。}{
    \Word{livelihoods}{livelihood}{n.}{生计；饭碗}[ˈlaɪvlɪhʊd]
}

\SentenceBlock[0:45:46]{You know what, I was… I was probably a tad premature, wasn't I?}{你知道，我……我可能有点不成熟，对吧？}{
    \Word{tad}{tad}{n.}{一点点；少量}[tæd]
}

\SentenceBlock[0:46:38]{Well, we pin it on the fucking chump who deserves to go.}{我们就找该滚蛋的大聪明背。}{
    \Word{chump}{chump}{n.}{（口）笨蛋；冤大头}[tʃʌmp]
}

\SentenceBlock[0:47:04]{If you're not out of your office within the hour, I'm gonna send this to every grubby little hack I know from my drinking days.}{如果你一小时内还没离职，我要把这个发给我之前喝酒时认识的每一个卑鄙小记者。}{
    \Word{grubby}{grubby}{adj.}{肮脏的；卑鄙的}[ˈɡrʌbi]
    \Word{hack}{hack}{n.}{（贬）蹩脚记者；枪手}[hæk]
}

\SentenceBlock[0:48:37]{Do I detect a note of sarcasm?}{你是不是在讽刺我？}{
    \Word{sarcasm}{sarcasm}{n.}{讽刺；嘲讽}[ˈsɑːkæzəm]
}

\SentenceBlock[0:49:38]{It's a bloodbath.}{这是场血腥杀戮。}{
    \Word{bloodbath}{bloodbath}{n.}{大屠杀；血腥杀戮}[ˈblʌdbɑːθ]
}



\end{document}
