\documentclass[11pt,a4paper]{article}
%% =========================================================
%% Theme options (default: Blue)
%% Usage: \usepackage[Indigo]{aiwordbook}
%% Available: Blue, Orange, Cyan, Indigo, Amber, Green, BlueGrey
%% =========================================================
\usepackage[Orange]{aiwordbook}

\title{Slow Horses}
\subtitle{S05E04: Missiles}


\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:00:47]{And if she has done anything, it was done under duress.}{就算她做了什么 那也是被胁迫的}{
    \Word{duress}{n.}{胁迫，强迫}[djʊəˈres]
}

\SentenceBlock[0:01:14]{No. I'm saying I once worked undercover.}{不 我是说 我当过卧底}{
    \Word{undercover}{adv.}{秘密地，暗中地}[ˌʌndəˈkʌvə]
}

\SentenceBlock[0:02:56]{Because they're gonna get invited to a hoedown,}{因为我会要他们好看}{
    \Word{hoedown}{n.}{乡村舞会，农家舞会}[ˈhəʊdaʊn]
}

\SentenceBlock[0:04:44]{When you two knobheads went to Tara's address,}{你们两个蠢货去塔拉的地址时}{
    \Word{knobhead}{n.}{蠢货，笨蛋}[ˈnɒbhed]
}

\SentenceBlock[0:07:22]{in what the police is referring to as ``fuel tampering.''}{“燃料破坏”事件 发表了如下声明}{
    \Word{tamper}{v.}{擅自改动，篡改}[ˈtæmpə]
}

\SentenceBlock[0:07:49]{I mean, I'll look detached and afraid.}{会显得我跟儿子关系不好、胆小怕事}{
    \Word{detached}{adj.}{冷漠的，不带感情的}[dɪˈtætʃt]
}

\SentenceBlock[0:07:54]{You're proud of your son's stance and passion}{你为儿子的立场和热情感到骄傲}{
    \Word{stance}{n.}{立场，态度}[stɑːns]
}

\SentenceBlock[0:08:01]{Stoke the sympathy.}{激发同情心}{
    \Word{stoke}{v.}{激起，煽动}[stəʊk]
}

\SentenceBlock[0:09:06]{Here are the full unredacted background files on Jaffrey and Gimball.}{这是贾弗里与金博尔的完整未删背景资料}{
    \Word{unredacted}{adj.}{未删减的}[ˌʌnrɪˈdæktɪd]
}

\SentenceBlock[0:09:45]{This once great city is suffering from a plague again.}{昔日辉煌的城市再遭瘟疫侵袭}{
    \Word{plague}{n.}{瘟疫，灾祸}[pleɪɡ]
}

\SentenceBlock[0:09:57]{gnaw away at the rigging of our national identity.}{我们民族身份的根基}{
    \Word{gnaw}{v.}{侵蚀，逐渐破坏}[nɔː]
    \Word{rigging}{n.}{结构，支撑体系}[ˈrɪɡɪŋ]
}

\SentenceBlock[0:11:52]{Yeah, well, of course it is, you knucklehead.}{是 当然安全了 蠢货}{
    \Word{knucklehead}{n.}{笨蛋，蠢货}[ˈnʌkəlhed]
}

\SentenceBlock[0:12:17]{Guess he spooked her.}{我猜他跟她通过电话了}{
    \Word{spook}{v.}{吓到，使惊慌}[spuːk]
}

\SentenceBlock[0:12:24]{He's convinced she's an innocent coerced into turning on him}{他坚信她是无辜的 是被迫背叛他的}{
    \Word{coerce}{v.}{强迫，胁迫}[kəʊˈɜːs]
}

\SentenceBlock[0:12:41]{No. Trust me. I feel it in my chakra.}{不 相信我 我的第六感告诉我了}{
    \Word{chakra}{n.}{脉轮（指精神能量中心）}[ˈtʃʌkrə]
}

\SentenceBlock[0:13:15]{Look, I just wanna insulate Slough House from whatever the fuck is going on.}{我只想将斯劳部门隔绝于这乱局之外}{
    \Word{insulate}{v.}{使隔绝，保护}[ˈɪnsjʊleɪt]
}

\SentenceBlock[0:13:51]{Let the bastard crawl in.}{让那个混蛋进来吧}{
    \Word{crawl}{v.}{爬行，卑微地进入}[krɔːl]
}

\SentenceBlock[0:14:22]{What about your smears against my husband}{那你对我丈夫的污蔑}{
    \Word{smear}{n.}{诽谤，污蔑}[smɪə]
}

\SentenceBlock[0:15:26]{who, incidentally, you were also boffing.}{而且你也跟她上床了}{
    \Word{incidentally}{adv.}{顺便一提}[ˌɪnsɪˈdentəli]
    \Word{boff}{v.}{发生性关系}[bɒf]
}

\SentenceBlock[0:16:13]{Your mother, Denise, was a masseuse.}{你的母亲丹尼丝曾是一名按摩师}{
    \Word{masseuse}{n.}{女按摩师}[mæˈsɜːs]
}

\SentenceBlock[0:16:27]{convicted, and sent to prison for GBH.}{被判犯有故意伤害罪 并被送入监狱}{
    \Word{convict}{v.}{判定有罪}[kənˈvɪkt]
}

\SentenceBlock[0:17:24]{and your god-awful livelihoods in public.}{彻底摧毁你们以及你们那可憎至极的营生}{
    \Word{livelihood}{n.}{生计，谋生方式}[ˈlaɪvlɪhʊd]
}

\SentenceBlock[0:18:02]{He groomed me.}{他对我进行引诱和洗脑}{
    \Word{groom}{v.}{引诱，操纵}[ɡruːm]
}

\SentenceBlock[0:18:14]{destroys you and your god-awful livelihoods in public.}{彻底摧毁你们以及你们那可憎至极的营生}{
    \Word{livelihood}{n.}{生计，谋生方式}[ˈlaɪvlɪhʊd]
}

\SentenceBlock[0:18:16]{See? Got him on tape trying to blackmail us.}{看见没？我把他勒索我们的话录下来了}{
    \Word{blackmail}{v.}{勒索，敲诈}[ˈblækmeɪl]
}

\SentenceBlock[0:18:35]{about how the Turks are the mongrels of Europe.}{说土耳其人是欧洲的杂种}{
    \Word{mongrel}{n.}{杂种，混血儿}[ˈmʌŋɡrəl]
}

\SentenceBlock[0:20:05]{It's an auditorium and a stage, so it's one big sight line.}{此为礼堂舞台一体结构形成无障碍视线}{
    \Word{auditorium}{n.}{礼堂，观众席}[ˌɔːdɪˈtɔːrɪəm]
}

\SentenceBlock[0:20:25]{Well, at least the security team are top notch.}{至少安保团队是极品}{
    \Word{notch}{n.}{等级，水准}[nɒtʃ]
}

\SentenceBlock[0:20:43]{Earlier, you were very dismissive of me.}{早些时候 你对我非常不屑一顾}{
    \Word{dismissive}{adj.}{轻视的，不屑一顾的}[dɪsˈmɪsɪv]
}

\SentenceBlock[0:23:58]{At least my lot fuck up on an epic scale.}{至少我的人一搞砸就搞大的}{
    \Word{epic}{adj.}{巨大的，史诗般的}[ˈepɪk]
}

\SentenceBlock[0:24:01]{They're not just run-of-the-mill fuckups like yours.}{不像你的人 搞砸都那么无聊}{
    \Word{run-of-the-mill}{adj.}{普通的，平庸的}[ˌrʌn əv ðə ˈmɪl]
}

\SentenceBlock[0:24:28]{It'll be bland, but inoffensive.}{演讲会平淡无奇 但不冒犯人}{
    \Word{bland}{adj.}{平淡的，乏味的}[blænd]
}

\SentenceBlock[0:28:40]{But, instead, we find ourselves mourning and more divided than ever.}{但我们却在哀悼 空前分裂}{
    \Word{mourning}{n.}{哀悼}[ˈmɔːnɪŋ]
}

\SentenceBlock[0:33:29]{Of course they're gonna fucking find out, you moron.}{他们当然会发现的 蠢货}{
    \Word{moron}{n.}{蠢货，傻子}[ˈmɔːrɒn]
}

\SentenceBlock[0:33:40]{Come on, pal. The mayor's murderous son is just too good a target to pass up.}{市长那杀人儿子是绝佳目标 岂能放过}{
    \Word{murderous}{adj.}{杀人的，凶残的}[ˈmɜːdərəs]
}

\SentenceBlock[0:33:54]{It's electoral fucking kryptonite.}{这是选举中的重大弱点}{
    \Word{kryptonite}{n.}{致命弱点}[ˈkrɪptənaɪt]
}

\SentenceBlock[0:34:41]{Your lot always revert to type.}{你们这种人总是本性难移}{
    \Word{revert}{v.}{恢复，回到原状}[rɪˈvɜːt]
}

\SentenceBlock[0:35:05]{Fucking disgrace.}{真丢脸}{
    \Word{disgrace}{n.}{耻辱，丢脸的事}[dɪsˈɡreɪs]
}

\SentenceBlock[0:36:08]{Good to see the bulldog spirit's alive in the younger generation.}{很高兴看到斗牛犬精神犹存于年轻一代}{
    \Word{bulldog}{adj.}{顽强的，不屈不挠的}[ˈbʊldɒɡ]
}



\end{document}
