\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Slow Horses\\\Large S05E03: Tall Tales}


\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:00:24]{Injuries are reported but no fatalities as yet.}{据报有人受伤 但目前无人死亡}{
    \Word{fatality}{n.}{死亡，致死事件}
}

\SentenceBlock[0:00:31]{which is hampering the response of emergency services.}{从而延误了急救服务}{
    \Word{hamper}{v.}{妨碍，阻碍}
}

\SentenceBlock[0:00:42]{Take Ho down to interrogation cell eight.}{把何带去八号审讯室}{
    \Word{interrogation}{n.}{审讯，盘问}
}

\SentenceBlock[0:00:45]{- The fright cube? - Yep.}{- 恐惧空间？ - 对}{
    \Word{fright}{n.}{恐惧，惊吓}
}

\SentenceBlock[0:01:17]{Denying liability. Claiming sabotage.}{拒绝承担责任 说有人搞破坏}{
    \Word{liability}{n.}{责任，法律责任}
}

\SentenceBlock[0:01:32]{and the firefighters can't get in there until the gridlock eases.}{可消防员因为交通瘫痪无法进入现场}{
    \Word{gridlock}{n.}{交通瘫痪，僵局}
}

\SentenceBlock[0:01:59]{There will be repercussions, I promise you that.}{会有后果的 我向你保证}{
    \Word{repercussion}{n.}{严重后果，连锁反应}
}

\SentenceBlock[0:02:28]{so we're assuming that's where the tampering happened.}{所以我们猜那里是遭到破坏的现场}{
    \Word{tampering}{n.}{篡改，破坏}
}

\SentenceBlock[0:04:35]{Well, once the fire is out, get forensics in.}{一旦火被扑灭 就让法证科进场}{
    \Word{forensics}{n.}{法医学，刑事鉴定}
}

\SentenceBlock[0:04:49]{Taverner wants them in lockdown while she sweats Ho.}{泰维纳希望在她审讯何期间 继续保持封锁}{
    \Word{sweat}{v.}{施压，逼供}
}

\SentenceBlock[0:05:00]{I'd check the downstairs lav.}{可能在楼下的厕所里}{
    \Word{lav}{n.}{厕所}
}

\SentenceBlock[0:05:02]{She'll either be shoveling one up or curling one out.}{她要么在嗑药物 要么在排秽物}{
    \Word{shovel}{v.}{大量吞服}
    \Word{curl}{v.}{排便（俚语）}
}

\SentenceBlock[0:05:21]{Well… Talking of breakfast made me a bit peckish.}{说到早餐 我有点饿了}{
    \Word{peckish}{adj.}{有点饿的}
}

\SentenceBlock[0:05:24]{There's fresh cake and crisps downstairs.}{楼下有新鲜的蛋糕和薯片}{
    \Word{crisp}{n.}{薯片}
}

\SentenceBlock[0:07:00]{And I bust out of that years ago.}{而我多年前就从那里越狱了}{
    \Word{bust}{v.}{逃脱，越狱}
}

\SentenceBlock[0:07:03]{I am mythical, historical and futuristical.}{我充满神话色彩 兼具历史底蕴和未来气息}{
    \Word{mythical}{adj.}{神话般的}
    \Word{futuristical}{adj.}{未来主义的}
}

\SentenceBlock[0:07:08]{Roddy Ho is merely the latest incarnation of my most potent energy.}{罗迪·何不过是我最新、最强的化身}{
    \Word{incarnation}{n.}{化身，体现}
    \Word{potent}{adj.}{强大的，有效的}
}

\SentenceBlock[0:07:37]{Is that a lack of breastfeeding or too much breastfeeding?}{缺少母乳喂养还是母乳喂养过剩？}{
    \Word{breastfeeding}{n.}{母乳喂养}
}

\SentenceBlock[0:09:13]{Why didn't you warn me we were swarming with pricks?}{你们为什么不警告我 这里被一群混蛋占领了？}{
    \Word{swarm}{v.}{蜂拥，充斥}
}

\SentenceBlock[0:09:42]{Flyte's up to speed. Maybe she'll deign to share.}{弗莱特了解最新情况 也许她愿意屈尊分享一下}{
    \Word{deign}{v.}{屈尊，勉强做}
}

\SentenceBlock[0:10:11]{Was trying to allude to it rather than mention it}{我本来是想暗示一下 而不是}{
    \Word{allude}{v.}{暗指，影射}
}

\SentenceBlock[0:10:18]{is out of sheer embarrassment at the batshit lunacy of it.}{是这件事实在太疯癫、太荒唐}{
    \Word{batshit}{adj.}{疯狂的，荒唐的}
    \Word{lunacy}{n.}{疯狂，荒谬}
}

\SentenceBlock[0:10:25]{He thinks sinister forces are trying to bring down the country.}{他认为恶势力想搞垮整个英国}{
    \Word{sinister}{adj.}{邪恶的，不祥的}
}

\SentenceBlock[0:10:29]{Yeah, but it's bollocks.}{是 但这是无稽之谈}{
    \Word{bollocks}{n.}{胡说八道}
}

\SentenceBlock[0:11:20]{Couldn't spare me some change, could you? I'm trying to get a hostel.}{能给我点零钱吗？我想找个旅社住}{
    \Word{hostel}{n.}{旅社，青年旅舍}
}

\SentenceBlock[0:12:47]{I'm expelling excess gas.}{我在排出多余气体}{
    \Word{expel}{v.}{排出}
}

\SentenceBlock[0:12:52]{It's like you've got a pauper's grave in your arsehole.}{简直像你的屁眼里有个万人坑}{
    \Word{pauper}{n.}{穷人}
    \Word{arsehole}{n.}{肛门（粗俗）}
}

\SentenceBlock[0:12:58]{Yeah, you might wanna keep hold of that. I think I hit a seam.}{是 你最好拿着清新剂 我好像解除封印了}{
    \Word{seam}{n.}{矿层；（此处指）一股}
}

\SentenceBlock[0:13:03]{I-I'm up to my nipples in acid reflux is what I am.}{我…肚子里在反酸水才对}{
    \Word{nipple}{n.}{乳头}
    \Word{reflux}{n.}{反流}
}

\SentenceBlock[0:13:13]{Do I have permission to use the downstairs boudoir then?}{那我可以用楼下的洗手间吗？}{
    \Word{boudoir}{n.}{化妆室；（讽刺）厕所}
}

\SentenceBlock[0:13:18]{Please let him go. He fucking reeks.}{请让他去吧 他简直臭气熏天}{
    \Word{reek}{v.}{散发恶臭}
}

\SentenceBlock[0:13:55]{Yeah, you know where you are with the filth.}{是啊 跟那些“混蛋”打交道 至少心里有数}{
    \Word{filth}{n.}{警察（俚语，贬义）}
}

\SentenceBlock[0:13:59]{Yeah, it's totally amoral.}{完全没有道德底线}{
    \Word{amoral}{adj.}{不讲道德的}
}

\SentenceBlock[0:14:00]{Yeah, slip 'em a fiver, they'll show you a dead body.}{对 给他们塞5英镑 就能让你看尸体}{
    \Word{slip}{v.}{偷偷给}
}

\SentenceBlock[0:14:14]{Yeah, this banter stuff's harder than it looks.}{好嘛 没想到拌嘴这件事还挺难}{
    \Word{banter}{n.}{玩笑式斗嘴}
}

\SentenceBlock[0:14:33]{If you're looking for the gun in the cistern,}{如果你是在找水箱里的枪}{
    \Word{cistern}{n.}{水箱}
}

\SentenceBlock[0:15:07]{As MI5's legal counsel, I don't really do off the record.}{我是军情五处律师 不私下发表看法}{
    \Word{counsel}{n.}{法律顾问}
}

\SentenceBlock[0:15:21]{Like a parlor game. Kind of.}{就像客厅里那种小游戏 差不多的意思}{
    \Word{parlor}{n.}{客厅}
}

\SentenceBlock[0:15:34]{I-I'm not sure she's got the heft.}{我觉得她能力不足}{
    \Word{heft}{n.}{分量；实力}
}

\SentenceBlock[0:15:57]{given how we're ruffling Gimball's feathers and his wife, he…}{鉴于我们惹毛了金博尔和他老婆 他…}{
    \Word{ruffle}{v.}{惹恼}
}

\SentenceBlock[0:16:01]{You know his wife? Works for that snotty tabloid.}{你认识他老婆吗？那家八卦报社的}{
    \Word{snotty}{adj.}{自以为是的}
    \Word{tabloid}{n.}{小报，八卦报纸}
}

\SentenceBlock[0:16:04]{Well, she has a known animus towards me}{她一向对我有敌意}{
    \Word{animus}{n.}{敌意}
}

\SentenceBlock[0:16:07]{and there could be some un-underhanded things coming my way.}{而且很可能用些下三滥手段来对付我}{
    \Word{ununderhanded}{adj.}{卑鄙的}
}

\SentenceBlock[0:16:11]{Unpleasant things. Lies. Scandalous lies.}{令人不快的 比如谎言 关于丑闻的谎言}{
    \Word{scandalous}{adj.}{丑闻性的}
}

\SentenceBlock[0:17:22]{And don't trust or listen to that human fungus.}{不要相信 也不要听那个烂人的话}{
    \Word{fungus}{n.}{真菌；（比喻）令人厌恶的人}
}

\SentenceBlock[0:17:57]{So why don't you just drop the theatrics and come at the king head-on.}{你就别演戏了 直接面对我这个王者吧}{
    \Word{theatrics}{n.}{做作的表演}
}

\SentenceBlock[0:18:11]{dragon slayer, the human tripod}{屠龙者 人体三脚架}{
    \Word{slayer}{n.}{屠杀者，杀手}
    \Word{tripod}{n.}{三脚架}
}

\SentenceBlock[0:18:20]{Do you have any connection with the incel community?}{你和非自愿单身者社群有什么联系吗？}{
    \Word{incel}{n.}{非自愿独身者}
}

\SentenceBlock[0:18:27]{Is this your subtle way of asking if the ramrod's getting any?}{你是在拐弯抹角问“打桩王”有没有性生活？}{
    \Word{ramrod}{n.}{性能力极强的人（俚语）}
}

\SentenceBlock[0:18:41]{I'm the opposite of an involuntary celibate.}{我和非自愿独身者恰恰相反}{
    \Word{involuntary}{adj.}{非自愿的}
    \Word{celibate}{n.}{独身者}
}

\SentenceBlock[0:19:23]{Okay. Coincidence. Happenstance.}{好吧 巧合 偶然事件}{
    \Word{happenstance}{n.}{偶然事件}
}

\SentenceBlock[0:19:37]{Hell hath no fury like a Roddy Ho ex, yeah?}{罗迪何之前的前男友怒不可遏 是吧？}{
    \Word{hath}{v.}{有（古英语）}
    \Word{fury}{n.}{狂怒}
}

\SentenceBlock[0:19:44]{It's like orgasmic vertigo or the bends.}{就像头晕或减压病的高潮}{
    \Word{vertigo}{n.}{眩晕}
    \Word{orgasmic}{adj.}{极度兴奋的}
}

\SentenceBlock[0:19:53]{No, you're not a lothario. You're not James Bond.}{对 你不是迷人浪子 不是占士邦}{
    \Word{lothario}{n.}{风流浪子}
}

\SentenceBlock[0:20:04]{followed by periods of intense neediness}{紧接着就是对对方极度依赖}{
    \Word{neediness}{n.}{情感依赖}
}

\SentenceBlock[0:20:13]{as I'm sure you have pondered yourself,}{我相信你自己也想过}{
    \Word{ponder}{v.}{仔细思考}
}

\SentenceBlock[0:20:31]{carrying what looks like a thermos.}{手里拿着一个看起来像热水瓶的东西}{
    \Word{thermos}{n.}{保温瓶}
}

\SentenceBlock[0:22:42]{London grieves for you.}{伦敦为大家哀悼}{
    \Word{grieve}{v.}{哀悼}
}

\SentenceBlock[0:23:32]{The Metropolitan Police have informed us that they located the device}{伦敦警察厅已向我们通报}{
    \Word{Metropolitan}{adj.}{大都会的}
}

\SentenceBlock[0:23:36]{that was detonated inside the penguin enclosure.}{他们在企鹅池发现了已被引爆的装置}{
    \Word{detonate}{v.}{引爆}
}

\SentenceBlock[0:23:56]{No, he has special dispensation.}{不 他获得了特殊豁免权}{
    \Word{dispensation}{n.}{特许，豁免}
}

\SentenceBlock[0:24:40]{Assassinate a populist leader.}{暗杀一位民粹主义领导人}{
    \Word{populist}{n.}{民粹主义者}
}

\SentenceBlock[0:24:45]{Well, Gimball… G-Gimball's a populist. What, they're gonna whack Gimball?}{金博尔是民粹分子…难道要动干掉他？}{
    \Word{whack}{v.}{杀掉}
}

\SentenceBlock[0:25:20]{Evergreen statement.}{这是老生常谈}{
    \Word{evergreen}{adj.}{老生常谈的}
}

\SentenceBlock[0:25:34]{The next on the list is assassinate a populist leader.}{接下来就该暗杀民粹主义领袖了}{
    \Word{assassinate}{v.}{暗杀}
}

\SentenceBlock[0:25:37]{So right now, we're at DEFCON shit, fuck, bollocks and scramble,}{所以现在的情况是全国大危机}{
    \Word{scramble}{n.}{混乱，紧急状态}
}

\SentenceBlock[0:25:57]{I confiscated your gun. It's humiliating.}{我收缴了你的枪 这很丢人}{
    \Word{confiscate}{v.}{没收}
}

\SentenceBlock[0:27:03]{My last relationship ended badly. I didn't wanna jinx it.}{我上段感情结局很糟 所以不想触这霉头}{
    \Word{jinx}{v.}{带来霉运}
}

\SentenceBlock[0:28:08]{Things, they go loco. Yeah, I've… I've seen it before.}{很多行为会变得疯狂 对 我…见过}{
    \Word{loco}{adj.}{疯狂的}
}

\SentenceBlock[0:28:11]{It was in a Cindy Crawford flick, I think. She only did a couple of them--}{记得是辛迪·克劳馥的片子 她作品不多…}{
    \Word{flick}{n.}{电影}
}

\SentenceBlock[0:28:25]{She… She turned against her handlers, risked everything.}{她…背叛了自己的上线 冒险失去一切}{
    \Word{handler}{n.}{上线，操控者}
}

\SentenceBlock[0:30:16]{Except I had some charm and charisma.}{只是我当时有点魅力、亲和力}{
    \Word{charisma}{n.}{个人魅力}
}

\SentenceBlock[0:30:27]{Stasi were the real deal.}{民主德国安全部可不是开玩笑的}{
    \Word{Stasi}{n.}{东德国家安全部}
}

\SentenceBlock[0:30:53]{I think I'd rather be crucified}{我宁愿被钉在十字架上}{
    \Word{crucify}{v.}{钉死在十字架上}
}

\SentenceBlock[0:31:03]{Standish, I'm fucking gasping. It's just the one.}{斯坦迪什 我烟瘾犯了 就一支}{
    \Word{gasp}{v.}{极度渴望}
}

\SentenceBlock[0:31:27]{Inventive, though.}{不过很有创造力}{
    \Word{inventive}{adj.}{有创造力的}
}

\SentenceBlock[0:31:32]{Eastern bloc budgets didn't stretch to blowtorches}{东欧集团的预算里没有钱买喷灯}{
    \Word{bloc}{n.}{集团，阵营}
    \Word{blowtorch}{n.}{喷灯}
}

\SentenceBlock[0:31:40]{They got an aerosol can}{他们用一个喷雾罐}{
    \Word{aerosol}{n.}{喷雾罐}
}

\SentenceBlock[0:32:04]{he's on the brink of death,}{他奄奄一息}{
    \Word{brink}{n.}{边缘}
}

\SentenceBlock[0:32:17]{Stored in the poor bastard's battered head.}{它就在那个可怜虫被揍烂的脑袋里}{
    \Word{battered}{adj.}{被重击的}
}

\SentenceBlock[0:32:30]{M-Maybe not love, but the closest thing a spook can come to it.}{也许不是爱 但那是一个特工 最接近爱的东西了}{
    \Word{spook}{n.}{间谍}
}

\SentenceBlock[0:32:49]{Yeah, they were shacking up together in a safe house.}{对 他们一起住在一个安全屋里}{
    \Word{shack up}{v.}{同居}
}

\SentenceBlock[0:33:27]{Even when they beat her in the stomach with a fire extinguisher.}{即使他们用灭火器砸她的肚子}{
    \Word{extinguisher}{n.}{灭火器}
}

\SentenceBlock[0:35:29]{- Fuck. - Come on, fuckwits.}{- 该死 - 来吧 废物们}{
    \Word{fuckwit}{n.}{蠢货}
}

\SentenceBlock[0:36:20]{You go to Jaffrey's. Just as a precaution.}{你去贾弗里那里 以防万一}{
    \Word{precaution}{n.}{预防措施}
}

\SentenceBlock[0:36:40]{Don't be fucking daft, Standish.}{别傻了 斯坦迪什}{
    \Word{daft}{adj.}{愚蠢的}
}

\SentenceBlock[0:37:28]{She wasn't even fussed when I showed her I could hack into the MI5 database.}{我向她秀我能侵入军情五处的数据库 她甚至都不在意}{
    \Word{fussed}{adj.}{在意的}
}

\SentenceBlock[0:37:18]{in a much nastier and smaller cell than this.}{牢房会比这里肮脏、狭小许多}{
    \Word{nasty}{adj.}{恶劣的}
}




\end{document}
