\documentclass[11pt,a4paper]{article}
%% =========================================================
%% Theme options (default: Blue)
%% Usage: \usepackage[Indigo]{aiwordbook}
%% Available: Blue, Orange, Cyan, Indigo, Amber, Green, BlueGrey
%% =========================================================
\usepackage[Indigo]{aiwordbook}

\title{Pluribus}
\subtitle{S01E04: Please, Carol}

\date{}
\author{}

\begin{document}

\maketitle

\SentenceBlock[0:05:31]{To all of our customers: Management was obligated to open your units.}{致尊敬的客户：管理人员有义务打开你们的仓库。}{
    \Word{obligated}{obligated}{adj.}{有义务的；被迫的}[ˈɒblɪɡeɪtɪd]
}

\SentenceBlock[0:05:33]{Restitution will be made. Apologies.}{事后会支付赔偿。万分抱歉。}{
    \Word{Restitution}{restitution}{n.}{赔偿；补偿；归还}[ˌrestɪˈtjuːʃən]
}

\SentenceBlock[0:12:12]{If you feel like responding, all you have to do is pick up the handset and speak into it.}{如果想回复我们，只需要拿起对讲机说话就行。}{
    \Word{handset}{handset}{n.}{（电话）听筒；（对讲机）手柄}[ˈhændset]
}

\SentenceBlock[0:12:45]{Also, we're happy to remove the alcohol interlock device.}{而且我们很愿意帮你拆除酒精锁装置。}{
    \Word{interlock}{interlock}{n.}{联锁装置；连锁机构}[ˈɪntəlɒk]
}

\SentenceBlock[0:13:16]{You're in my house? What the hell are you doing inside my house? Patching shrapnel holes. Plus, there was a lot of broken glass to clean up.}{你们进我家？你们在我家里做了什么？修补榴弹碎片造成的孔。而且还有很多碎玻璃要清理。}{
    \Word{shrapnel}{shrapnel}{n.}{弹片；榴弹碎片}[ˈʃræpnəl]
}

\SentenceBlock[0:16:53]{In your first novel, we greatly admire the description of Lucasia's gown on page two.}{在你的第一本小说里，我们非常欣赏你在第2页对露卡西亚礼服的描写。}{
    \Word{gown}{gown}{n.}{礼服；长袍}[ɡaʊn]
}

\SentenceBlock[0:16:58]{``Gossamer threads of the finest shang silk shimmered like spun gold, as if the sun itself were showering Lucasia's shoulders with resplendent kisses.''}{“上好的商代丝绸像金丝一样闪闪发光，仿佛太阳在露卡西亚的肩上洒下灿烂的吻。”}{
    \Word{shimmered}{shimmer}{v.}{（微微）闪光；闪烁}[ˈʃɪmə]
    \Word{spun}{spin}{v.}{纺（丝/线）；纺成}[spɪn]
    \Word{resplendent}{resplendent}{adj.}{灿烂夺目的；辉煌的}[rɪˈsplendənt]
}

\SentenceBlock[0:17:12]{That made quite a few of us tingle.}{这带给我们很多人一阵激动。}{
    \Word{tingle}{tingle}{v.}{（因激动等）一阵发麻；刺痛}[ˈtɪŋɡl]
}

\SentenceBlock[0:17:48]{Wonderful. Have you read the first quarto of 1597?}{非常棒。你有读过1597年的初版四开本吗？}{
    \Word{quarto}{quarto}{n.}{四开本（书）；（尤指）早期四开本版本}[ˈkwɔːtəʊ]
}

\SentenceBlock[0:18:24]{Crazy Moira from Kansas City that sends me these dumb crocheted hats?}{住在堪萨斯城、送我钩针编织帽子的疯狂莫伊拉？}{
    \Word{crocheted}{crochet}{adj.}{钩编的；钩针织的}[ˈkrəʊʃeɪ]
}

\SentenceBlock[0:19:20]{Yeah, but you know what? Special dispensation this one time.}{是啊，不过你知道吗？这一次是特许。}{
    \Word{dispensation}{dispensation}{n.}{特许；豁免；（特殊）许可}[ˌdɪspənˈseɪʃən]
}

\SentenceBlock[0:23:39]{It wouldn't have happened if I had had the foresight to understand that you people are... generous enough to give me actual explosives, and I regret it.}{本来不会发生的，如果我提前知道你们这些人……慷慨到会给我真正的炸药，我就不会这样了；所以我很后悔。}{
    \Word{foresight}{foresight}{n.}{远见；先见之明}[ˈfɔːsaɪt]
}

\SentenceBlock[0:26:28]{The counselors there were some -- Some of the worst people I have ever known.}{那里的辅导员……是我见过最可怕的人之一。}{
    \Word{counselors}{counselor}{n.}{辅导员；顾问}[ˈkaʊnsələ]
}

\SentenceBlock[0:28:52]{What can I say? Sophomore year was tough.}{我能怎么办呢？做二年级生不容易啊。}{
    \Word{Sophomore}{sophomore}{n.}{（美）大学二年级学生；（高中）二年级生}[ˈsɒfəmɔː]
}

\SentenceBlock[0:29:12]{Yesterday, you people gave me a hand grenade. Are you seriously gonna begrudge me some H?}{昨天你们给了我手榴弹，现在却不情愿给我一点H（海洛因）吗？}{
    \Word{begrudge}{begrudge}{v.}{吝惜；舍不得给；对……心怀不满}[bɪˈɡrʌdʒ]
}

\SentenceBlock[0:29:17]{We have other opioids.}{我们还有其他类阿片。}{
    \Word{opioids}{opioid}{n.}{阿片类药物（镇痛药等）}[ˈəʊpiɔɪd]
}

\SentenceBlock[0:29:23]{Would oxycodone suffice? The closest unadulterated heroin is eight miles from here.}{羟考酮可以吗？离这里最近的纯海洛因有8英里。}{
    \Word{suffice}{suffice}{v.}{足够；足以}[səˈfaɪs]
    \Word{unadulterated}{unadulterated}{adj.}{纯的；未掺假的}[ˌʌnəˈdʌltəreɪtɪd]
}

\SentenceBlock[0:29:39]{Where are the hypodermic needles?}{皮下注射针在哪里？}{
    \Word{hypodermic}{hypodermic}{adj.}{皮下的；皮下注射用的}[ˌhaɪpəˈdɜːmɪk]
}

\SentenceBlock[0:29:41]{Might we suggest snorting the heroin instead?}{我们能建议你改成吸海洛因吗？}{
    \Word{snorting}{snort}{v.}{（把毒品）吸入鼻中}[snɔːt]
}

\SentenceBlock[0:33:56]{It's absolutely ineffectious.}{这绝对无效。}{
    \Word{ineffectious}{ineffectious}{adj.}{无效的；不起作用的}[ˌɪnɪˈfekʃəs]
}

\SentenceBlock[0:34:48]{Dark slipsand falling from his clothing, a shadowy figure.''}{黑暗的流沙自衣衫滑落，一个幽暗的魅影显形。}{
    \Word{shadowy}{shadowy}{adj.}{阴影重重的；朦胧的；可疑的}[ˈʃædəʊi]
}

\SentenceBlock[0:34:57]{``She slowly turned to face the raspy voice.''}{“她缓缓转身，朝那嘶哑的嗓音望去。”}{
    \Word{raspy}{raspy}{adj.}{（声音）沙哑的；刺耳的}[ˈrɑːspi]
}

\SentenceBlock[0:35:42]{How annoying is that chick.}{那女的有多烦人。}{
    \Word{chick}{chick}{n.}{（俚）小妞；姑娘}[tʃɪk]
}

\SentenceBlock[0:35:47]{Very, very fucking annoying. All smiley.}{非常、极其地烦人。总是面带微笑。}{
    \Word{smiley}{smiley}{adj.}{爱笑的；笑眯眯的}[ˈsmaɪli]
}

\SentenceBlock[0:36:00]{She's like. ``Oh, oh. We're the whole wide world, and we're stoked.}{她会说：“噢，噢。我们就是全世界，而且我们嗨到不行。}{
    \Word{stoked}{stoked}{adj.}{（俚）兴奋的；很嗨的；很开心的}[stəʊkt]
}

\SentenceBlock[0:39:54]{Well, It's currently 27.778 degrees Celsius, or 82 degrees Fahrenheit.}{现在是27.778摄氏度，或者华氏82度。}{
    \Word{Fahrenheit}{Fahrenheit}{n.}{华氏温标}[ˈfærənhaɪt]
}

\SentenceBlock[0:40:11]{Any chance of precipitation?}{有降雨的可能吗？}{
    \Word{precipitation}{precipitation}{n.}{降水；降雨}[prɪˌsɪpɪˈteɪʃən]
}



\end{document}
