\documentclass[11pt,a4paper]{article}
%% =========================================================
%% Theme options (default: Blue)
%% Usage: \usepackage[Indigo]{aiwordbook}
%% Available: Blue, Orange, Cyan, Indigo, Amber, Green, BlueGrey
%% =========================================================
\usepackage[Blue]{aiwordbook}

\title{Pluribus}
\subtitle{S01E01: We Is Us}

\date{}
\author{}

\begin{document}

\maketitle

\SentenceBlock[0:01:21]{It is this friggin' wide.}{它有这么大。}{
    \Word{friggin'}{frigging}{adj.}{该死的，讨厌的（用于强调）}[ˈfrɪɡɪn]
}

\SentenceBlock[0:01:23]{And it's periodic.}{还有规律。}{
    \Word{periodic}{periodic}{adj.}{周期性的；有规律的}[ˌpɪəriˈɒdɪk]
}

\SentenceBlock[0:01:35]{Something terrestrial, gotta be.}{肯定是地球上的信号。}{
    \Word{terrestrial}{terrestrial}{adj.}{地球的；陆地的}[təˈrestriəl]
}

\SentenceBlock[0:01:39]{Gee. I never thought to check that.}{就你厉害，以为我没想过核实吗？}{
    \Word{Gee}{gee}{interj.}{哎呀；天哪（表示惊讶、无奈等）}[dʒiː]
}

\SentenceBlock[0:03:24]{- Looks like a player piano. - So not binary but base four. Quaternary.}{- 看起来像钢琴。- 所以不是二进制，而是以四为底数：四进制。}{
    \Word{Quaternary}{quaternary}{adj.}{四进制的；以四为底的}[kwəˈtɜːnəri]
}

\SentenceBlock[0:05:29]{She paced the blood-soaked decks of the Mercator, looking for something, anything, that might take her mind off Raban.}{她在墨卡托号血流成河的甲板上踱步，寻找着东西——任何能让她忘记拉班的东西。}{
    \Word{blood-soaked}{blood-soaked}{adj.}{血浸的；血染的}[ˈblʌd səʊkt]
}

\SentenceBlock[0:05:36]{Ascending the forecastle, her gaze lingered over a bare-chested young sailor.}{她登上艏楼，目光停留在赤裸着上身的一名年轻水手身上。}{
    \Word{bare-chested}{bare-chested}{adj.}{赤裸上身的}[ˌbeəˈtʃestɪd]
}

\SentenceBlock[0:05:41]{On hands and knees he scrubbed, his sinewy forearms stretched taut as he washed away all trace of the day's fight.}{他跪在地上擦洗着，洗去今天战斗留下的所有痕迹；健壮的前臂绷得紧紧的。}{
    \Word{scrubbed}{scrub}{v.}{刷洗；擦洗}[skrʌb]
    \Word{sinewy}{sinewy}{adj.}{肌肉结实的；筋骨分明的}[ˈsɪnjuːi]
    \Word{forearms}{forearm}{n.}{前臂}[ˈfɔːrɑːm]
    \Word{taut}{taut}{adj.}{绷紧的；拉紧的}[tɔːt]
}

\SentenceBlock[0:05:48]{With a languid nod...}{她慵懒地一颔首……}{
    \Word{languid}{languid}{adj.}{慵懒的；无精打采的}[ˈlæŋɡwɪd]
}

\SentenceBlock[0:05:51]{Lucasia bade him follow to her cabin.}{露卡西亚示意他跟自己回船舱。}{
    \Word{bade}{bid}{v.}{吩咐；命令；示意}[bɪd]
}

\SentenceBlock[0:05:54]{Little did this callow deckhand know that serving at his captain's pleasure might take on such sweet meaning.}{这个初出茅庐的甲板水手几乎不知道，为他的船长效劳竟能有如此甜蜜的含义。}{
    \Word{deckhand}{deckhand}{n.}{甲板水手；船员}[ˈdekˌhænd]
    \Word{callow}{callow}{adj.}{稚嫩的；涉世未深的}[ˈkæləʊ]
}

\SentenceBlock[0:06:01]{Or, regrettably, that it would last but a single night.}{又或者，遗憾的是，这只能维持一夜。}{
    \Word{regrettably}{regrettably}{adv.}{遗憾地；可惜地}[rɪˈɡretəbli]
}

\SentenceBlock[0:06:08]{Later, at four bells, Lucasia stood by the mizzenmast.}{稍后，“四钟”响起时，露卡西亚站在后桅杆旁。}{
    \Word{mizzenmast}{mizzenmast}{n.}{后桅；后桅杆}[ˈmɪzənmɑːst]
}

\SentenceBlock[0:06:18]{She pulled her topcoat tighter, fingering its coarse wool as her thoughts flashed back to Raban.}{她将大衣裹得更紧，手指摩挲着粗糙的羊毛，思绪一下子闪回到拉班身上。}{
    \Word{coarse}{coarse}{adj.}{粗糙的；粗硬的}[kɔːs]
}

\SentenceBlock[0:06:33]{With that, Raban, proud, haughty Raban, mounted the plank and leaped from sight.}{说完，拉班——那个骄傲、傲慢的拉班——登上跳板一跃而出，瞬间消失。}{
    \Word{haughty}{haughty}{adj.}{傲慢的；自大的}[ˈhɔːti]
    \Word{plank}{plank}{n.}{（船上的）跳板；木板}[plæŋk]
}

\SentenceBlock[0:06:40]{The amaranthine slipsand closed over him, leaving nary a ripple.}{紫红色的流沙淹没了他，不留一丝涟漪。}{
    \Word{amaranthine}{amaranthine}{adj.}{苋红色的；紫红色的}[ˌæməˈrænθaɪn]
    \Word{slipsand}{slipsand}{n.}{流沙}[ˈslɪpsænd]
    \Word{nary}{nary}{adj.}{几乎不；一个也没有}[ˈneəri]
}

\SentenceBlock[0:06:58]{Attention, lovers of speculative historical romance literature, best-selling author Carol Sturka will now sign her new novel, ``Bloodsong of Wycaro,'' the fourth book in her ``Winds of Wycaro'' trilogy.}{各位推理历史兼浪漫文学的爱好者请注意：畅销作家卡萝尔·斯图尔卡将开始为新书签名，书名是《威卡罗的血歌》，是《威格罗之风》三部曲中的第四册。}{
    \Word{speculative}{speculative}{adj.}{推测的；臆测的}[ˈspekjələtɪv]
}

\SentenceBlock[0:08:45]{This is a authentic cutlass just like Raban's.}{这像拉班用的正宗短弯刀。}{
    \Word{cutlass}{cutlass}{n.}{短弯刀；弯刃军刀}[ˈkʌtləs]
}

\SentenceBlock[0:09:07]{And C: A small but very crucial point, as a two-masted schooner, the Mercator would not possess a mizzenmast. So...}{第三，问题不大但很重要的一点：作为双桅斯库纳船，墨卡托号不可能有一根后桅杆。所以……}{
    \Word{two-masted}{two-masted}{adj.}{双桅的}[ˌtuːˈmɑːstɪd]
    \Word{schooner}{schooner}{n.}{（通常为两桅的）纵帆船；斯库纳帆船}[ˈskuːnə]
    \Word{mizzenmast}{mizzenmast}{n.}{后桅；后桅杆}[ˈmɪzənmɑːst]
}

\SentenceBlock[0:09:40]{That was quite a send-off. I'm sorry, should I know who you are?}{刚才好多人送别啊。不好意思，我该认识你吗？}{
    \Word{send-off}{send-off}{n.}{送别；送行；欢送会}[ˈsend ɒf]
}

\SentenceBlock[0:10:33]{Help yourself. I think they're mostly glazed, but one box ought to be sprinkled, powdered and all that.}{随便挑。我觉得大多是糖霜的，不过有一盒应该有彩针、撒糖粉之类的。}{
    \Word{sprinkled}{sprinkle}{adj.}{撒了糖针（彩糖）的}[ˈsprɪŋkl]
}

\SentenceBlock[0:11:11]{Our team's fairly certain we've got a sequence that encodes for a lysogenic virus.}{我们团队相当确定，我们得到的是溶原性病毒的编码序列。}{
    \Word{lysogenic}{lysogenic}{adj.}{溶原性的}[ˌlaɪsəˈdʒenɪk]
}

\SentenceBlock[0:11:14]{Macaques, rabbits, mice...}{猕猴、兔子、小老鼠……}{
    \Word{Macaques}{macaque}{n.}{猕猴}[məˈkɑːk]
}

\SentenceBlock[0:11:16]{- Guinea pigs. - Guinea pigs. Now rats.}{- 豚鼠。- 豚鼠。现在是老鼠。}{
    \Word{Guinea}{Guinea}{n.}{几内亚（用于“guinea pig”指豚鼠）}[ˈɡɪni]
}

\SentenceBlock[0:11:26]{No clinical signs whatsoever. Put another way... we got bubkes.}{没有任何临床症状。换句话说……我们一无所获。}{
    \Word{bubkes}{bubkes}{n.}{（口）一无所有；屁也没有}[ˈbʌbkɪs]
}

\SentenceBlock[0:11:47]{I can put 'em to sleep if you wanna do the cardiac sticks.}{呃，你想做心脏注射的话，我可以让它们睡着。}{
    \Word{cardiac}{cardiac}{adj.}{心脏的}[ˈkɑːdiæk]
}

\SentenceBlock[0:13:22]{Keep it submerged.}{让水覆盖手。}{
    \Word{submerged}{submerged}{adj.}{浸没的；在水下的}[səbˈmɜːdʒd]
}

\SentenceBlock[0:15:36]{You've got skinny arms. Do you think you could maybe...}{你手臂比较细，可不可以帮我一下？}{
    \Word{skinny}{skinny}{adj.}{瘦的；细的}[ˈskɪni]
}

\SentenceBlock[0:21:04]{- You gonna leave me hanging here? - I do not clink glasses with fucking Diet Pepsi.}{- 你要让我空等吗？- 我才不和该死的无糖百事可乐碰杯。}{
    \Word{clink}{clink}{v.}{（使）碰杯；（使）叮当作响}[klɪŋk]
}

\SentenceBlock[0:21:13]{You endure it, you do not toast it.}{你只能忍受，而不是庆祝。}{
    \Word{toast}{toast}{v.}{为……举杯；祝酒；庆祝}[təʊst]
}

\SentenceBlock[0:21:45]{And the world needed yet another female character who spends all her time mooning over some fucking proud and haughty pirate.}{这个世界还需要另一个女主角，成天痴痴地看着某个傲慢自大的海盗。}{
    \Word{haughty}{haughty}{adj.}{傲慢的；自大的}[ˈhɔːti]
}

\SentenceBlock[0:21:50]{He's a corsair, not a pirate.}{他是私掠者，不是海盗。}{
    \Word{corsair}{corsair}{n.}{私掠者；海上掠夺者}[ˈkɔːseə]
}

\SentenceBlock[0:21:57]{It's like a bad episode of Star Trek.}{就像《星际争霸战》被拍烂了一样。}{
    \Word{Trek}{Trek}{n.}{（专名）《星际迷航》（Star Trek）}[trek]
}

\SentenceBlock[0:21:59]{So how about you throw everybody a changeup?}{那不如给读者来点改变？}{
    \Word{changeup}{changeup}{n.}{（棒球）变速球；（比喻）变招，变化}[ˈtʃeɪndʒʌp]
}

\SentenceBlock[0:23:19]{To Raban. Proud, haughty Raban.}{敬拉班。傲慢自大的拉班。}{
    \Word{haughty}{haughty}{adj.}{傲慢的；自大的}[ˈhɔːti]
}

\SentenceBlock[0:23:56]{Are you trying to start a forest fire? Stop wasting my butane.}{你想烧光一片森林吗？别浪费我的丁烷。}{
    \Word{butane}{butane}{n.}{丁烷}[ˈbjuːteɪn]
}

\SentenceBlock[0:24:06]{- That's etiquette. - Yeah? On a plane, do you put your own oxygen mask on first?}{- 这是礼貌。- 是吗？在飞机上，你不也先给自己戴氧气罩吗？}{
    \Word{etiquette}{etiquette}{n.}{礼仪；礼节}[ˈetɪkət]
}

\SentenceBlock[0:24:23]{- 16, 17 exclamation points. - Wow.}{- 16、17个感叹号。- 哇。}{
    \Word{exclamation}{exclamation}{n.}{感叹；感叹号}[ˌekskləˈmeɪʃən]
}

\SentenceBlock[0:24:27]{``Spoiler alert, Raban is back and yummier that ever.''}{“警告有剧透：拉班以更精彩的姿势回归。”}{
    \Word{yummier}{yummy}{adj.}{更美味的；更诱人的（口）}[ˈjʌmi]
}

\SentenceBlock[0:24:37]{``I'd walk his plank any time.''}{我随时能和他在甲板上做。”}{
    \Word{plank}{plank}{n.}{（船上的）跳板；木板}[plæŋk]
}

\SentenceBlock[0:24:39]{I'm sensing a nautical motif.}{似乎跟航海主题有关。}{
    \Word{nautical}{nautical}{adj.}{航海的；海事的}[ˈnɔːtɪkəl]
    \Word{motif}{motif}{n.}{主题；母题；反复出现的意象}[məʊˈtiːf]
}

\SentenceBlock[0:26:21]{Someone with dreadlocks. Hip it up.}{有脏辫的那种，搞点刺激的嘛。}{
    \Word{dreadlocks}{dreadlocks}{n.}{脏辫；雷鬼辫}[ˈdredlɒks]
}

\SentenceBlock[0:48:55]{This must be so bewildering for you.}{这些事一定让你感到很困惑。}{
    \Word{bewildering}{bewildering}{adj.}{令人困惑的；让人不知所措的}[bɪˈwɪldərɪŋ]
}

\SentenceBlock[0:49:02]{Especially Helen's passing. Please know none of that was intentional.}{尤其是海伦过世。请理解这些不是有意而为之。}{
    \Word{intentional}{intentional}{adj.}{故意的；有意的}[ɪnˈtenʃənl]
}

\SentenceBlock[0:49:06]{All the death and destruction you witnessed tonight. Especially Helen's passing. Please know none of that was intentional. You have our deepest condolences.}{今晚你所目睹的死亡和破坏，尤其是海伦过世。请理解这些不是有意而为之；对此，我们深表遗憾。}{
    \Word{condolences}{condolence}{n.}{哀悼；慰问；吊唁}[kənˈdəʊləns]
}

\SentenceBlock[0:49:18]{Your well-being is of utmost importance to us.}{你的健康快乐对我们来说至关重要。}{
    \Word{utmost}{utmost}{adj.}{最重要的；极度的}[ˈʌtməʊst]
}

\SentenceBlock[0:51:15]{We are, however, beneficiaries of extraterrestrial technology.}{然而，我们是外星科技的受益者。}{
    \Word{extraterrestrial}{extraterrestrial}{adj.}{地外的；外星的}[ˌekstrətəˈrestriəl]
}

\SentenceBlock[0:51:20]{Fourteen months ago, astronomers discovered a radio signal from 600 light-years away.}{14个月前，天文学家发现了无线电信号：从600光年之外发送的。}{
    \Word{astronomers}{astronomer}{n.}{天文学家}[əˈstrɒnəmə]
}

\SentenceBlock[0:51:40]{It's a recipe, it turns out, for a nucleotide sequence.}{后来证明，那是一个核苷酸序列的配方。}{
    \Word{nucleotide}{nucleotide}{n.}{核苷酸}[ˈnjuːklɪətaɪd]
}

\SentenceBlock[0:51:48]{It is not a living thing, per se. It is more akin to a virus.}{本质上，它不是生物，更像是一种病毒。}{
    \Word{akin}{akin}{adj.}{类似的；同类的}[əˈkɪn]
}

\SentenceBlock[0:54:27]{We are not here in our sweatpants screening your call.}{我们不在这里穿着运动裤接听你的电话。}{
    \Word{sweatpants}{sweatpants}{n.}{运动裤}[ˈswetpænts]
}



\end{document}
