\documentclass[11pt,a4paper]{article}
%% =========================================================
%% Theme options (default: Blue)
%% Usage: \usepackage[Indigo]{aiwordbook}
%% Available: Blue, Orange, Cyan, Indigo, Amber, Green, BlueGrey
%% =========================================================
\usepackage[Orange]{aiwordbook}

\title{Pluribus}
\subtitle{S01E02: Pirate Lady}

\date{}
\author{}

\begin{document}

\maketitle

\SentenceBlock[0:12:19]{Sorry, we didn't mean to startle you. We wouldn't have intruded but, if you don't mind us saying, maybe you could slow down and take a break.}{抱歉，我们不是有意吓着你。我们本不该过问，可是冒昧地说两句：或许你该缓一缓，休息一下。}{
    \Word{startle}{startle}{v.}{使受惊，吓一跳}[ˈstɑːt(ə)l]
    \Word{intruded}{intrude}{v.}{闯入；侵扰；打扰}[ɪnˈtruːd]
}

\SentenceBlock[0:12:40]{- An MQ-9 Reaper. - A what?}{- 是MQ-9死神。- 什么？}{
    \Word{Reaper}{reaper}{n.}{收割者；（此处）“死神”（代称）}[ˈriːpə]
}

\SentenceBlock[0:13:07]{Please? We'd feel so much better if you'd hydrate.}{喝水吧？你喝口水的话，我们比较放心。}{
    \Word{hydrate}{hydrate}{v.}{（给……）补充水分；（使）补水}[haɪˈdreɪt]
}

\SentenceBlock[0:13:56]{Regardless, you are on the verge of heat exhaustion, and that's the opinion of every medical doctor on Earth.}{无论如何，你已经接近中暑了；这是地球上所有医生的看法。}{
    \Word{verge}{verge}{n.}{边缘；关头}[vɜːdʒ]
    \Word{exhaustion}{exhaustion}{n.}{精疲力竭；衰竭}[ɪɡˈzɔːstʃən]
}

\SentenceBlock[0:15:13]{You're gonna need a pickax by the way.}{顺便提一句，你可能需要十字镐。}{
    \Word{pickax}{pickaxe}{n.}{十字镐；鹤嘴锄}[ˈpɪkæks]
}

\SentenceBlock[0:16:50]{You bunch of ghouls!}{你们这群食尸鬼！}{
    \Word{ghouls}{ghoul}{n.}{食尸鬼；（引申）令人作呕的人}[ɡuːl]
}

\SentenceBlock[0:25:44]{Missile silos? Area 51?}{导弹发射井？51区？}{
    \Word{silos}{silo}{n.}{（导弹）发射井；（亦指）筒仓}[ˈsaɪləʊ]
}

\SentenceBlock[0:26:17]{There was just one minor injury. Mostly there was consternation.}{有一位受了轻伤。大部分是极度震惊。}{
    \Word{consternation}{consternation}{n.}{惊惶；震惊；慌乱}[ˌkɒnstəˈneɪʃən]
}

\SentenceBlock[0:34:34]{Anything capable of blowing up the world needs to have some heft to it, don't you think?}{那些能炸毁世界的东西，总得有点分量吧？同意吗？}{
    \Word{heft}{heft}{n.}{分量；重量；（引申）影响力}[heft]
}

\SentenceBlock[0:35:16]{You can all just go wait out on the tarmac.}{你们可以去停机坪等着。}{
    \Word{tarmac}{tarmac}{n.}{停机坪；柏油路面}[ˈtɑːmæk]
}

\SentenceBlock[0:36:24]{Actually, if you recall, Harrison Ford never rode in the escape pod which I thought was a clever gambit.}{其实，回想一下的话，哈里逊·福特从来没有用逃生舱；我觉得这是很聪明的策略。}{
    \Word{gambit}{gambit}{n.}{策略；（棋/牌）开局弃子；（手段）}[ˈɡæmbɪt]
}

\SentenceBlock[0:38:36]{The automobile crashed, and my grandfather died.}{结果出了车祸，我爷爷死了。}{
    \Word{automobile}{automobile}{n.}{汽车}[ˈɔːtəməbiːl]
}

\SentenceBlock[0:41:10]{Apparently, when it came to the lions and the tigers, they suffered quite a few maulings.}{据说他们在放狮子老虎时，遭受了很多撕咬伤。}{
    \Word{maulings}{mauling}{n.}{（猛兽的）撕咬伤；袭击伤}[ˈmɔːlɪŋ]
}

\SentenceBlock[0:42:54]{Because I'm smart enough to know you don't ask a drug dealer to describe their heroin.}{因为我足够聪明，知道不该让贩毒者去形容他们的海洛因。}{
    \Word{heroin}{heroin}{n.}{海洛因}[ˈherəʊɪn]
}

\SentenceBlock[0:43:11]{Who's hungry? I, myself, am famished.}{有人饿吗？我自己快饿死了。}{
    \Word{famished}{famished}{adj.}{极饿的；饥肠辘辘的}[ˈfæmɪʃt]
}

\SentenceBlock[0:44:11]{We searched a wide radius, but the only lobster currently available is live.}{我们搜索了大范围，但目前唯一能找到的龙虾是活的。}{
    \Word{radius}{radius}{n.}{半径；范围}[ˈreɪdiəs]
    \Word{lobster}{lobster}{n.}{龙虾}[ˈlɒbstə]
}

\SentenceBlock[0:45:01]{What if I wanted escargot? Surely you can kill snails.}{如果我想吃法国蜗牛呢？杀蜗牛不成问题吧。}{
    \Word{escargot}{escargot}{n.}{（法式菜）蜗牛}[ˈeskɑːɡəʊ]
}

\SentenceBlock[0:45:38]{They won't step on a bug, but they'll enslave an entire planet.}{他们不会踩虫子，但他们会奴役整个星球。}{
    \Word{enslave}{enslave}{v.}{使为奴；奴役}[ɪnˈsleɪv]
}

\SentenceBlock[0:45:45]{Our joining is very much the antithesis of slavery.}{我们的加入完全是奴隶制的反义词。}{
    \Word{antithesis}{antithesis}{n.}{对立面；完全相反的人（或事物）}[ænˈtɪθəsɪs]
}

\SentenceBlock[0:46:10]{For us, it's a biological imperative. Like breathing.}{对我们来说，这是生物本能，就像呼吸一样。}{
    \Word{imperative}{imperative}{n.}{必要性；迫切需要；（尤指）必须做的事}[ɪmˈperətɪv]
}

\SentenceBlock[0:46:37]{For a pelvic exam, what kind of speculum do you prefer, metal or plastic?}{做盆腔检查时，你喜欢用哪种窥器：金属的还是塑料的？}{
    \Word{pelvic}{pelvic}{adj.}{骨盆的}[ˈpelvɪk]
    \Word{speculum}{speculum}{n.}{窥器（医学器械）}[ˈspekjʊləm]
}

\SentenceBlock[0:46:48]{But, I mean, you probably wouldn't do a palpation, right?}{可是，我的意思是，你应该不会做触诊，对吧？}{
    \Word{palpation}{palpation}{n.}{触诊}[pælˈpeɪʃən]
}

\SentenceBlock[0:48:20]{Or say I procured a chicken or a pig, and I myself did the...}{又或者说我弄来一只鸡或一头猪，然后亲自宰……}{
    \Word{procured}{procure}{v.}{取得；弄到；（设法）获得}[prəˈkjʊə]
}

\SentenceBlock[0:49:07]{-I'm going home. -Good riddance.}{-我要回家。-走得好。}{
    \Word{riddance}{riddance}{n.}{摆脱；甩掉（尤用于Good riddance）}[ˈrɪdəns]
}

\SentenceBlock[0:49:38]{Go to the Guggenheim, Disneyland Paris, wherever else these whacked-out Moonies take you next.}{去参观古根海姆、巴黎迪士尼乐园吧；这些有病的邪教信徒接下来带你们去哪儿，你们就去哪儿。}{
    \Word{whacked-out}{whacked-out}{adj.}{古怪的；疯疯癫癫的}[ˌwæktˈaʊt]
    \Word{Moonies}{Moonie}{n.}{“统一教”教徒（对该教成员的俗称）}[ˈmuːni]
}

\SentenceBlock[0:49:46]{You are traitors to the human race!}{你们是人类的叛徒！}{
    \Word{traitors}{traitor}{n.}{叛徒；背叛者}[ˈtreɪtə]
}

\SentenceBlock[0:50:17]{Get the fuck off me! You fucking freaks!}{给我放开！你们这些该死的怪物！}{
    \Word{freaks}{freak}{n.}{怪人；怪物；（粗）令人厌恶的家伙}[friːk]
}

\SentenceBlock[0:52:59]{We flew it in for you. And your favorite crispy brioche from Les Crayères.}{我们给你空运过来了。还有你最爱的——来自Les Crayères的酥脆奶油蛋卷。}{
    \Word{brioche}{brioche}{n.}{布里欧修（黄油甜面包）}[ˈbriːɒʃ]
}

\SentenceBlock[0:54:53]{I will occupy the penthouse of Mr. Elvis Presley.}{我会住在艾维斯·普雷斯利先生的顶层公寓。}{
    \Word{penthouse}{penthouse}{n.}{空中别墅}[ˈpenthaʊs]
}

\SentenceBlock[0:54:58]{Some say it is haunted by his ghost. This intrigues me.}{有些人说那里闹鬼，是他的幽灵在徘徊。这让我特别感兴趣。}{
    \Word{haunted}{haunt}{adj.}{闹鬼的；（地方）常有鬼魂出没的}[ˈhɔːntɪd]
    \Word{intrigues}{intrigue}{v.}{使着迷；引起……的兴趣}[ɪnˈtriːɡ]
}

\SentenceBlock[0:55:19]{Who's Zosia? Your chaperone.}{谁是佐西亚？你的随行监护。}{
    \Word{chaperone}{chaperone}{n.}{（尤指年轻女性外出时的）监护人；陪同者}[ˈʃæpərəʊn]
}

\SentenceBlock[0:56:06]{They are a bunch of brain-damaged incompetents but you keep sticking your dick in them.}{她们是一群脑子受损、毫无能力的家伙，你却一直往她们里面塞老二。}{
    \Word{incompetents}{incompetent}{n.}{无能者；不称职的人}[ɪnˈkɒmpɪtənt]
}

\SentenceBlock[0:56:29]{Have I behaved in an untoward fashion?}{我的行为是否逾矩？}{
    \Word{untoward}{untoward}{adj.}{不妥的；不当的；不合礼数的}[ʌnˈtɔːd]
}

\SentenceBlock[0:57:02]{Casanova McBoner here wants you to join his harem, which is hunky-dory with you, provided I give you my permission?}{花花公子麦大屌要你加入他的后宫，只要我允许的话，你就欣然接受？}{
    \Word{harem}{harem}{n.}{后宫；（一夫多妻制下的）妻妾群}[ˈhɑːriːm]
    \Word{hunky-dory}{hunky-dory}{adj.}{一切顺利的；没问题的}[ˌhʌŋki ˈdɔːri]
}

\SentenceBlock[0:57:17]{- And I'm what, your pimp? - That is completely uncalled for.}{- 然后我是什么，龟公吗？- 这话完全是多余的。}{
    \Word{pimp}{pimp}{n.}{皮条客；拉皮条的人}[pɪmp]
    \Word{uncalled}{uncalled}{adj.}{不必要的；不合适的}[ʌnˈkɔːld]
}


\end{document}
