\documentclass[11pt,a4paper]{article}
%% =========================================================
%% Theme options (default: Blue)
%% Usage: \usepackage[Indigo]{aiwordbook}
%% Available: Blue, Orange, Cyan, Indigo, Amber, Green, BlueGrey
%% =========================================================
\usepackage[Cyan]{aiwordbook}

\title{Pluribus}
\subtitle{S01E03: Grenade}

\date{}
\author{}

\begin{document}

\maketitle

\SentenceBlock[0:00:56]{The cold stimulates ancient nerves. It makes you feel a primal connection to the world.}{寒冷会刺激年代久远的神经，让你感受到与世界的原始联系。}{
    \Word{primal}{primal}{adj.}{原始的，本能的}[ˈpraɪməl]
}

\SentenceBlock[0:01:32]{We have different artists and artisans help us build again each year, so every stay is truly once in a lifetime.}{每年我们会邀请不同的艺术家和工匠帮我们重建，所以每一次住宿都真的是一生一次的体验。}{
    \Word{artisans}{artisan}{n.}{工匠，手艺人}[ˌɑːtɪˈzæn]
}

\SentenceBlock[0:01:52]{The Koi Suite. Wow. It's brisk. Our guest suites are slightly warmer than the rest of the hotel.}{锦鲤套房。哇，挺清凉的。比起酒店其他地方，客房会稍微温暖一点。}{
    \Word{brisk}{brisk}{adj.}{（天气）清凉的，寒爽的}[brɪsk]
}

\SentenceBlock[0:02:04]{It's quite invigorating once you get used to it.}{一旦习惯了，就会觉得很提神、很有活力。}{
    \Word{invigorating}{invigorating}{adj.}{使人精神振奋的，提神的}[ɪnˈvɪɡəreɪtɪŋ]
}

\SentenceBlock[0:02:12]{As we say, you will feel som plommen i egget. Like a yolk in an egg.}{用我们的话说，就是会感觉……如鱼得水。}{
    \Word{yolk}{yolk}{n.}{（蛋）蛋黄}[jəʊk]
}

\SentenceBlock[0:02:34]{And I highly recommend trying our complimentary house brandy.}{而且我强力推荐你们尝尝我们免费赠送的自制白兰地。}{
    \Word{brandy}{brandy}{n.}{白兰地}[ˈbrændi]
}

\SentenceBlock[0:03:45]{I mean, do we absolutely have to go every wacky place Rick Steves recommends?}{我是说，我们一定要去瑞克·史蒂夫斯介绍的每个古怪的地方吗？}{
    \Word{wacky}{wacky}{adj.}{古怪的，离奇的}[ˈwæki]
}

\SentenceBlock[0:08:04]{And between the two of them, they've piloted every variant of this capable and trustworthy Airbus A330 aircraft.}{这两人也驾驶过这款性能出色、可靠可信的空客A330飞机的每一种型号。}{
    \Word{variant}{variant}{n.}{变体；不同版本/型号}[ˈveəriənt]
}

\SentenceBlock[0:08:18]{- That's an affirmative, Carol. - Please stop that.}{- 你说得对，卡萝尔。- 让他别再说了。}{
    \Word{affirmative}{affirmative}{adj.}{肯定的；（无线电用语）确认/收到}[əˈfɜːmətɪv]
}

\SentenceBlock[0:08:22]{It's much more spacious up in first class.}{头等舱的位子更宽敞。}{
    \Word{spacious}{spacious}{adj.}{宽敞的， простор的}[ˈspeɪʃəs]
}

\SentenceBlock[0:08:57]{Back in Spain, that was all the English speakers, right? Anyone with conversational ability, yes.}{那些在西班牙见到的，是所有能说英语的人，对吧？没错，任何具备会话能力的都去了。}{
    \Word{conversational}{conversational}{adj.}{会话的；适于交谈的}[ˌkɒnvəˈseɪʃənl]
}

\SentenceBlock[0:09:05]{Well, let's see. There's Bora Colak, a 68-year-old candy vendor in Istanbul.}{好吧，让我看看。有个住在伊斯坦布尔、68岁卖糖的博拉·乔拉克。}{
    \Word{vendor}{vendor}{n.}{小贩，摊贩}[ˈvendə]
}

\SentenceBlock[0:09:16]{In Bali, there's Ida Ayu Dewi. Twenty-three. Speaks Indonesian Balinese. She's a contortionist and a dancer.}{有个住在巴厘岛的伊达·阿玉·德维，23岁，会说印尼语和巴厘语。她是柔身术演员兼舞蹈家。}{
    \Word{contortionist}{contortionist}{n.}{柔术演员；柔身术表演者}[kənˈtɔːʃənɪst]
}

\SentenceBlock[0:09:20]{Performs the Barong, the Legong Jobog. It's all quite exquisite.}{会表演巴厘传统舞蹈巴戎舞、蕾贡乔波舞；都非常精致。}{
    \Word{exquisite}{exquisite}{adj.}{精致的；精美的}[ɪkˈskwɪzɪt]
}

\SentenceBlock[0:09:54]{He sings the call to prayer. He has a powerful tenor voice. He also loves cats.}{他颂唱礼拜宣礼词，有一副强而有力的男高音嗓子。他也很爱猫。}{
    \Word{tenor}{tenor}{n.}{男高音；（声音）男高音音域}[ˈtenə]
}

\SentenceBlock[0:17:15]{One day I got up the courage to go up to Mean Old Lady Hickenlooper and ask her why she always frowned.}{有天我鼓起勇气走向刻薄老妇希肯卢珀，问她为什么总是皱着眉头。}{
    \Word{frowned}{frown}{v.}{皱眉，蹙眉}[fraʊn]
}

\SentenceBlock[0:18:55]{You were very complimentary of the chef that morning. It really stuck with her. - The sorghum flour pancakes-- - So you took it upon yourself to make me breakfast? }{那天早上你对厨师称赞有加，她至今没忘。- 用高粱面粉做的煎饼—— - 所以你就自作主张，帮我做早餐？}{
    \Word{sorghum}{sorghum}{n.}{高粱}[ˈsɔːɡəm]
}

\SentenceBlock[0:19:03]{Well, we knew your fridge was pretty bare. You've only got tonic water, half a carton of oat milk, a jar of green olives, a jar of black olives, a jar of red olives--}{我们知道你冰箱里没什么东西。你只有汤力水、半盒燕麦牛奶，绿橄榄、黑橄榄、红橄榄各一罐——}{
    \Word{carton}{carton}{n.}{纸盒；（尤指）牛奶/果汁纸盒}[ˈkɑːtən]
}

\SentenceBlock[0:21:39]{I am a very independent person. Okay? I always have been. I fend for myself. I just want my Sprouts back.}{我是个非常独立的人，好吗？一直如此。我能照顾自己。我只想要我的 Sprouts 回来。}{
    \Word{fend}{fend}{v.}{自力更生；照料（自己）}[fend]
}

\SentenceBlock[0:24:02]{May we sneak past you here?}{我们可以从这里悄悄借过一下吗？}{
    \Word{sneak}{sneak}{v.}{偷偷地走；溜过去}[sniːk]
}

\SentenceBlock[0:25:18]{- We'll get it... - ...to you toot sweet.}{- 我们会把它……- ……立刻送到你那儿。}{
    \Word{toot}{toot sweet}{adv.}{立刻，马上（口语，源自法语 \,tout de suite）}[tuːt swiːt]
}

\SentenceBlock[0:28:19]{There is nothing wrong with me that a fucking hand grenade wouldn't fix.}{没有什么问题，是一颗该死的手榴弹解决不了的。}{
    \Word{grenade}{grenade}{n.}{手榴弹}[ɡrəˈneɪd]
}

\SentenceBlock[0:29:29]{It must've just been the excitement of the moment, but they said the only way to prevent the eruption was for me to crawl through their legs, up the volcano, while they gave me my birthday whacks.}{一定只是一时激动，不过他们说唯一能防止爆发的办法，是我从他们胯下爬过，再爬上火山，同时他们按生日习俗拍打我。}{
    \Word{eruption}{eruption}{n.}{（火山）喷发；爆发}[ɪˈrʌpʃən]
    \Word{whacks}{whack}{n.}{猛击；（此处）拍打几下}[wæk]
}

\SentenceBlock[0:30:26]{We thought you were probably being sarcastic, but we didn't want to take the chance.}{我们觉得你应该是在讽刺，但我们不想冒这个险。}{
    \Word{sarcastic}{sarcastic}{adj.}{讽刺的，挖苦的}[sɑːˈkæstɪk]
}

\SentenceBlock[0:30:56]{Do you maniacs drink?}{你们这些疯子喝酒吗？}{
    \Word{maniacs}{maniac}{n.}{疯子；狂热者}[ˈmeɪniæk]
}

\SentenceBlock[0:32:49]{It's a hard thing to predict. Scientific advances tend to ebb and flow.}{这个很难预测。科学进步往往有起有落。}{
    \Word{ebb}{ebb}{v.}{衰退；减弱}[eb]
}

\SentenceBlock[0:33:17]{Sorry, Carol. We have a biological imperative.}{抱歉，卡萝尔。这是我们的生物本能。}{
    \Word{imperative}{imperative}{n.}{迫切需要；必然要求}[ɪmˈperətɪv]
}

\SentenceBlock[0:34:23]{Actually, let me guess. It's... it's all beautiful scenery, and you feel nothing but contentment.}{其实，让我来猜猜吧。你们眼前全是美丽的风景，除了满足感，你们没有其他感受。}{
    \Word{contentment}{contentment}{n.}{满足；知足}[kənˈtentmənt]
}

\SentenceBlock[0:34:26]{Just wave after wave of bliss and peace and everything is perfect. It's like living inside a postcard, every second of every day.}{只有一波又一波的幸福与安宁，一切都这么完美。就好像每天时时刻刻住在一张明信片里。}{
    \Word{bliss}{bliss}{n.}{极乐；幸福感}[blɪs]
}

\SentenceBlock[0:34:59]{Or you're taking a walk at sunset on the most flawless beach in Croatia.}{又好比说，日落时分你在克罗地亚最完美无瑕的海滩上散步。}{
    \Word{flawless}{flawless}{adj.}{完美无瑕的}[ˈflɔːləs]
}

\SentenceBlock[0:38:26]{There was some blood loss, but no real nerve damage. She did get a pretty severe concussion that we're gonna wanna keep an eye on.}{她有些出血情况，但没伤到任何神经。她确实有严重的脑震荡，我们会密切留意观察的。}{
    \Word{concussion}{concussion}{n.}{脑震荡}[kənˈkʌʃən]
}

\SentenceBlock[0:39:19]{And the thing a bazooka shoots? A rocket, or whatever.}{还有火箭筒发射的东西？火箭弹什么的。}{
    \Word{bazooka}{bazooka}{n.}{（俗称）火箭筒}[bəˈzuːkə]
}

\SentenceBlock[0:40:05]{You gave me a grenade, for fuck's sake. It'd be okay to say no at this point. That would be sane. Not utterly batshit crazy.}{你们给了我手榴弹啊，我的天。到了这个时候，你们拒绝我也完全没问题；那才是明智的，而不是彻底疯到离谱。}{
    \Word{sane}{sane}{adj.}{理智的，清醒的}[seɪn]
}


\end{document}
