\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Echo Valley}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:02:45]{I had to leave super early this morning to drop off some saddles.}{我今天早上不得不很早离开去送一些马鞍}{
    \Word{saddle}{n.}{马鞍}
}
\SentenceBlock[0:04:08]{You see the dips? Those rafters could collapse any day now.}{看到那些凹陷处吗 椽子随时都可能坍塌}{
    \Word{rafter}{n.}{椽子}
}
\SentenceBlock[0:04:15]{Well, if you stick with the shingles,you're looking at around \$9,000.}{如果你还是用沥青瓦那大概要九千美元左右}{
    \Word{shingle}{n.}{屋顶板}
}
\SentenceBlock[0:05:11]{Come on, sweetie. We got to hustle.}{来吧 宝宝 我们得快点了}{
    \Word{hustle}{v.}{赶紧}
}
\SentenceBlock[0:05:13]{I'm coming, I'm coming. Geez, Mom.}{我来了 天 妈妈}{
    \Word{geez}{int.}{哎呀}
}
\SentenceBlock[0:06:14]{You know, I ran into Kathy Dumont at the club.}{你知道 我在俱乐部遇到凯西杜蒙}{
    \Word{Dumont}{n.}{杜蒙（人名）}
}
\SentenceBlock[0:07:21]{when we sat down with the counselor, do you remember?}{见律师的时候 记得吗}{
    \Word{counselor}{n.}{顾问；辅导员}
}
\SentenceBlock[0:09:20]{Splash. Fish food.}{噗的一声入水 变鱼食}{
    \Word{splash}{n.}{溅落声}
}
\SentenceBlock[0:09:33]{He is probably freaking the fuck out right now.}{他现在大概正慌呢}{
    \Word{freak}{v.}{惊慌}
}
\SentenceBlock[0:09:47]{Well, that's what happens when you send dick pics to skanks}{当着女友面给贱货们发老二照片}{
    \Word{skank}{n.}{荡妇}
}
\SentenceBlock[0:09:52]{I am going. Sprinting.}{我会的 这就去分}{
    \Word{sprint}{v.}{冲刺}
}
\SentenceBlock[0:11:06]{The ghost of Marsh Creek Lake.}{玛什溪湖之鬼魂}{
    \Word{creek}{n.}{小溪}
}
\SentenceBlock[0:15:05]{Okay, do you guys want me to do a front flip or a backflip?}{好了 你们要看我前空翻还是后空翻}{
    \Word{backflip}{n.}{后空翻}
}
\SentenceBlock[0:15:12]{You have to pinkie promise, okay?}{拉钩发誓好吗}{
    \Word{pinkie}{n.}{小指}
}
\SentenceBlock[0:19:16]{I was just commentating on how beautiful it is out here.}{我刚才只是在感叹这一区景色优美}{
    \Word{commentate}{v.}{评论}
}
\SentenceBlock[0:19:56]{your junkie daughter has two choices.}{你的毒虫女儿有两个选择}{
    \Word{junkie}{n.}{瘾君子}
}
\SentenceBlock[0:22:20]{Narcan. You know what?}{纳洛酮 这样吧}{
    \Word{Narcan}{n.}{纳洛酮（解毒剂）}
}
\SentenceBlock[0:22:26]{in case you OD again.}{以防你又吸毒过量}{
    \Word{OD}{v.}{吸毒过量}
}
\SentenceBlock[0:22:53]{I pledge allegiance to neglect my daughter,}{我保证会对女儿不管不顾}{
    \Word{allegiance}{n.}{忠诚}
}
\SentenceBlock[0:26:38]{Oh, God, she's still an awful old cunt.}{噢 老天 她还是那么贱}{
    \Word{cunt}{n.}{贱人（粗俗侮辱语）}
}
\SentenceBlock[0:28:09]{I don't know, get drunk as skunks}{不知道 醉得稀巴烂}{
    \Word{skunk}{n.}{臭鼬；酒鬼（俚语）}
}
\SentenceBlock[0:28:12]{and laugh our tits off just like old times.}{然后笑得前仰后合 像以前一样}{
    \Word{tits}{n.}{乳房（粗俗用法）}
}
\SentenceBlock[0:28:46]{Do you remember the time Patty served it on a silver platter?}{你还记得那次帕蒂用银餐盘装纯素火鸡吗}{
    \Word{platter}{n.}{大浅盘}
}
\SentenceBlock[0:28:58]{The last time we talked, she was back in rehab.}{我们上次聊的时候 她回去戒毒了}{
    \Word{rehab}{n.}{戒毒所}
}
\SentenceBlock[0:29:18]{You're grieving, you lost Patty.}{你还在哀悼中 你失去了帕蒂}{
    \Word{grieve}{v.}{悲伤}
}
\SentenceBlock[0:46:56]{He came up to me and he jammed a gun right under my chin.}{他走到我跟前 用枪顶着我的下巴}{
    \Word{chin}{n.}{下巴}
}
\SentenceBlock[0:50:03]{Change your diagonal.}{换边起落}{
    \Word{diagonal}{n.}{对角线}
}
\SentenceBlock[0:57:41]{I lost my ring on our honeymoon.}{我在蜜月期间弄丢了戒指}{
    \Word{honeymoon}{n.}{蜜月}
}
\SentenceBlock[0:57:45]{My wife was ready to strangle me.}{我妻子差点掐死我}{
    \Word{strangle}{v.}{掐死}
}
\SentenceBlock[1:02:49]{We found Les and another female in the barn.}{我们在谷仓找到了莱斯和另一名女性}{
    \Word{barn}{n.}{谷仓}
}
\SentenceBlock[1:02:59]{Well, we heard moaning of a sexual nature.}{我们听到了有性意味的呻吟声}{
    \Word{moan}{v.}{呻吟}
}
\SentenceBlock[1:03:32]{so he set fire to the hayloft one night, trying to make it look like an accident}{所以有天晚上 他放火烧了草棚想假装成事故}{
    \Word{hayloft}{n.}{干草棚}
}
\SentenceBlock[1:03:53]{Looks like I'll be doing the chores myself tomorrow morning.}{看来我明早得自己干活了}{
    \Word{chore}{n.}{杂务}
}
\SentenceBlock[1:06:53]{But he gets impatient and he cuts the drugs with fentanyl to stretch it,}{但他心太急 在毒品里混了芬太尼充数}{
    \Word{fentanyl}{n.}{芬太尼}
}
\SentenceBlock[1:08:09]{Right now, no one's searching for some fucking missing dope addict}{现在 没有人在搜寻某个失踪的毒虫}{
    \Word{dope}{n.}{毒品}
    \Word{addict}{n.}{瘾君子}
}
\SentenceBlock[1:14:38]{He used a flare.}{他用了一个燃烧棒}{
    \Word{flare}{n.}{照明弹}
}
\SentenceBlock[1:14:54]{but when the fire marshal found it, he knew it was set intentionally.}{但消防员发现的时候就知道是有人故意点火的}{
    \Word{marshal}{n.}{消防队长}
}
\SentenceBlock[1:15:30]{Hay spontaneously combusts at 130 degrees.}{干草在130度时会自燃}{
    \Word{hay}{n.}{干草}
    \Word{spontaneously}{adv.}{自发地}
    \Word{combust}{v.}{燃烧}
}
\SentenceBlock[1:16:02]{I will be clear across the country by the time that payout arrives.}{理赔到账时 我已经在美国另一边了}{
    \Word{payout}{n.}{赔付款}
}
\SentenceBlock[1:16:08]{I could make you an employee of the farm, and then send it in installments,}{我可以雇你为农场的员工然后把钱分期转给你}{
    \Word{installment}{n.}{分期付款}
}
\SentenceBlock[1:16:25]{Are they insured too?}{也买了保险吗}{
    \Word{insured}{adj.}{投保的}
}
\SentenceBlock[1:17:59]{I'm the new fucking farmhand. I'm the new fucking farmhand.}{我是新来的农场工 我是新来的农场工}{
    \Word{farmhand}{n.}{农场工人}
}
\SentenceBlock[1:18:49]{Cause if shit goes sideways, I'm nowhere near any of this.}{因为如果事情败露 那我要甩得一干二净}{
    \Word{sideways}{adv.}{出岔}
}
\SentenceBlock[1:23:25]{The fire marshal just informed me}{消防员刚才告诉我}{
    \Word{marshal}{n.}{消防队长}
}
\SentenceBlock[1:23:26]{that the blaze was set intentionally, Ms. Garretson.}{是有人故意放火的 盖瑞特森太太}{
    \Word{blaze}{n.}{火焰}
}
\SentenceBlock[1:28:06]{All right. Let's just fucking rewind, okay?}{好吧 我们倒回去讲}{
    \Word{rewind}{v.}{倒带}
}
\SentenceBlock[1:32:21]{I think Greg Kaminski's a known drug abuser.}{我认为格雷戈卡敏斯基是一个出了名的大毒虫}{
    \Word{abuser}{n.}{滥用者}
}
\SentenceBlock[1:35:52]{Okay, go to your working trot.}{好的 调整为工作快步}{
    \Word{trot}{n.}{快步}
}
\SentenceBlock[1:36:51]{she'll be mucking horse shit for the next two months.}{她必须铲两个月的马粪}{
    \Word{muck}{v.}{清理粪便}
}


\end{document}