\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries F1: The Movie}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:02:32]{How's the gearbox?}{变速箱怎么样}{
    \Word{gearbox}{n.}{变速箱}
}
\SentenceBlock[0:02:56]{Sonny Hayes back in the Porsche for Peak Geico Chip Hart Racing,}{桑尼海耶斯回到了山峰政府雇员保险公司 奇普哈特车队的保时捷上}{
    \Word{Geico}{n.}{政府雇员保险公司（公司名）}
}
\SentenceBlock[0:05:09]{Sonny Hayes brings it into pit lane after an epic third stint}{桑尼海耶斯在完成了 精彩绝伦的第三轮驾驶后 进入维修区}{
    \Word{epic}{adj.}{史诗般的；精彩绝伦的}
    \Word{stint}{n.}{一段时间的工作（此指一轮驾驶）}
}
\SentenceBlock[0:05:34]{Hey, dirtbag!}{嘿 混蛋}{
    \Word{dirtbag}{n.}{卑鄙小人；混蛋}
}
\SentenceBlock[0:05:49]{Hey. Attaboy, Sonny.}{嘿 好样的 桑尼}{
    \Word{Attaboy}{interj.}{好样的；干得好}
}
\SentenceBlock[0:06:14]{Your first win at Daytona. Don't you even want to touch it?}{你在代托纳的第一场胜利 你连碰都不碰}{
    \Word{Daytona}{n.}{代托纳（美国城市，以赛车闻名）}
}
\SentenceBlock[0:06:30]{You're CHR family now.}{你现在是奇普车队的一员了}{
    \Word{CHR}{n.}{Chip Hart Racing（车队缩写）}
}
\SentenceBlock[0:07:14]{...ninety-five seven, the Hog.}{调频95.7 HOG电台}{
    \Word{Hog}{n.}{Hog电台名称（广播品牌名）}
}
\SentenceBlock[0:08:03]{Are you thinking Baja?}{你想去下加州}{
    \Word{Baja}{n.}{下加利福尼亚（墨西哥半岛）}
}
\SentenceBlock[0:08:07]{That's exactly what I said to myself when I bought Apex GP.}{这正是我当初买下弯心车队时 对自己说的话}{
    \Word{Apex}{n.}{弯心（赛车术语，车队名）}
}
\SentenceBlock[0:08:41]{He said the car was a shitbox.}{他说我们的赛车是辆破烂货}{
    \Word{shitbox}{n.}{破车；破烂货}
}
\SentenceBlock[0:09:27]{Louis Chiron was 57 years old when he won the Monaco Grand Prix.}{路易希龙赢得摩纳哥大奖赛时都57岁了}{
    \Word{Prix}{n.}{大奖赛（法语“奖”的意思）}
}
\SentenceBlock[0:09:38]{a gambling junkie who missed his shot.}{一个错过机会的赌徒}{
    \Word{junkie}{n.}{对…上瘾的人（此处指嗜赌者）}
}
\SentenceBlock[0:09:47]{You're off your meds.}{你脑子进水了}{
    \Word{meds}{n.}{药物（medications 的口语缩写）}
}
\SentenceBlock[0:09:48]{My rookie's a phenomenal talent. Phenomenal. But he's young.}{我的新车手才华横溢 堪称天才 但他很年轻}{
    \Word{phenomenal}{adj.}{非凡的；惊人的}
}
\SentenceBlock[0:12:46]{Battery is full. You're good for strat two.}{电池满了 可以切换到模式二}{
    \Word{strat}{n.}{策略（strategy 的缩写）}
}
\SentenceBlock[0:14:17]{Let's go find those gremlins.}{来查查问题出在哪吧}{
    \Word{gremlins}{n.}{小故障；捣乱小妖（俚语，指机械故障）}
}
\SentenceBlock[0:15:13]{Then it understeers in the slow corners and oversteers the fast.}{然后在慢速弯道它转向不足 在快速弯道又转向过度}{
    \Word{understeers}{v.}{转向不足}
    \Word{oversteers}{v.}{转向过度}
}
\SentenceBlock[0:17:56]{Five-time Constructors champion with Ferrari.}{和法拉利一起五夺车队总冠军}{
    \Word{Constructors}{n.}{车队（F1术语，制造商车队）}
}
\SentenceBlock[0:18:12]{Sonny is here for the audition.}{桑尼是来面试的}{
    \Word{audition}{n.}{试镜；试演；面试}
}
\SentenceBlock[0:18:30]{Sidebar bitte , Ruben.}{请单独谈谈 鲁本}{
    \Word{bitte}{adv.}{请（德语）}
}
\SentenceBlock[0:18:32]{When I interview with you, many veteran drivers--}{我跟你面试的时候 很多老车手…}{
    \Word{veteran}{adj.}{经验丰富的}
}
\SentenceBlock[0:18:53]{With respect, Ruben, I cannot condone we spend our only test day}{恕我直言 鲁本 我不同意用仅有的试车日}{
    \Word{condone}{v.}{宽恕；容忍（此处为“赞同”之意）}
}
\SentenceBlock[0:19:09]{New wing, new side pods.}{新的前翼和侧箱}{
    \Word{pods}{n.}{舱体；侧箱（赛车部件）}
}
\SentenceBlock[0:20:00]{Differential one through four.}{差速器从一到四}{
    \Word{Differential}{n.}{差速器}
}
\SentenceBlock[0:21:23]{Twenty quid says he stacks it.}{我赌20英镑 他会一败涂地}{
    \Word{quid}{n.}{英镑（英式口语）}
    \Word{stacks}{v.}{摔车（赛车术语，俚语）}
}
\SentenceBlock[0:24:17]{But definitely snappy in the high-speed corners.}{但高速转弯确实灵敏过头}{
    \Word{snappy}{adj.}{灵敏的；敏捷的（可引申为“过头”）}
}
\SentenceBlock[0:25:40]{Facety.}{真是没大没小}{
    \Word{Facety}{adj.}{无礼的（英式俚语）}
}
\SentenceBlock[0:26:07]{He's such an arsehole, Mum.}{他是个大混蛋 妈}{
    \Word{arsehole}{n.}{混蛋（英式粗俗语）}
}
\SentenceBlock[0:27:42]{Hayes was considered something of a reckless young phenomenon,}{年轻时曾被视为鲁莽的奇才}{
    \Word{reckless}{adj.}{鲁莽的；不顾后果的}
}
\SentenceBlock[0:28:00]{and even a stint as a New York taxi driver.}{甚至还当过一段时间纽约市德士司机}{
    \Word{stint}{n.}{一段时间的工作}
}
\SentenceBlock[0:28:12]{None of this will dampen speculation}{这一切都不会减少}{
    \Word{dampen}{v.}{抑制；削弱}
}
\SentenceBlock[0:29:46]{So, uh, it must be surreal to be back.}{回来的感觉一定很不真实}{
    \Word{surreal}{adj.}{超现实的；不真实的}
}
\SentenceBlock[0:29:59]{Before declaring yourself personally bankrupt?}{然后宣布破产}{
    \Word{bankrupt}{adj.}{破产的}
}

\SentenceBlock[0:30:04]{You had a marriage annulled and two more ended in divorce?}{你有一次婚姻被宣告无效 还有两次以离婚收场}{
    \Word{annul}{v.}{宣告无效}
}
\SentenceBlock[0:33:50]{Drivers, two minutes to national anthem.}{各位车手 两分钟后奏国歌}{
    \Word{anthem}{n.}{国歌}
}
\SentenceBlock[0:34:48]{The rest are calling it, you know, Ruben's Inferno.}{其他人都说车队是“鲁本的炼狱”}{
    \Word{Inferno}{n.}{地狱；炼狱}
}
\SentenceBlock[0:34:50]{But, seriously, man, I'm hooked.}{但是说真的 哥们 我很感兴趣}{
    \Word{hooked}{adj.}{入迷的；着迷的}
}
\SentenceBlock[0:34:51]{I've binged all of Drive to Survive .}{我一口气刷完了《疾速争胜》}{
    \Word{binge}{v.}{狂看；狂吃}
}
\SentenceBlock[0:38:57]{Copy. Gap is 0.9 to Perez. You're within DRS range.}{收到 距离佩雷斯0.9秒 已进入减阻系统区间}{
    \Word{DRS}{n.}{减阻系统（Drag Reduction System）}
}
\SentenceBlock[0:39:19]{We've seen the attack. Now it's all about defense.}{刚刚的进攻我们已经见识过了 现在就看他守得如何}{
    \Word{defense}{n.}{防守}
}
\SentenceBlock[0:40:00]{I'm jammed. Back up!}{卡住了 换备用的}{
    \Word{jammed}{adj.}{卡住的；无法动弹的}
}
\SentenceBlock[0:40:32]{- You're kidding me. - This is causing absolute pandemonium,}{-逗我呢 -导致弯心车队维修区混乱不堪}{
    \Word{pandemonium}{n.}{混乱；喧嚣}
}
\SentenceBlock[0:41:44]{And what a brawl it is.}{战况真是激烈啊}{
    \Word{brawl}{n.}{混战；斗殴}
}
\SentenceBlock[0:42:12]{Both Apex GP cars into the gravel, and Pearce hits the barrier.}{弯心车队的两辆赛车 全部冲上了碎石地 皮尔斯撞上了防护墙}{
    \Word{gravel}{n.}{碎石地}
}
\SentenceBlock[0:42:23]{The cardinal sin of motor racing.}{赛车运动中的大忌}{
    \Word{cardinal}{adj.}{根本的；主要的（此处指“严重的”）}
}
\SentenceBlock[0:42:25]{A double DNF.}{双双退出比赛}{
    \Word{DNF}{n.}{未完成比赛（Did Not Finish）}
}
\SentenceBlock[0:43:50]{You. You're an arsehole. You come in like an arsehole. You swan.}{就是你 你是个混蛋 像个混蛋一样闯进队里 拽得不行}{
    \Word{arsehole}{n.}{混蛋}
}
\SentenceBlock[0:44:05]{Back home we call that a participation trophy.}{在我老家 这叫参与奖}{
    \Word{trophy}{n.}{奖杯；奖品}
}
\SentenceBlock[0:45:42]{""I'm sorry, Ruben, for demolishing not one but both of your lovely cars.}{“对不起 鲁本 我一下子 报废掉你的两台宝贝赛车}{
    \Word{demolish}{v.}{摧毁；拆毁}
}
\SentenceBlock[0:45:51]{and came all this way to humiliate myself on global television.}{就为了在全球电视观众面前自取其辱}{
    \Word{humiliate}{v.}{羞辱；使丢脸}
}
\SentenceBlock[0:45:59]{Listen, he's cocky. He's arrogant. He's got a lot to learn.}{听着 他很自负 很傲慢 他要学的东西还多着呢}{
    \Word{cocky}{adj.}{自大的；自负的}
}
\SentenceBlock[0:46:18]{and I have to decide whether to continue this fiasco,}{我得作出决定 是继续这出闹剧}{
    \Word{fiasco}{n.}{惨败；彻底失败}
}
\SentenceBlock[0:46:46]{Okay, stay there in that tub of ice until Budapest.}{够了 给我待在冰水里 直到布达佩斯站}{
    \Word{tub}{n.}{桶；容器}
}
\SentenceBlock[0:47:52]{Cool. And you can replicate turns? Lateral airflow?}{厉害 那你能复制转弯动作吗 横向气流呢}{
    \Word{replicate}{v.}{复制；再现}
}
\SentenceBlock[0:48:00]{Okay, what about turbulent air from a car we're following?}{好 那跟在一辆车后面遇到的乱流呢}{
    \Word{turbulent}{adj.}{湍流的；混乱的}
}
\SentenceBlock[0:48:45]{That he is clutching at straws.}{他在握紧最后的救命稻草}{
    \Word{clutch}{v.}{紧握}
    \Word{straw}{n.}{稻草}
}
\SentenceBlock[0:49:03]{From others, I mostly prefer praise, flattery, hero worship,}{从其他人那里 我更喜欢听赞美 吹捧 英雄崇拜}{
    \Word{flattery}{n.}{奉承；恭维}
}
\SentenceBlock[0:49:10]{Ruben. I love the guy. Most solid, steadfast--}{我很喜欢鲁本 他是最可靠 最坚定的…}{
    \Word{steadfast}{adj.}{坚定的；忠诚的}
}
\SentenceBlock[0:49:14]{Disloyal, mean, twisted, bitter, husk of a man.}{不忠 卑鄙 阴险 怨毒 徒有其表的男人}{
    \Word{husk}{n.}{外壳；空壳（引申为“无实质的人”）}
}
\SentenceBlock[0:49:24]{He said to avoid you like the plague.}{他说要像躲瘟疫一样躲着你}{
    \Word{plague}{n.}{瘟疫；灾祸}
}
\SentenceBlock[0:50:41]{A lone wolf.}{一只独狼}{
    \Word{lone}{adj.}{孤独的；独自的}
}
\SentenceBlock[0:52:36]{Seen by some as reckless, it nevertheless served him well}{有些人认为这种风格颇为鲁莽 但它确实为他带来了不小的回报}{
    \Word{reckless}{adj.}{鲁莽的；不计后果的}
}
\SentenceBlock[0:52:42]{relentlessly pursuing his first F1 victory.}{不懈地追求他的第一次F1胜利}{
    \Word{relentlessly}{adv.}{不懈地；持续不断地}
}
\SentenceBlock[0:53:05]{There you can see the debris on the right.}{可以看到右侧全是赛车残骸}{
    \Word{debris}{n.}{碎片；残骸}
}

\SentenceBlock[0:53:51]{At this temp, the tire deg will be too high.}{在这个温度下 轮胎磨损会过于严重}{
    \Word{deg}{n.}{磨损（degradation 的缩写）}
}
\SentenceBlock[0:55:09]{Hit debris. Check my tires.}{碰到碎片了 检查我的轮胎}{
    \Word{debris}{n.}{碎片}
}
\SentenceBlock[0:55:10]{Yeah, you've got a puncture. Right rear. Box. Box this lap.}{好 右后胎爆了 这圈进站}{
    \Word{puncture}{n.}{爆胎；穿刺}
}
\SentenceBlock[0:56:42]{-It's a late lunge! -He's damaged his front wing.}{-这是一次迟刹强攻 -他的前翼受损了}{
    \Word{lunge}{n.}{猛冲；突进}
}
\SentenceBlock[0:56:44]{Any driver knows Magnussen will shut the door on a clumsy move like that.}{任何一个车手都知道 马格努森 一定不会让这种拙劣的招数得逞}{
    \Word{clumsy}{adj.}{笨拙的；不灵巧的}
}
\SentenceBlock[0:56:49]{Aw, dagnabbit.}{真该死}{
    \Word{dagnabbit}{interj.}{该死的（委婉语，表示懊恼）}
}
\SentenceBlock[0:57:06]{Standby. Kate,}{待命 凯特}{
    \Word{Standby}{v.}{待命；准备好}
}
\SentenceBlock[0:59:59]{bringing the Hungarian Grand Prix to an absolute crawl.}{匈牙利大奖赛变成了大塞车}{
    \Word{crawl}{n.}{缓慢行进；爬行}
}
\SentenceBlock[1:00:03]{A sub three-second stop, and he'll keep P10.}{三秒内完成维修 他就能保住第十名}{
    \Word{sub}{adj.}{不足…的（此处指“低于三秒”）}
}
\SentenceBlock[1:01:10]{And behind our podium placings,}{而在领奖台之外}{
    \Word{podium}{n.}{领奖台}
}
\SentenceBlock[1:01:45]{I'm still a bit rusty and, you know, finding my way with this car,}{我还有些生疏 还在熟悉这辆赛车}{
    \Word{rusty}{adj.}{生疏的；生锈的}
}
\SentenceBlock[1:01:49]{A rope-a-dope at Silverstone, a demolition derby here in Hungary...}{在银石赛道扮猪吃老虎 在匈牙利上演撞车大赛}{
    \Word{demolition}{n.}{拆毁；毁坏}
}
\SentenceBlock[1:02:17]{Take it out of my paycheck.}{从我工资里扣好了}{
    \Word{paycheck}{n.}{工资；薪水}
}
\SentenceBlock[1:04:05]{Traveling the world, the roar of a crowd...}{周游世界 观众的欢呼}{
    \Word{roar}{n.}{吼声；呼喊声}
}
\SentenceBlock[1:04:14]{Who swiftly became my ex-husband.}{他就迅速变成前夫了}{
    \Word{swiftly}{adv.}{迅速地}
}
\SentenceBlock[1:05:47]{Certainly do. Uh, first of all, he's a lot grayer now.}{当然 首先 他现在两鬓“灰”白 人也更加老奸巨猾了}{
    \Word{gray}{adj.}{灰白的}
}
\SentenceBlock[1:06:48]{For three weeks, all the talk's been how reckless I am.}{三周了 大家都在说我多么鲁莽}{
    \Word{reckless}{adj.}{鲁莽的}
}
\SentenceBlock[1:07:41]{Apex GP is prepping a fresh set of tires for Hayes.}{弯心车队在为海耶斯准备一套新轮胎}{
    \Word{prep}{v.}{准备}
}
\SentenceBlock[1:07:44]{That's gonna bring in all the other teams to avoid the undercut.}{这一动作会带动其他车队进站 以避免被“抢先进站”反超}{
    \Word{undercut}{n.}{抢先进站（赛车术语）}
}
\SentenceBlock[1:07:49]{But, no! He's staying out, with the cars behind him all scrambling}{但他没进站 而是继续比赛}{
    \Word{scramble}{v.}{争抢；混乱地移动}
}
\SentenceBlock[1:09:32]{And Max shows his disapproval,}{而马克斯表示了不满}{
    \Word{disapproval}{n.}{不满；不同意}
}
\SentenceBlock[1:09:34]{and I don't blame him, as they head down towards the second chicane.}{不怪他 两人来到了第二组连续弯道}{
    \Word{chicane}{n.}{连续急弯（赛车术语）}
}
\SentenceBlock[1:09:52]{and who might gamble to stay out on slicks.}{又有谁会冒险坚持用干胎继续比赛}{
    \Word{slicks}{n.}{光头胎（赛车专用轮胎）}
}
\SentenceBlock[1:10:02]{You're running P4. We think P2 and P3 are switching to inters for safety,}{你现在排第四位 我们认为 第二和第三要换半雨胎 以求安全}{
    \Word{inters}{n.}{半雨胎（intermediate tires）}
}
\SentenceBlock[1:10:24]{Sonny, Joshua is staying out on slicks. If he can hold on and find a dry line,}{桑尼 约书亚用干胎继续比赛 如果他能顶住 并找到一条干线}{
    \Word{slicks}{n.}{光头胎}
}

\SentenceBlock[1:11:00]{Sonny Hayes is in another standoff over team strategy.}{桑尼海耶斯再次因为车队策略 和指挥僵持不下}{
    \Word{standoff}{n.}{僵局；对峙}
}
\SentenceBlock[1:11:40]{Pearce picks up the slipstream from Hayes,}{皮尔斯借助海耶斯的尾流}{
    \Word{slipstream}{n.}{尾流；气流带}
}
\SentenceBlock[1:11:58]{- Overtake him. Overtake. - Copy.}{-超车… -收到}{
    \Word{Overtake}{v.}{超过；超车}
}
\SentenceBlock[1:11:59]{He's been gaining, and boom! Joshua Pearce slingshots past Sonny Hayes,}{他一直在追赶 突然之间 约书亚皮尔斯飞速超过桑尼海耶斯}{
    \Word{slingshot}{v.}{高速超越}
}
\SentenceBlock[1:16:30]{A chaotic week for Expensify Apex GP,}{Expensify弯心车队经历了混乱的一周}{
    \Word{chaotic}{adj.}{混乱的}
}
\SentenceBlock[1:16:36]{Many are blaming him for his teammate's horrific accident at Monza.}{很多人把他队友可怕的事故怪在他头上}{
    \Word{horrific}{adj.}{可怕的；令人震惊的}
}
\SentenceBlock[1:17:25]{They've docked us to the back of the grid 'cause they don't like the way we drive.}{他们把我们罚到发车队尾了 因为他们不喜欢我们的驾驶方式}{
    \Word{dock}{v.}{扣分；降低}
}
\SentenceBlock[1:18:32]{but here he is, coming from the cellar, passing his new teammate, Luca Cortez.}{从末位出发 超过了新队友卢卡科尔特斯}{
    \Word{cellar}{n.}{垫底；最末位（引申义）}
}
\SentenceBlock[1:19:35]{Scrapping away on the last lap,}{在最后一圈奋力追赶}{
    \Word{scrap}{v.}{拼搏；奋力争夺}
}
\SentenceBlock[1:19:46]{- It's a valiant seventh. - Combat, I love it!}{-勇夺第七 -战斗 我爱这计划}{
    \Word{valiant}{adj.}{英勇的；顽强的}
}
\SentenceBlock[1:19:59]{Sonny may be a saboteur, Josh.}{桑尼也许是故意捅你一刀 约书亚}{
    \Word{saboteur}{n.}{破坏者；捣乱分子}
}
\SentenceBlock[1:21:18]{He's treating you like a pawn, Josh.}{他把你当小卒 约书亚}{
    \Word{pawn}{n.}{棋子；被利用的人}
}
\SentenceBlock[1:23:45]{Into the chicane we go and they touch wheels!}{赛车来到双急弯 双方车轮碰撞了}{
    \Word{chicane}{n.}{连续急弯}
}
\SentenceBlock[1:24:26]{You wanna sabotage your career, you go right ahead.}{你想自毁前程 请随意}{
    \Word{sabotage}{v.}{蓄意破坏}
}
\SentenceBlock[1:25:38]{Good. Sensational.}{好 好极了}{
    \Word{Sensational}{adj.}{轰动的；极好的}
}
\SentenceBlock[1:26:13]{- Ish. - And please don't call me JP.}{-没全听 -还有 请别叫我JP}{
    \Word{Ish}{adv.}{大约；差不多（口语）}
}
\SentenceBlock[1:27:50]{You have a deficient frontal cortex.}{你的额叶皮质发育不良}{
    \Word{deficient}{adj.}{有缺陷的；不足的}
    \Word{frontal}{adj.}{额部的}
    \Word{cortex}{n.}{皮质（尤指大脑皮层）}
}
\SentenceBlock[1:32:07]{-I like this, bruv. -Glad you're having fun, man.}{-我喜欢这里 兄弟 -你开心我就开心 哥们}{
    \Word{bruv}{n.}{兄弟（英式俚语）}
}
\SentenceBlock[1:33:17]{I shouldn't drink tequila.}{我不该喝龙舌兰的}{
    \Word{tequila}{n.}{龙舌兰酒}
}
\SentenceBlock[1:34:56]{So I lost my seat, my money, my sanity, my...}{我失去了席位 钱 理智 还有…}{
    \Word{sanity}{n.}{神志清醒；理智}
}
\SentenceBlock[1:35:03]{Just became this angry, resentful shithead.}{成了一个满腔愤怒 怨气冲天的混蛋}{
    \Word{resentful}{adj.}{怨恨的；愤愤不平的}
}
\SentenceBlock[1:37:55]{- I'll take that with a pinch of salt. - Someone can fabricate documents.}{-我对此持保留意见 -文档是可以伪造的}{
    \Word{pinch}{n.}{少量；一撮（此处指“保留态度”）}
    \Word{fabricate}{v.}{伪造；编造}
}
\SentenceBlock[1:38:14]{This is not car racing, sir, this is like corporate espionage!}{这可不是赛车 先生 这是商业间谍活动}{
    \Word{espionage}{n.}{间谍活动}
}
\SentenceBlock[1:40:31]{Hard on the brakes now, and into the chicane.}{现在急刹车了 进入连续弯道}{
    \Word{chicane}{n.}{连续急弯}
}

\SentenceBlock[1:41:43]{""C5 neck fracture.}{“C5颈椎骨折"}{
    \Word{fracture}{n.}{骨折}
}
\SentenceBlock[1:41:46]{Spinal contusion.}{脊髓挫伤}{
    \Word{Spinal}{adj.}{脊柱的}
    \Word{contusion}{n.}{挫伤}
}
\SentenceBlock[1:41:48]{Compressed thoracic vertebrae.}{压缩性胸椎骨折}{
    \Word{thoracic}{adj.}{胸部的}
    \Word{vertebra}{n.}{椎骨}
}
\SentenceBlock[1:41:51]{Further blunt force impact trauma likely to result in vision loss,}{再受钝性创伤 可能会导致失明}{
    \Word{blunt}{adj.}{钝的；钝性的}
}
\SentenceBlock[1:41:55]{paralysis, death.""}{瘫痪甚至死亡”}{
    \Word{paralysis}{n.}{瘫痪}
}
\SentenceBlock[1:42:26]{And don't think there's some bullshit loophole to get you out of this.}{别以为有什么狗屁空子 能让你钻了后全身而退}{
    \Word{loophole}{n.}{漏洞；空子}
}
\SentenceBlock[1:42:42]{broke losers.}{破产的失败者}{
    \Word{broke}{adj.}{破产的；身无分文的}
}
\SentenceBlock[1:45:18]{I thought you were gonna be the... the final nail in the coffin.}{我本以为你会是压垮骆驼的最后一根稻草}{
    \Word{coffin}{n.}{棺材（引申为失败的最终打击）}
}
\SentenceBlock[1:46:21]{- Sorry to make you sweat. - Hey.}{-抱歉 害你紧张了 -嘿}{
    \Word{sweat}{v.}{紧张；出汗}
}
\SentenceBlock[1:49:24]{Parc fermé. Waiting for FIA to cut the seals.}{车被封存监管 在等国际汽车联合会来剪开封条}{
    \Word{Parc}{n.}{封闭区（法语词，赛车术语）}
    \Word{ferm}{adj.}{封闭的（法语词，来自“fermé”）}
    \Word{FIA}{n.}{国际汽车联合会（Fédération Internationale de l'Automobile）}
}
\SentenceBlock[1:49:44]{Welcome to the Paddock Club, for our most valued guests.}{欢迎来到围场俱乐部 这里是为我们最尊贵的宾客而设}{
    \Word{Paddock}{n.}{围场区；维修区}
}
\SentenceBlock[1:51:02]{Jesús, it's like a morgue around here.}{天啊 这里简直像个停尸房}{
    \Word{morgue}{n.}{停尸房}
}
\SentenceBlock[1:51:22]{...waiving all liability to you,}{本人主动声明 放弃追究你和你的公司}{
    \Word{liability}{n.}{法律责任；义务}
}
\SentenceBlock[1:55:27]{Drivers jockeying for position as we head full-throttle down the main straight}{车手们在主直道全油门疾驰 争相抢位}{
    \Word{jockey}{v.}{争抢位置}
}
\SentenceBlock[1:57:16]{Often, the irresistible force meets the immovable object.}{每次都是硬碰硬 针锋相对 互不相让}{
    \Word{irresistible}{adj.}{不可抗拒的}
}
\SentenceBlock[1:58:41]{He's keeping the leaders at bay. DRS active next straight, Sonny.}{他压着领跑集团呢 下一个直道可以开启减阻系统 桑尼}{
    \Word{DRS}{n.}{减阻系统（Drag Reduction System）}
}
\SentenceBlock[1:59:47]{One of the leaders is gonna undercut. I need to be there when they do.}{有人会抢先进站造成时间差 我一定要抓住这个时机}{
    \Word{undercut}{v.}{抢先进站（赛车术语）}
}
\SentenceBlock[2:02:08]{A great underdog story,}{这是一个精彩的黑马故事}{
    \Word{underdog}{n.}{劣势方；黑马}
}
\SentenceBlock[2:02:13]{Yeah. Sadly, the deck's been stacked against them}{对 很不幸 局势对他们不利}{
    \Word{stack}{v.}{堆积；对…不利}
}
\SentenceBlock[2:02:43]{There's debris all over the race track,}{赛道上到处都是碎片}{
    \Word{debris}{n.}{碎片}
}
\SentenceBlock[2:03:18]{We are still alive, hermano.}{我们还有戏 兄弟}{
    \Word{hermano}{n.}{兄弟（西班牙语）}
}
\SentenceBlock[2:03:55]{for what will be a three-lap sprint.}{准备冲刺三圈}{
    \Word{sprint}{n.}{短距离冲刺；冲刺赛}
}
\SentenceBlock[2:05:16]{The marshals just sweeping the last few bits of debris off the track,}{赛道工人在清扫赛道上最后一点碎片}{
    \Word{marshal}{n.}{赛道官员}
}
\SentenceBlock[2:06:26]{This red flag is a lifeline.}{这个红旗是救命稻草}{
    \Word{lifeline}{n.}{救命稻草；生命线}
}
\SentenceBlock[2:06:49]{and when this race resumes, this is gonna be an epic sprint.}{比赛一旦重新开始 将是一场史诗级的冲刺对决}{
    \Word{epic}{adj.}{史诗般的；精彩绝伦的}
    \Word{sprint}{n.}{冲刺}
}
\SentenceBlock[2:09:20]{Hayes plays the decoy,}{海耶斯充当诱饵}{
    \Word{decoy}{n.}{诱饵；佯动}
}
\SentenceBlock[2:18:50]{but in a way that was more poetic.}{不过要用更有诗意的方式说}{
    \Word{poetic}{adj.}{富有诗意的}
}
\SentenceBlock[2:19:48]{You know, couple more dragons to slay.}{还有几条恶龙要屠呢}{
    \Word{slay}{v.}{屠杀；征服（比喻用法）}
}



\end{document}