\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S01E06: Hide and Seek}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:01:32]{Tame in me the tempers four}{驯服我心中的四种脾气}{%
  \Word{Tame}{v.}{驯服}
  \Word{tempers}{n.}{脾气}
}

\SentenceBlock[0:01:37]{that I may serve thee evermore.}{好让我永远为你服务}{%
  \Word{thee}{pron.}{你（古语，宾格）}
  \Word{evermore}{adv.}{永远}
}

\SentenceBlock[0:01:46]{that I may feel thy touch divine.}{好让我感受你神圣的触摸}{%
  \Word{thy}{pron.}{你的（古语，属格）}
}

\SentenceBlock[0:06:05]{It does discourage romantic fraternization, though.}{不过手册确实不鼓励员工发展浪漫关系}{%
  \Word{fraternization}{n.}{亲密交往；（尤指敌对双方或上下级间的）不适当交往}
}

\SentenceBlock[0:07:50]{Devon. From the retreat.}{德文 我们在度假村见过}{%
  \Word{retreat}{n.}{静修地；度假地}
}

\SentenceBlock[0:07:52]{I accosted you for your coffee.}{我为了你的咖啡找你搭话}{%
  \Word{accosted}{v.}{上前搭话（尤指唐突或挑衅地）}
}

\SentenceBlock[0:08:55]{What does camaraderie mean?}{同事情谊是什么意思}{%
  \Word{camaraderie}{n.}{友情；同志情谊}
}

\SentenceBlock[0:09:15]{But I think camaraderie is more than smiling together in photos.}{但我认为同事情谊不仅限于 一起在照片中微笑}{%
  \Word{camaraderie}{n.}{友情；同志情谊}
}

\SentenceBlock[0:09:41]{Someone's eager to fraternize.}{有人很想搞好同事关系啊}{%
  \Word{fraternize}{v.}{亲善；与…亲密交往}
}

\SentenceBlock[0:09:43]{Fraternization has nothing to do with it.}{这和搞好同事关系无关}{%
  \Word{Fraternization}{n.}{亲密关系；不当交往}
}

\SentenceBlock[0:09:50]{Maybe his ghost can officiate your wedding.}{也许他的鬼魂可以主持你的婚礼}{%
  \Word{officiate}{v.}{主持（仪式）}
}

\SentenceBlock[0:10:38]{Back to work, slackers.}{回去工作了 懒鬼们}{%
  \Word{slackers}{n.}{懒鬼；逃避责任者}
}

\SentenceBlock[0:11:00]{Look at you all dewy mouthed.}{瞧你口水都快流出来了}{%
  \Word{dewy}{adj.}{湿润的；露水般的}
}

\SentenceBlock[0:11:44]{Because I snuck Helly out.}{因为我把赫莉带走了}{%
  \Word{snuck}{v.}{偷偷地移动；溜}
}

\SentenceBlock[0:11:51]{Valiance.}{勇气}{%
  \Word{Valiance}{n.}{英勇；勇敢}
}

\SentenceBlock[0:12:02]{She's just a wellness counselor, Mark.}{她只是个健康顾问 马克}{%
  \Word{counselor}{n.}{顾问；辅导员}
}

\SentenceBlock[0:12:20]{Or were you sniffing around other departments}{还是说你们在调查其他部门}{%
  \Word{sniffing}{v.}{嗅探；打探}
}

\SentenceBlock[0:12:22]{while your department falls woefully below quota?}{而你的部门距离业绩指标还差得很远}{%
  \Word{woefully}{adv.}{严重地；令人悲伤地}
}

\SentenceBlock[0:12:28]{It's not your job to play nursemaid to every new refiner.}{你的职责不是给每一位新精检员当保姆}{%
  \Word{nursemaid}{n.}{保姆；照顾小孩的人}
}

\SentenceBlock[0:12:48]{And until you get that through your mildewed little brain and hit quota,}{在你用愚蠢的脑袋 理解这一点并完成指标前}{%
  \Word{mildewed}{adj.}{发霉的；霉斑的}
}

\SentenceBlock[0:12:55]{MDR's hallway privileges are hereby revoked.}{宏观数据精检部去走廊的特权被取消了}{%
  \Word{hereby}{adv.}{特此；以此方式}
  \Word{revoked}{v.}{撤销；取消}
}

\SentenceBlock[0:13:14]{MDR will mourn the "will-they-won't-they" energy shared by Ms. Casey and myself.}{宏观数据精检部 将为我和凯西女士的好奇心哀悼}{%
  \Word{mourn}{v.}{哀悼；悲痛}
}

\SentenceBlock[0:13:25]{Well, maybe love transcends severance.}{也许爱情可以跨越记忆分离}{%
  \Word{transcends}{v.}{超越；超出}
}

\SentenceBlock[0:15:58]{I know change can be disorienting,}{我知道变化会使人迷惑}{%
  \Word{disorienting}{adj.}{使人迷失方向的；令人困惑的}
}

\SentenceBlock[0:16:09]{much as I hope all of us will be welcome to visit you at your place of endeavors.}{我也希望你们欢迎我们所有人 去你们努力工作的地方参观}{%
  \Word{endeavors}{n.}{努力；事业}
}

\SentenceBlock[0:16:49]{The hatchets weren't aggressive.}{斧头才没有攻击性呢}{%
  \Word{hatchets}{n.}{短柄小斧}
}

\SentenceBlock[0:18:02]{If the Eagan philosophy is illumination above all--}{如果伊根的理念 是凌驾于一切之上的启蒙…}{%
  \Word{illumination}{n.}{启示；照明}
}

\SentenceBlock[0:20:01]{Brings the bounty to the plain Through the torment, through the rains}{历经苦难、穿过风雨 给平原带来丰收}{%
  \Word{bounty}{n.}{丰富；慷慨}
  \Word{torment}{n.}{痛苦；折磨}
}

\SentenceBlock[0:20:32]{Your inefficiency and free-range chicken roaming}{你工作效率低下 像走地鸡一般自由散漫}{%
  \Word{roaming}{v.}{闲逛；漫游}
}

\SentenceBlock[0:20:47]{Escort him to the break room.}{送他去休息室}{%
  \Word{Escort}{v.}{护送；陪同}
}

\SentenceBlock[0:22:26]{Apparently, I jammed my hand at work replenishing a watercooler.}{据说是我在给公司的饮水机 换水桶时夹到手了}{%
  \Word{replenishing}{v.}{补充；重新装满}
  \Word{watercooler}{n.}{饮水机}
}

\SentenceBlock[0:22:32]{Those jugs are very heavy.}{那些水桶很重}{%
  \Word{jugs}{n.}{水壶；大容器}
}

\SentenceBlock[0:22:35]{Another merlot?}{再来一杯梅洛}{%
  \Word{merlot}{n.}{梅洛葡萄酒}
}

\SentenceBlock[0:22:52]{- Latching difficulties? - Yes.}{- 哺乳困难  - 是}{%
  \Word{Latching}{n.}{（婴儿）含乳；啜乳}
}

\SentenceBlock[0:22:56]{Well, she just wanted the names of some lactation consultants.}{她想要一些哺乳期顾问的信息}{%
  \Word{lactation}{n.}{哺乳；泌乳}
}

\SentenceBlock[0:23:56]{She was very pragmatic.}{她很务实}{%
  \Word{pragmatic}{adj.}{务实的；实际的}
}

\SentenceBlock[0:24:32]{She's just pissed that she's dead.}{她只是因为自己死了很生气}{%
  \Word{pissed}{adj.}{生气的（非正式）}
}

\SentenceBlock[0:26:11]{I went giddy when Mark mentioned you were looking for someone.}{马克说你在找顾问 我听了很高兴}{%
  \Word{giddy}{adj.}{兴奋的；头晕的}
}

\SentenceBlock[0:26:13]{- So serendipitous. - I know.}{- 太巧了 - 是啊}{%
  \Word{serendipitous}{adj.}{意外发现的；侥幸得到的}
}

\SentenceBlock[0:26:26]{- You had a vaginal birth, yes? - Oh, yeah.}{- 是自然分娩的 对吗  - 对}{%
  \Word{vaginal}{adj.}{阴道的}
}

\SentenceBlock[0:26:33]{Shea butter salve for your nipples.}{涂抹乳头用的乳木果油软膏}{%
  \Word{Shea}{adj.}{乳木果的}
  \Word{salve}{n.}{软膏；药膏}
  \Word{nipples}{n.}{乳头}
}

\SentenceBlock[0:27:50]{The ideographic card you took from O\&D.}{你从光学与设计部拿走的表意图片卡}{%
  \Word{ideographic}{adj.}{表意的}
}

\SentenceBlock[0:27:53]{Did you smuggle it out? Is it here?}{你把它偷偷带出来了吗 在这里吗}{%
  \Word{smuggle}{v.}{走私；偷偷带出}
}

\SentenceBlock[0:29:23]{If it's lame, we'll leave.}{如果不好听我们就走}{%
  \Word{lame}{adj.}{无趣的；蹩脚的}
}

\SentenceBlock[0:30:11]{Hi. Who's doing sound in this alleyway tonight? It's terrible.}{嗨 今晚巷子里的声音 是谁发出的  真难听}{%
  \Word{alleyway}{n.}{小巷；狭道}
}

\SentenceBlock[0:30:32]{I feel a callus on my heart 'Cause every day's the same}{我感觉自己的心已经麻木 因为每天一成不变}{%
  \Word{callus}{n.}{老茧；硬结}
}

\SentenceBlock[0:31:29]{What's happening? This is depraved.}{怎么回事 堕落了}{%
  \Word{depraved}{adj.}{堕落的；道德败坏的}
}


\SentenceBlock[0:33:21]{What's that a euphemism for?}{这是什么的委婉说法}{%
  \Word{euphemism}{n.}{委婉语}
}



\end{document}
