\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S01E04: The You You Are}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:07:29]{Okay, good. I've been fretting, though, because you mentioned}{很好，不过我一直在发愁，因为你说}{%
  \Word{fretting}{v.}{烦恼}
}
\SentenceBlock[0:07:32]{the anticipation could distract from your work,}{这种期待可能会干扰你的工作}{%
  \Word{anticipation}{n.}{期待}
}
\SentenceBlock[0:07:37]{So I figured, heck, let's bring them over now.}{于是我想，管它呢，现在就给他们送过去}{%
  \Word{heck}{n.}{该死}
}
\SentenceBlock[0:08:43]{That was before O\&D started disemboweling people's bowels.}{那是在光学与设计部开始给人们开肠破肚之前}{%
  \Word{disemboweling}{v.}{剖腹} \Word{bowels}{n.}{内脏}
}
\SentenceBlock[0:09:44]{No. Like, the angry, mumbly guy.}{不，像是那个气呼呼、爱嘟囔的家伙}{%
  \Word{mumbly}{adj.}{含糊不清的}
}
\SentenceBlock[0:11:16]{The big envelopes can handle an appendix reissue.}{大信封可以装下一份再版的附录}{%
  \Word{reissue}{n.}{再版}
}
\SentenceBlock[0:11:20]{But, of course, we ship all the hallway pieces in-frame.}{但是当然了，所有走廊里的画我们都是装好画框再发货的}{%
  \Word{hallway}{n.}{走廊}
}
\SentenceBlock[0:11:51]{when you guys put up The Youthful Convalescence of Kier.}{因为你们挂起了“青年基尔康复”那副画}{%
  \Word{Convalescence}{n.}{康复}
}
\SentenceBlock[0:12:42]{Cherished workers, drown it inside you.}{可贵的员工们，战胜软弱吧}{%
  \Word{Cherished}{adj.}{珍爱的}
}
\SentenceBlock[0:12:45]{Rise up from your deathbed and sally forth,}{在临终时站起来，勇往直前}{%
  \Word{deathbed}{n.}{临终之床} \Word{sally}{v.}{勇敢出发}
}
\SentenceBlock[0:15:44]{You're such a hypocrite,}{你真虚伪}{%
  \Word{hypocrite}{n.}{伪君子}
}
\SentenceBlock[0:16:02]{It's an Eagan rule. "Render not my creation in miniature."}{是伊根的规矩：“不得缩绘我的创造物”}{%
  \Word{miniature}{n.}{缩影}
}
\SentenceBlock[0:16:11]{Yeah, exactly, because these are random, bored doodles.}{没错，这是人无聊的时候乱画的}{%
  \Word{doodles}{n.}{涂鸦}
}
\SentenceBlock[0:16:40]{We could have fun and work without the whole goddamn department imploding.}{我们可以开心地工作，整个部门也不会垮掉}{%
  \Word{imploding}{v.}{内爆}
}
\SentenceBlock[0:17:00]{I could not, with a razor to my throat,}{就算有人用刀架在我脖子上}{%
  \Word{razor}{n.}{剃刀}
}
\SentenceBlock[0:18:03]{It's just raining contraband today.}{今天的违禁品真多啊}{%
  \Word{contraband}{n.}{违禁品}
}
\SentenceBlock[0:18:12]{Be content in my words, and dally not in the scholastic pursuits of lesser men.}{满足于我的文字，不要浪费时间向不如我的人学习}{%
  \Word{dally}{v.}{浪费时间} \Word{scholastic}{adj.}{学术的}
}
\SentenceBlock[0:18:23]{His ego's pissed 'cause Helly called him out for boot-licking.}{他自尊心受挫了，因为赫莉说他是听话好员工}{%
  \Word{pissed}{adj.}{生气的}
}
\SentenceBlock[0:18:41]{What? Why? It's booty. It's booty with your name on it.}{什么，为什么？这是战利品，上面写着你的名字呢}{%
  \Word{booty}{n.}{战利品}
}
\SentenceBlock[0:18:45]{This is an idolatrous text that should be brought to him immediately.}{这是有关盲目崇拜的文字，应立即交给他}{%
  \Word{idolatrous}{adj.}{盲目崇拜的}
}
\SentenceBlock[0:19:15]{So what's their space like? Stalactites and shit?}{他们的办公室什么样，像地下洞窟一样有钟乳石？}{%
  \Word{Stalactites}{n.}{钟乳石}
}
\SentenceBlock[0:23:25]{Scroll down to explore our rustic birthing cabins.}{向下滚动，探索我们的乡村分娩小屋}{%
  \Word{rustic}{adj.}{乡村的}
}
\SentenceBlock[0:23:47]{Get all of your snark out now or you're never gonna earn your uncle badge.}{现在把怨言全都说出来，否则永远不让你当舅舅}{%
  \Word{snark}{n.}{挖苦}
}
\SentenceBlock[0:23:50]{You know what? I think I might have some more snark in me. I'm kinda tired.}{是这样，我心中可能还有更多怨言，我有点累了}{%
  \Word{snark}{n.}{挖苦}
}
\SentenceBlock[0:25:30]{His corpse is scheduled to be destroyed by cremation,}{他的尸体将被火化销毁}{%
  \Word{corpse}{n.}{尸体} \Word{cremation}{n.}{火葬}
}
\SentenceBlock[0:25:57]{Verve.}{勇气}{%
  \Word{Verve}{n.}{活力}
}
\SentenceBlock[0:26:05]{Benevolence.}{仁爱}{%
  \Word{Benevolence}{n.}{仁慈}
}
\SentenceBlock[0:26:07]{Nimbleness.}{灵活}{%
  \Word{Nimbleness}{n.}{敏捷}
}
\SentenceBlock[0:26:11]{Probity.}{正直}{%
  \Word{Probity}{n.}{正直}
}
\SentenceBlock[0:26:14]{Wiles.}{狡猾}{%
  \Word{Wiles}{n.}{诡计}
}
\SentenceBlock[0:27:06]{He used to come by my shop. He adored my hibiscus wrap.}{他以前来过我的店，很喜欢我的芙蓉花包装纸}{%
  \Word{adored}{v.}{热爱} \Word{hibiscus}{n.}{芙蓉花}
}
\SentenceBlock[0:27:17]{Well, on the upside, at least now we both have a date.}{往好的方面想，至少现在我们都有伴了}{%
  \Word{upside}{n.}{好的一面}
}
\SentenceBlock[0:31:15]{Tuck you in, warm within}{盖好被子暖洋洋}{%
  \Word{Tuck}{v.}{盖好}
}
\SentenceBlock[0:32:42]{Hush, little baby, don't say a word}{闭嘴，小宝贝，不要说话}{%
  \Word{Hush}{v.}{安静}
}
\SentenceBlock[0:33:55]{-Yeah. -I think I have this cystitis under--}{-是 -我以为膀胱炎已经…}{%
  \Word{cystitis}{n.}{膀胱炎}
}
\SentenceBlock[0:37:35]{Would you mind taking that up to diagnostics for me?}{请你替我把它送去诊断部好吗}{%
  \Word{diagnostics}{n.}{诊断学}
}
\SentenceBlock[0:38:49]{He could slip.}{他可能会滑倒}{%
  \Word{slip}{v.}{滑倒}
}
\SentenceBlock[0:38:54]{It was a thrill to have someone from MDR come see us,}{令人兴奋的是宏观数据精检部的人来拜访我们}{%
  \Word{thrill}{n.}{激动}
}
\SentenceBlock[0:39:50]{No workplace shall be repurposed for slumber.}{工作场所不得睡觉}{%
  \Word{repurposed}{v.}{重新利用} \Word{slumber}{n.}{睡眠}
}
\SentenceBlock[0:39:59]{The original word of Kier: "And I shall whisper to ye dutiful through the ages.}{基尔的原话：“我将对你们这些尽职尽责的人轻声细语，历久弥新}{%
  \Word{dutiful}{adj.}{尽职的}
}
\SentenceBlock[0:40:06]{In your noblest thoughts and epiphanies shall be my voice.}{在你最崇高的思想和顿悟中将有我的声音}{%
  \Word{epiphanies}{n.}{顿悟}
}
\SentenceBlock[0:40:17]{when I am 10 centuries demised.}{长达死后十个世纪之久}{%
  \Word{demised}{v.}{去世}
}
\SentenceBlock[0:40:37]{But I've lived abroad as a vagrant,}{但我曾作为一名流浪汉在国外生活}{%
  \Word{vagrant}{n.}{流浪者}
}
\SentenceBlock[0:40:40]{abstaining from my own money to rely on the charity of strangers.}{放弃了自己的财富，靠陌生人施舍而活}{%
  \Word{abstaining}{v.}{戒除}
}
\SentenceBlock[0:40:45]{Most were beggars themselves, yet they were happy.}{大部分自己就是乞丐，但他们很快乐}{%
  \Word{beggars}{n.}{乞丐}
}
\SentenceBlock[0:42:55]{Sometimes I ask people to sculpt how they feel out of clay.}{有时我会让人用黏土塑造自己的感受}{%
  \Word{sculpt}{v.}{雕刻} \Word{clay}{n.}{黏土}
}
\SentenceBlock[0:43:40]{'Destiny'. An acrostic poem experience by the author, Ricken Hale.}{《命运》 藏头诗 作者：里肯黑尔}{%
  \Word{acrostic}{n.}{藏头诗}
}
\SentenceBlock[0:44:24]{S is for stewardship,}{S是管理}{%
  \Word{stewardship}{n.}{管理}
}
\SentenceBlock[0:44:50]{Until N, meaning newness,}{N意外着新鲜}{%
  \Word{newness}{n.}{新鲜}
}
\SentenceBlock[0:45:00]{That's a question we needn't now ponder.}{那是我们现在无需考虑的问题}{%
  \Word{ponder}{v.}{深思}
}
\SentenceBlock[0:45:04]{For destiny, friends, shall deliver all yonder.}{因为命运，朋友们，会带我们去更好的地方}{%
  \Word{yonder}{adv.}{在远处}
}



\end{document}
