\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S01E02: Half Loop}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:00:02.29]{I acknowledge that, henceforth,}{我同意 从今以后}{%
  \Word{henceforth}{adv.}{从今以后；今后}
}

\SentenceBlock[0:00:09.21]{I will be unable to access outside recollections}{我在卢蒙地下分离楼层时}{%
  \Word{recollections}{n.}{记忆；回忆}
}

\SentenceBlock[0:00:11.80]{whilst on Lumon's severed basement floor,}{将无法想起外面的记忆}{%
  \Word{severed}{adj.}{切断的；分离的}
}

\SentenceBlock[0:00:14.93]{nor retain work memories upon my ascent.}{返回地面楼层时也不会保留工作时的记忆}{%
  \Word{ascent}{n.}{上升；升高}
}

\SentenceBlock[0:00:44.92]{So your work personage will be waking in a few hours on the severed floor.}{几个小时后 你的工作人格会在分离楼层醒来}{%
  \Word{personage}{n.}{人物；角色}
}

\SentenceBlock[0:00:48.34]{But the next time you yourself will be sentient will be this evening,}{但你下次拥有自己的知觉就是今天晚上}{%
  \Word{sentient}{adj.}{有感觉能力的；有意识的}
}

\SentenceBlock[0:00:54.76]{The elevator has a handrail at hip-level if you feel dizzy.}{电梯里在你胯部的高度有扶手 以防你感到头晕}{%
  \Word{handrail}{n.}{扶手}
  \Word{dizzy}{adj.}{头晕的}
}

\SentenceBlock[0:01:12.99]{We'll get you prepped in here.}{我们在这里为你做准备}{%
  \Word{prepped}{v.}{准备（prep的过去式）}
}

\SentenceBlock[0:02:07.66]{Little vibration now.}{现在会有一点震动}{%
  \Word{vibration}{n.}{震动；颤动}
}

\SentenceBlock[0:02:51.96]{Sorry if I freak out on you a little.}{如果我在你面前失控的话 我道歉}{%
  \Word{freak}{v.}{惊慌；失控}
}

\SentenceBlock[0:03:57.48]{we help by bringing them here to the stairwell,}{我们会把他们带到楼梯间来}{%
  \Word{stairwell}{n.}{楼梯间}
}

\SentenceBlock[0:03:59.78]{to experience the transition viscerally.}{帮他们从内心去体验转变的过程}{%
  \Word{viscerally}{adv.}{发自内心地；内在地}
}

\SentenceBlock[0:04:24.72]{Maybe with a little oomph?}{这次带点热情}{%
  \Word{oomph}{n.}{活力；魅力}
}

\SentenceBlock[0:04:49.08]{You're an inquisitive one.}{你的好奇心很强}{%
  \Word{inquisitive}{adj.}{好奇的；爱打听的}
}

\SentenceBlock[0:09:05.71]{You may feel rejuvenated or happy.}{你也许会感觉精力充沛或者快乐}{%
  \Word{rejuvenated}{adj.}{恢复活力的；变年轻的}
}

\SentenceBlock[0:09:09.29]{Less tense in the shoulders. Spry.}{双肩没有那么紧绷 精神抖擞}{%
  \Word{tense}{adj.}{紧张的；绷紧的}
  \Word{Spry}{adj.}{精神矍铄的；活泼的}
}

\SentenceBlock[0:09:16.01]{Yeah, they stagger the entries too so we don't meet on the outside.}{对 他们也会让我们错开进公司 这样就不会在外面遇见}{%
  \Word{stagger}{v.}{错开；交错安排}
}

\SentenceBlock[0:09:53.80]{You'll note I've accrued an embarrassment of wealth in that regard.}{你会注意到 我积累的奖励多得令人不好意思}{%
  \Word{accrued}{v.}{积累；增加（accrue的过去式）}
}

\SentenceBlock[0:10:12.94]{Okay, hazards on, eager lemur.}{好了 小心点 热血少女}{%
  \Word{lemur}{n.}{狐猴}
}

\SentenceBlock[0:10:25.50]{Helly, could you flip on this console?}{赫莉 你能打开这个主机吗}{%
  \Word{flip}{v.}{打开；翻动}
}

\SentenceBlock[0:11:25.35]{Just poke around first. Use the arrows.}{你先试试看 用箭头键}{%
  \Word{poke}{v.}{随便看看；戳}
}

\SentenceBlock[0:11:53.50]{Each category of numbers presents in such an order as to elicit}{每一类数字都以特定顺序出现}{%
  \Word{elicit}{v.}{引出；诱出}
}

\SentenceBlock[0:12:07.56]{They'll be sort of disconcerting, scary.}{它们会有点令人不安 可怕}{%
  \Word{disconcerting}{adj.}{令人不安的；令人困惑的}
}

\SentenceBlock[0:12:19.28]{Are the numbers bloody? Do they chant?}{这些数字残忍吗 它们喊口号吗}{%
  \Word{chant}{v.}{反复吟唱；反复说}
}

\SentenceBlock[0:12:29.41]{Just might be good to peruse when you're between things.}{你不忙的时候最好仔细阅读一下}{%
  \Word{peruse}{v.}{细读；详细考察}
}

\SentenceBlock[0:13:07.32]{Well, since this perceptual version of you only exists at Lumon,}{因为这个感知版本的你只存在于卢蒙}{%
  \Word{perceptual}{adj.}{感知的；知觉的}
}

\SentenceBlock[0:13:27.18]{I'm agog at how well I can tell you're already fitting in.}{你已经和大家打成一片了 我很惊讶}{%
  \Word{agog}{adj.}{兴奋的；急切的}
}

\SentenceBlock[0:15:17.00]{is pretty curtailed.}{是受到极大限制的}{%
  \Word{curtailed}{adj.}{被削减的；受限制的}
}

\SentenceBlock[0:17:05.77]{took 'em from the cubicles and put 'em in the storage closet,}{把照片从办公隔间拿走 放进了储物柜里}{%
  \Word{cubicles}{n.}{小隔间；办公隔间}
}

\SentenceBlock[0:17:36.64]{I mean, her outie filmed a thank-you.}{她外面的自己录制了感谢视频}{%
  \Word{outie}{n.}{外在人格（与“innie”相对）}
}

\SentenceBlock[0:18:30.11]{I also think that melon isn't getting any tastier.}{我还认为现在该吃瓜了}{%
  \Word{tastier}{adj.}{更美味的（tasty的比较级）}
}

\SentenceBlock[0:19:08.73]{Hey, sorry I derailed your game.}{抱歉 我把你的游戏毁了}{%
  \Word{derailed}{v.}{打乱；出轨（derail的过去式）}
}

\SentenceBlock[0:19:26.12]{because our babysitter told you to stop?}{就因为我们的保姆吩咐说别问}{%
  \Word{babysitter}{n.}{保姆；临时照看小孩的人}
}

\SentenceBlock[0:21:20.98]{Shit. Mr. Graner?}{该死 格兰纳先生}{%
  \Word{Graner}{n.}{（专有名词）格兰纳}
}

\SentenceBlock[0:21:43.55]{Hey. I see you've found my wayward trainee.}{嘿 你找到我那任性的受训人员了}{%
  \Word{wayward}{adj.}{任性的；难以控制的}
}

\SentenceBlock[0:22:19.79]{Earnestly.}{诚恳道歉}{%
  \Word{Earnestly}{adv.}{认真地；诚挚地}
}

\SentenceBlock[0:23:51.05]{So you're a doula?}{所以你是一位分娩导乐}{%
  \Word{doula}{n.}{分娩导乐；陪产员}
}

\SentenceBlock[0:23:53.01]{A midwife, actually.}{其实是助产士}{%
  \Word{midwife}{n.}{助产士；接生员}
}

\SentenceBlock[0:26:35.80]{And legalized severance in the workplace?}{还有工作场所的合法分离问题}{%
  \Word{legalized}{adj.}{合法化的}
  \Word{severance}{n.}{切断；解除（合同、关系）}
}

\SentenceBlock[0:27:07.16]{I mean, I heard that some of them are so deluded}{我是说 听说有些人被蒙蔽了}{%
  \Word{deluded}{adj.}{被欺骗的；受蒙蔽的}
}

\SentenceBlock[0:27:28.56]{Are you captive right now?}{你现在处于囚禁中吗}{%
  \Word{captive}{adj.}{被监禁的；受控制的}
}

\SentenceBlock[0:27:34.44]{to be an infantilizing prick to people.}{当一个把别人当成小孩的混蛋}{%
  \Word{infantilizing}{v.}{使幼儿化；使显得幼稚}
  \Word{prick}{n.}{混蛋；讨厌的人}
}

\SentenceBlock[0:27:36.99]{Severance is subjugation, asshole.}{分离是奴役 混蛋}{%
  \Word{subjugation}{n.}{征服；奴役}
}

\SentenceBlock[0:28:46.01]{I'm experimenting with chamomile, so no hard feelings if you gag.}{我在尝试用甘菊 所以如果你作呕请别难过}{%
  \Word{chamomile}{n.}{甘菊}
  \Word{gag}{v.}{作呕；哽咽}
}

\SentenceBlock[0:28:54.35]{Still waiting for that third bulb to revive itself?}{你还在等第三个灯泡自己亮起来吗}{%
  \Word{bulb}{n.}{灯泡；球状物}
}

\SentenceBlock[0:29:05.82]{Sort of. My sister set me up with, like, her doula, or midwife.}{算是吧 我妹妹给我安排了 和她的导乐见面 或是叫助产士}{%
  \Word{doula}{n.}{分娩导乐}
  \Word{midwife}{n.}{助产士}
}

\SentenceBlock[0:29:42.90]{he said he would start building us a house in the hereafter.}{他说会为我们在来世建一栋房子}{%
  \Word{hereafter}{n.}{来世；将来}
}

\SentenceBlock[0:30:14.73]{I'll give you a mugwort bath bomb that'll make you sleep like a rag doll.}{我给你一个艾草气泡浴球 会让你睡得像个死人}{%
  \Word{mugwort}{n.}{艾草}
  \Word{rag}{n.}{破布；（比喻）疲软的人}
}

\SentenceBlock[0:31:24.34]{You'd better be on the stakeout and not}{你最好是在盯梢 而不是出来吃牛排}{%
  \Word{stakeout}{n.}{监视；盯梢}
}


\SentenceBlock[0:32:55.60]{I know your innie will be sad to have missed the day.}{我知道你公司里的自己 会因为错过一天而难过}{%
  \Word{innie}{n.}{内在人格（与“outie”相对）}
}

\SentenceBlock[0:33:21.58]{Wow. Lot a confidence for a man who once got disciplined for dozing.}{天啊 对于一个曾因打瞌睡 遭到惩戒的人来说 你可真自信}{%
  \Word{dozing}{v.}{打瞌睡（doze的现在分词）}
}

\SentenceBlock[0:33:39.68]{Endless toil.}{无尽的劳作}{%
  \Word{toil}{n.}{辛苦；劳作}
}

\SentenceBlock[0:33:48.32]{No. No way. He did his stint in the break room yesterday.}{不 不可能 他昨天已经去休息室受罚了}{%
  \Word{stint}{n.}{一段工作时间；限额}
}

\SentenceBlock[0:33:58.24]{I don't know. He said it was abdominal.}{我不知道 他说肚子不舒服}{%
  \Word{abdominal}{adj.}{腹部的}
}

\SentenceBlock[0:34:44.87]{The erasers are mostly decorative, since we don't have pencils.}{橡皮擦基本上是装饰 因为我们没有铅笔}{%
  \Word{decorative}{adj.}{装饰性的}
}

\SentenceBlock[0:35:01.26]{Which is better than it used to be before Mark's freshman fluke.}{这比马克那次新员工侥幸事件之前要好}{%
  \Word{fluke}{n.}{侥幸；意外成功}
}

\SentenceBlock[0:37:17.40]{We'll deduct the time you spent dozing from your outie's paycheck.}{我们会把你打瞌睡的时间 从你外面的自己的工资里扣除}{%
  \Word{paycheck}{n.}{工资；薪水}
}

\SentenceBlock[0:38:37.60]{Famine, plagues, et cetera.}{饥饿 瘟疫等等}{%
  \Word{Famine}{n.}{饥荒}
  \Word{plagues}{n.}{瘟疫；灾难（plague 的复数）}
}

\SentenceBlock[0:38:46.03]{Populate the sea?}{住到大海里}{%
  \Word{Populate}{v.}{居住于；迁移到}
}

\SentenceBlock[0:38:52.41]{all the deadly eels and shit, 'cause we can't cohabitate with that.}{致命鳗鱼什么的 因为我们不能和那种东西共生}{%
  \Word{eels}{n.}{鳗鱼（eel 的复数）}
  \Word{cohabitate}{v.}{共处；同居}
}

\SentenceBlock[0:39:40.25]{But I've been reintegrated for two weeks now.}{但我已经恢复完整记忆两周了}{%
  \Word{reintegrated}{v.}{重新融合；恢复（reintegrate的过去式）}
}

\SentenceBlock[0:40:32.59]{Reintegration sickness.}{恢复记忆病}{%
  \Word{Reintegration}{n.}{重新整合；复原}
}

\SentenceBlock[0:40:38.98]{Because I'm the first dipshit that's ever had it.}{因为我是第一个得这种病的蠢货}{%
  \Word{dipshit}{n.}{蠢货；笨蛋（俚语）}
}

\SentenceBlock[0:41:38.49]{None may atone for my actions but me, and only in me shall their stain live on.}{除了我 没有人可以为我的行为赎罪 只有在我身上 他们的污点才能继续存在}{%
  \Word{atone}{v.}{赎罪；弥补}
}

\SentenceBlock[0:41:46.71]{my fall cut short by those with wizened hands.}{那些干枯的手阻止了我继续堕落}{%
  \Word{wizened}{adj.}{干瘪的；干枯的}
}

\SentenceBlock[0:43:07.46]{That piece hung in the perpetuity wing for many years.}{这幅画在永恒区挂了很多年}{%
  \Word{perpetuity}{n.}{永恒；永久}
}

\SentenceBlock[0:43:35.28]{I loved that you did the Ambrose cycle in the team-building space last quarter.}{我喜欢你们上个季度 在团建区做的安布罗斯循环}{%
  \Word{Ambrose}{n.}{安布罗斯（专有名词）}
}

\SentenceBlock[0:43:43.45]{Well, it's rare to meet a sophisticate.}{难得遇到一个老练的人}{%
  \Word{sophisticate}{n.}{老练的人；见多识广的人}
}

\SentenceBlock[0:44:53.77]{Because your outie is an exemplary person, these facts should be very pleasing.}{因为你外面的自己是个楷模 这些事实应该是非常令人高兴的}{%
  \Word{exemplary}{adj.}{模范的；典范的}
}

\SentenceBlock[0:46:03.43]{Your outie is splendid and can swim gracefully and well.}{你外面的自己很美好 很会游泳 泳姿优美}{%
  \Word{splendid}{adj.}{极好的；辉煌的}
}

\SentenceBlock[0:46:46.26]{Your outie has no fear of muggers or knaves.}{你外面的自己不惧怕抢劫者或流氓}{%
  \Word{muggers}{n.}{抢劫者（mugger 的复数）}
  \Word{knaves}{n.}{恶棍；无赖（knave 的复数）}
}

\SentenceBlock[0:48:11.64]{Like, what if you wrote the letters funky, like one of those robot tests?}{如果你把字母写得古怪呢 就像那些测试机器人里的字母}{%
  \Word{funky}{adj.}{古怪的；有趣的}
}

\SentenceBlock[0:48:18.19]{Great. Very restorative.}{很好 很有恢复力}{%
  \Word{restorative}{adj.}{有恢复作用的；滋补的}
}

\SentenceBlock[0:48:35.83]{Beg-fucking-pardon. We're supposed to like the perks.}{你说什么 我们就应该喜欢这些奖励}{%
  \Word{perks}{n.}{额外待遇；福利（perk 的复数）}
}

\SentenceBlock[0:48:38.87]{"And all in Lumon's care shall revel in the bounty of the incentives spur."}{“所有人都会得到卢蒙的关怀 在充足奖励的鞭策下狂欢”}{%
  \Word{revel}{v.}{狂欢；陶醉}
  \Word{bounty}{n.}{丰富；慷慨的给予}
  \Word{spur}{n.}{刺激；激励}
}

\SentenceBlock[0:48:42.96]{Don't pervert a handbook passage to me, okay?}{不要对我滥用手册里的段落好吗}{%
  \Word{pervert}{v.}{曲解；滥用}
}

\SentenceBlock[0:48:47.01]{Lumon has been good to us, and it is feckless to--}{卢蒙一直对我们很好 你这样毫无意义}{%
  \Word{feckless}{adj.}{无效的；软弱的；不负责任的}
}

\SentenceBlock[0:49:06.57]{Can you see the perimeter?}{你能看到它的周边吗}{%
  \Word{perimeter}{n.}{边界；周边}
}

\SentenceBlock[0:50:13.68]{Well, I, you know, figured my work self would be pissed}{我觉得我上班的自己会生气}{%
  \Word{pissed}{adj.}{恼火的；生气的（俚语）}
}

\end{document}
