\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S01E03: In Perpetuity}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:00:44.75]{Hey. Are you sure nobody can see in any of these transoms?}{嘿 你确定没人能从横窗望进来吗}{%
  \Word{transoms}{n.}{横窗}%
}
\SentenceBlock[0:01:06.06]{Fortress of solitude.}{孤独的堡垒}{%
  \Word{Fortress}{n.}{堡垒}%
  \Word{solitude}{n.}{孤独}%
}
\SentenceBlock[0:01:16.36]{Dude, I pressed Cobel for an all-floor mixer last quarter.}{哥们 我上季度要求科贝尔举办楼层聚会}{%
  \Word{mixer}{n.}{社交聚会}%
}
\SentenceBlock[0:01:39.72]{With this sickness, I just-- I get disoriented.}{得了这种病 我经常会恍惚}{%
  \Word{disoriented}{adj.}{迷失方向的}%
}
\SentenceBlock[0:04:13.12]{It's like having two different lives suddenly stitched together.}{好像两种不同的生活突然被缝合在了一起}{%
  \Word{stitched}{v.}{缝合}%
}
\SentenceBlock[0:04:37.61]{“They” is a group of people that know severance is a blight on mankind.}{“他们”是一群知道分离手术对人类是一种摧残的人}{%
  \Word{blight}{n.}{摧残}%
  \Word{mankind}{n.}{人类}%
}
\SentenceBlock[0:04:47.82]{The kids trolling for signatures downtown? No, not the fucking WMC.}{那些在市中心征集签名的烦人小子  不 不是该死的健脑会}{%
  \Word{trolling}{v.}{招徕}%
}
\SentenceBlock[0:05:23.15]{You know, it hasn't been a blight for me.}{分离对我来说不是一种摧残}{%
  \Word{blight}{n.}{摧残}%
}
\SentenceBlock[0:08:13.49]{I think it's exactly the condescending verbiage that I'd expect.}{我觉得这种居高临下的措辞正是我预期}{%
  \Word{condescending}{adj.}{居高临下的}%
  \Word{verbiage}{n.}{措辞}%
}
\SentenceBlock[0:08:54.61]{The good news is, those clouds should dissipate somewhere over the Ganz area.}{好消息是 这些云层 会在甘茲地区一带消散}{%
  \Word{dissipate}{v.}{消散}%
}
\SentenceBlock[0:09:10.25]{So wherever you're headed, please do commute with care.}{所以无论你要去哪里 请小心出行}{%
  \Word{commute}{v.}{通勤}%
}
\SentenceBlock[0:09:50.96]{I'm not gonna reintegrate, you know?}{我不会选择恢复记忆 明白吗}{%
  \Word{reintegrate}{v.}{重新整合}%
}
\SentenceBlock[0:11:10.37]{I'm just deicing my stoop.}{我只是在给台阶除冰}{%
  \Word{deicing}{v.}{除冰}%
  \Word{stoop}{n.}{门廊台阶}%
}
\SentenceBlock[0:12:45.84]{Oh, yeah. Dylan took over training in your stead to great success.}{对 迪伦代替你做完了培训 很成功}{%
  \Word{stead}{n.}{代替}%
}
\SentenceBlock[0:12:49.72]{You look trim, Mark. I wonder if you were food poisoned.}{你看起来很瘦 马克 你是不是食物中毒了}{%
  \Word{trim}{adj.}{苗条的}%
}
\SentenceBlock[0:14:12.89]{They clog your outie's pores.}{这会堵住你们外面的自己的毛孔}{%
  \Word{clog}{v.}{堵塞}%
  \Word{pores}{n.}{毛孔}%
}
\SentenceBlock[0:14:18.90]{Also, please refrain from boasting about previously earned waffle parties?}{还有 请克制一点 不要吹嘘 自己曾得到华夫饼派对的奖励}{%
  \Word{refrain}{v.}{克制}%
}
\SentenceBlock[0:14:31.07]{Well, I've never seen a resignation request get such a quick turnaround.}{我从没见过辞职申请这么快得到批复}{%
  \Word{turnaround}{n.}{周转速度}%
}
\SentenceBlock[0:15:25.34]{Shall I, you know, tiptoe up and sneak to the door?}{我要不要蹑手蹑脚地走到门前}{%
  \Word{tiptoe}{v.}{踮脚走}%
  \Word{sneak}{v.}{悄悄行动}%
}

\SentenceBlock[0:17:36.97]{Kay, two things. How do you know what cubist form is?}{好 两个问题 你怎么知道什么是立体主义形式}{%
  \Word{cubist}{adj.}{立体主义的}%
}
\SentenceBlock[0:22:16.25]{So don't burst into the bathroom with your pathetic boss voice on.}{所以不要带着上级的口吻闯入厕所}{%
  \Word{pathetic}{adj.}{可怜的；差劲的}%
}
\SentenceBlock[0:22:24.72]{Okay, I'll give you five minutes to scrub your arms.}{好 我给你五分钟 把胳膊擦干净}{%
  \Word{scrub}{v.}{用力擦洗}%
}
\SentenceBlock[0:22:54.66]{The loathing with which she spoke to you.}{她对你说话时充满了恨意}{%
  \Word{loathing}{n.}{憎恨}%
}
\SentenceBlock[0:22:57.00]{Well, acclimating takes time.}{适应环境是需要时间的}{%
  \Word{acclimating}{v.}{适应}%
}
\SentenceBlock[0:23:15.39]{If it's a deeper meaning she craves, she should see the perpetuity wing.}{如果她渴求更深层次的意义 她应该去永恒区看看}{%
  \Word{craves}{v.}{渴望}%
  \Word{perpetuity}{n.}{永恒}%
}
\SentenceBlock[0:23:29.28]{It just seems premature. I mean, that place is a lot.}{时机似乎还不成熟 那个地方信息量太大}{%
  \Word{premature}{adj.}{过早的}%
}
\SentenceBlock[0:24:09.24]{Did you fill out an official request for supervisory interaction?}{你填写与上级互动的正式申请表了吗}{%
  \Word{supervisory}{adj.}{监督的}%
}
\SentenceBlock[0:25:02.83]{If Petey were the tone-setter you're lionizing him as.}{如果佩蒂像你推崇的那样 能给公司定下基调}{%
  \Word{lionizing}{v.}{吹捧}%
}
\SentenceBlock[0:26:09.90]{My delts are embarrassingly good today. My outie does muscle shows for sure.}{我的三角肌今天非常棒 我外面的自己一定在从事健美秀}{%
  \Word{delts}{n.}{三角肌}%
}
\SentenceBlock[0:26:21.54]{I imagine it's a tiered system.}{我想应该是个分级的系统}{%
  \Word{tiered}{adj.}{分层的}%
}
\SentenceBlock[0:26:24.58]{Perhaps there are monetary prizes for gold, silver and bronze.}{也许金牌 银牌和铜牌有金钱上的奖励}{%
  \Word{monetary}{adj.}{金钱的}%
}
\SentenceBlock[0:26:38.22]{I would think lats carry a high value.}{我觉得背阔肌应该比较值钱}{%
  \Word{lats}{n.}{背阔肌}%
}
\SentenceBlock[0:27:26.56]{And when he asks how long ago you ingested it.}{当他问你多久前吃下这文字的时候}{%
  \Word{ingested}{v.}{摄入}%
}
\SentenceBlock[0:27:58.92]{The power is in your calves. The power is in your calves.}{力量在小腿上 力量在小腿上}{%
  \Word{calves}{n.}{小腿}%
}
\SentenceBlock[0:28:05.26]{All eight CEOs have been of the Eagan lineage.}{所有八位首席执行官都是伊根的血亲}{%
  \Word{lineage}{n.}{血统}%
}
\SentenceBlock[0:28:09.77]{I have a mnemonic poem to help you remember their names.}{我有一首帮助记忆的诗 可以帮你们记住他们的名字}{%
  \Word{mnemonic}{adj.}{助记的}%
}
\SentenceBlock[0:28:12.94]{I authored it myself, and of course, it falls outside corporate canon.}{是我自创的 当然了 不属于公司规定}{%
  \Word{canon}{n.}{准则}%
}
\SentenceBlock[0:28:16.44]{and it's poetically imperfect, to be sure.}{而且从诗词的角度来说并不完美}{%
  \Word{poetically}{adv.}{富有诗意地}%
}
\SentenceBlock[0:28:18.82]{There's a slant rhyme in the second verse. of "Ambrose" to "ban those,"}{第二句有个斜韵 “安布罗斯”和“禁止那些事”}{%
  \Word{slant}{n.}{倾斜；斜韵}%
}
\SentenceBlock[0:28:22.91]{which was necessary to further the narrative, but regrettable.}{这对叙事是必要的 但还是很遗憾}{%
  \Word{regrettable}{adj.}{令人遗憾的}%
}
\SentenceBlock[0:28:26.74]{Ambrose is sometimes unfairly maligned as a black sheep in the annals of the family.}{有时 人们污蔑安布罗斯 是族谱中的另类 这很不公平}{%
  \Word{maligned}{v.}{污蔑}%
  \Word{annals}{n.}{编年史}%
}
\SentenceBlock[0:29:13.29]{Great, very restorative.}{很好 很有助于我恢复}{%
  \Word{restorative}{adj.}{有恢复作用的}%
}
\SentenceBlock[0:29:21.67]{Remember, we'll have those new handbook totes soon.}{要记得 我们很快就有新的手册袋了}{%
  \Word{totes}{n.}{手提袋}%
}
\SentenceBlock[0:29:25.72]{Thanks for the tip. You got business, or you out for a stroll?}{谢谢提醒 你有工作还是出来散步的}{%
  \Word{stroll}{n.}{散步}%
}
\SentenceBlock[0:29:38.15]{Tight department like us gotta keep our synergy up.}{像我们这样关系紧密的部门 必须保持配合默契}{%
  \Word{synergy}{n.}{协同作用}%
}
\SentenceBlock[0:31:07.70]{Salutations.}{问候各位}{%
  \Word{Salutations}{n.}{致意}%
}
\SentenceBlock[0:31:26.26]{Not to be alarmist, but prior to his departure.}{不是杞人忧天 但在他离开前}{%
  \Word{alarmist}{n.}{杞人忧天者}%
}
\SentenceBlock[0:31:52.12]{that the severance procedure is provenly irreversible.}{分离手术经过证明是不可逆的}{%
  \Word{provenly}{adv.}{被证明地}%
}
\SentenceBlock[0:32:10.51]{We are quickly rekindling our yield down here with our nimble new refiner.}{我们正在用新的精检员快速恢复产能}{%
  \Word{rekindling}{v.}{重新点燃}%
  \Word{nimble}{adj.}{灵活的}%
}

\SentenceBlock[0:34:28.56]{Handsome too. See those brows?}{还很英俊 看见他的眉毛了吗}{%
  \Word{brows}{n.}{眉毛}%
}
\SentenceBlock[0:35:35.17]{They wish to know how they should remember me as I rot.}{他们希望在我化成灰烬时 应该将我以何种身份记住}{%
  \Word{rot}{v.}{腐烂}%
}
\SentenceBlock[0:35:41.26]{In my life, I have identified four components, which I call tempers.}{在我这一生中 我鉴别出了四种元素 我称它们为脾气}{%
  \Word{tempers}{n.}{脾性}%
}
\SentenceBlock[0:35:52.81]{Woe. Frolic. Dread. Malice.}{悲哀 嬉笑 恐惧 恶意}{%
  \Word{Woe}{n.}{悲哀}%
  \Word{Frolic}{n.}{嬉戏}%
  \Word{Dread}{n.}{恐惧}%
  \Word{Malice}{n.}{恶意}%
}
\SentenceBlock[0:35:59.70]{Each man's character is defined by the precise ratio that resides in him.}{每个人的性格 由体内这些元素的精确比例决定}{%
  \Word{resides}{v.}{存在于}%
}
\SentenceBlock[0:36:07.37]{I walked into the cave of my own mind, and there I tamed them.}{我进入自己的心灵深处 驯服了这些元素}{%
  \Word{tamed}{v.}{驯服}%
}
\SentenceBlock[0:36:21.39]{It is this great and consecrated power,}{这是一种伟大 神圣的力量}{%
  \Word{consecrated}{adj.}{神圣的}%
}
\SentenceBlock[0:36:25.18]{that I hope to pass on to all of you, my children.}{我希望能够传给你们 我的孩子们}{%
}
\SentenceBlock[0:36:39.86]{what you are is the keeper of an ethos.}{你们都是一种精神的守护者}{%
  \Word{ethos}{n.}{精神特质}%
}
\SentenceBlock[0:37:22.99]{Nimbleness. Probity. Wiles.}{灵活 正直 狡猾}{%
  \Word{Nimbleness}{n.}{灵活}%
  \Word{Probity}{n.}{正直}%
  \Word{Wiles}{n.}{诡计}%
}
\SentenceBlock[0:38:18.54]{So what are we, like, a dental company?}{那么我们是个牙科公司吗}{%
  \Word{dental}{adj.}{牙科的}%
}
\SentenceBlock[0:38:31.72]{Damn, they took down the chick I like.}{该死 他们把我喜欢的小妞换下去了}{%
  \Word{chick}{n.}{女孩（俚语）}%
}
\SentenceBlock[0:39:05.05]{A perfect replica.}{完美的复制品}{%
  \Word{replica}{n.}{复制品}%
}
\SentenceBlock[0:39:59.35]{That's not fair. Up till now, I've been reverent as shit.}{这么说不公平 直到现在我都一直非常虔诚}{%
  \Word{reverent}{adj.}{虔诚的}%
}
\SentenceBlock[0:40:52.11]{So, of course, you'd pervert our founder's message}{当然了 你会用玩笑和不虔诚}{%
  \Word{pervert}{v.}{歪曲}%
}
\SentenceBlock[0:40:54.78]{with jokes and impiety.}{来曲解创始人的意思}{%
  \Word{impiety}{n.}{不虔诚}%
}
\SentenceBlock[0:46:26.41]{None may atone for my actions but me.}{除了我 没有人可以为我的行为赎罪}{%
  \Word{atone}{v.}{赎罪}%
}
\SentenceBlock[0:46:33.83]{I am thankful to have been caught.}{我很感激 自己被抓住了}{%
}
\SentenceBlock[0:46:36.58]{my fall cut short by those with wizened hands.}{干枯的手阻止了我的堕落}{%
  \Word{wizened}{adj.}{干枯的}%
}
\SentenceBlock[0:53:15.73]{I'm just gonna grab the stretcher. I'll be right back.}{我去拿担架 去去就回}{%
  \Word{stretcher}{n.}{担架}%
}


\end{document}
