\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S01E08: What's for Dinner?}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:06:06]{I just wonder if it might be helpful for us to stand behind her and perhaps chant her name}{我在想我们站在她身后高喊她的名字会不会有帮助}{%
\Word{chant}{v.}{反复呼喊；吟唱}%
}

\SentenceBlock[0:07:09]{and you have availed yourself well.}{你工作表现得很出色}{%
\Word{availed}{v.}{使受益；利用（avail oneself of 的过去式）}%
}

\SentenceBlock[0:10:05]{Yes, and spending half of your time farting around the halls.}{是的 你们还用了 一半的时间在走廊里闲逛}{%
\Word{farting}{v.}{鬼混；瞎混（fart around）}%
}

\SentenceBlock[0:11:01]{Mark, all sarcasm aside…}{马克 讽刺的话先放在一边}{%
\Word{sarcasm}{n.}{讽刺；挖苦}%
}

\SentenceBlock[0:12:52]{Your outie has brightened people's days by merely smiling.}{你外面的自己仅仅用微笑 就能令他人心情变好}{%
\Word{brightened}{v.}{使变得明朗；使高兴（brighten 的过去分词）}%
}

\SentenceBlock[0:13:22]{I know I vexed you.}{我知道我让你很苦恼}{%
\Word{vexed}{v.}{使恼火；使烦恼}%
}

\SentenceBlock[0:19:01]{A man whose mind is as sharp as his incisors.}{头脑和门牙一样犀利的人}{%
\Word{incisors}{n.}{门牙}%
}

\SentenceBlock[0:19:41]{Okay, yeah. Let's switch up the vibe in here.}{好 行了 我们来换个气氛吧}{%
\Word{vibe}{n.}{气氛；氛围}%
}

\SentenceBlock[0:20:16]{Yeah, the egg bar is coveted as fuck.}{是的 鸡蛋小吃是大家梦寐以求的}{%
\Word{coveted}{adj.}{梦寐以求的；渴望得到的}%
}

\SentenceBlock[0:23:22]{Endow in each swing of your ax}{每一次挥斧劈砍}{%
\Word{Endow}{v.}{赋予；给予}%
}

\SentenceBlock[0:24:55]{They left us unattended, and thought we'd be too dumb to notice.}{他们不管我们 以为我们太蠢 注意不到}{%
\Word{unattended}{adj.}{无人照看的；无人看管的}%
}

\SentenceBlock[0:28:48]{Your so-called boss may own the clock that taunts you from the wall.}{你所谓的老板虽然拥有计时的钟表 挂在墙上嘲讽着你}{%
\Word{taunts}{v.}{嘲讽；奚落}%
}

\SentenceBlock[0:29:42]{That'd be a hoot.}{那就太有趣了}{%
\Word{hoot}{n.}{非常有趣的人或事}%
}

\SentenceBlock[0:33:44]{Filth and fucking fire until she fucking dies!}{肮脏的贱人不得好死}{%
\Word{Filth}{n.}{污秽；肮脏；淫秽}%
}

\SentenceBlock[0:39:19]{- The elusive Mark. - Never thought of myself as elusive.}{- 行踪难觅的马克 - 我从来没觉得自己行踪难觅}{%
\Word{elusive}{adj.}{难以捉摸的；难找的；难以理解的}%
}

\SentenceBlock[0:40:13]{Gross. Hey, do you wanna give me your coat?}{恶心 嘿 把大衣给我吧}{%
\Word{Gross}{adj.}{令人恶心的；粗俗的}%
}

\SentenceBlock[0:40:24]{Oh, yeah. All glory unto Devon.}{是 一切荣耀归于德文}{%
\Word{unto}{prep.}{向；到（古语，用于文学或宗教语境）}%
}

\SentenceBlock[0:40:31]{Yeah. I've been pondering a decently-sized life change.}{是 我一直在考虑 做出一个巨大的生活改变}{%
\Word{pondering}{v.}{沉思；考虑}%
}

\SentenceBlock[0:40:43]{Watch for leakies, Mark.}{马克 小心宝宝尿你一身}{%
\Word{leakies}{n.}{尿液渗漏（婴儿用语，非正式）}%
}

\SentenceBlock[0:41:21]{I am sorry I was so terse before.}{很抱歉我之前对你态度冷淡}{%
\Word{terse}{adj.}{简短而生硬的；冷淡的}%
}

\SentenceBlock[0:43:55]{- I don't mean to be nosy, but… - No, no.}{- 我不想多管闲事 但… - 不会…}{%
\Word{nosy}{adj.}{爱管闲事的}%
}

\SentenceBlock[0:44:25]{Beehive.}{蜂窝}{%
\Word{Beehive}{n.}{蜂窝；蜂箱}%
}

\SentenceBlock[0:44:28]{Lullaby, open house, overtime.}{摇篮曲 开放参观 加班}{%
\Word{Lullaby}{n.}{摇篮曲}%
\Word{overtime}{n.}{加班；超时工作}%
}



\end{document}
