\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S01E05: The Grim Barbarity Of Optics and Design}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:05:02]{She has severe bruising but, thankfully, no permanent damage.}{她瘀伤很严重 但谢天谢地 没有永久性损伤}{%
  \Word{bruise}{n.}{瘀伤}
}

\SentenceBlock[0:06:33]{A society with festering workers cannot flourish,}{一个社会如果工人们心怀不满 就不可能繁荣昌盛}{%
  \Word{fester}{v.}{恶化；（指情绪）积压}
  \Word{flourish}{adj.}{兴旺的}
}

\SentenceBlock[0:07:12]{Bullies are nothing but Bull and Lies.}{霸凌者除了狂言和谎言外一无所有}{%
  \Word{bully}{n.}{恃强凌弱者}
  \Word{bull}{n.}{胡说八道}
}

\SentenceBlock[0:07:21]{They cannot crucify you if your hand is in a fist.}{如果你握紧拳头 他们就无法把你钉在十字架上}{%
  \Word{crucify}{v.}{严厉惩罚；钉上十字架}
  \Word{fist}{n.}{拳头}
}

\SentenceBlock[0:07:27]{Should you find yourself contorting to fit a system, dear reader,}{亲爱的读者 如果你发现 自己向一种体制低头}{%
  \Word{contort}{v.}{扭曲（以适应）}
}

\SentenceBlock[0:07:46]{Full synaptic coupling. Petey Kilmer's memory was reintegrated.}{突触完全融合 佩蒂吉尔莫的记忆恢复了}{%
  \Word{synaptic}{adj.}{突触的}
}

\SentenceBlock[0:08:14]{Comb the chip data for source signatures.}{梳理芯片数据 寻找源头特征}{%
  \Word{comb}{v.}{仔细搜查；梳理}
}

\SentenceBlock[0:10:01]{The contractions are about 20 minutes apart,}{宫缩大约20分钟一次}{%
  \Word{contraction}{n.}{收缩；（尤指分娩时的）子宫收缩}
}

\SentenceBlock[0:11:05]{All right. Well, glad to be here in this cozy nook.}{好吧 很高兴能待在这个温馨的小屋}{%
  \Word{cozy}{adj.}{温馨的；舒适的}
  \Word{nook}{n.}{角落；隐蔽处}
}

\SentenceBlock[0:11:11]{- Yeah. - It's, like, psychotically expensive.}{- 看见了 - 贵到了病态的地步}{%
  \Word{psychotically}{adv.}{精神病般地；疯狂地}
}

\SentenceBlock[0:11:14]{It's like a freakin' lodge. I hate whoever's in there.}{就像个别墅 不管里面是谁我都讨厌}{%
  \Word{lodge}{n.}{小屋；旅舍}
}

\SentenceBlock[0:11:16]{It's just fat cats making fat kittens.}{就是暴发户在生肥仔}{%
  \Word{kitten}{n.}{小猫；（喻）年轻一代}
}

\SentenceBlock[0:11:23]{It's a contraction.}{是宫缩}{%
  \Word{contraction}{n.}{宫缩；收缩}
}

\SentenceBlock[0:11:29]{- What? - The fetus is drawn to clear air.}{- 什么  - 胎儿喜欢坦诚的环境}{%
  \Word{fetus}{n.}{胎儿}
}

\SentenceBlock[0:11:32]{Purging secrets can create a soul void that speeds the labor.}{说出秘密会留下灵魂的空洞 能加速分娩}{%
  \Word{purge}{v.}{清除；净化}
}

\SentenceBlock[0:14:12]{Thank you for narcotics.}{谢谢你的麻醉剂}{%
  \Word{narcotic}{n.}{麻醉剂；致幻毒品}
}

\SentenceBlock[0:14:32]{Three kiddos. I'm so fucking scared of ruining one child.}{三个孩子 我很怕一个孩子都养不好}{%
  \Word{kiddos}{n.}{小孩（口语）}
}

\SentenceBlock[0:14:39]{- Lotta help, I guess. - Yeah.}{- 大概是得到了很多帮助吧 - 是}{%
  \Word{lotta}{adj.}{很多的（=a lot of，口语）}
}

\SentenceBlock[0:17:05]{What do you mean? Like, with your paychecks?}{什么意思 给你的工资有问题}{%
  \Word{paycheck}{n.}{薪水；工资支票}
}

\SentenceBlock[0:19:58]{So they locked away the extension cords and other dangerous items so, you know,}{他们把延长线 和其他危险物品锁起来了 所以}{%
  \Word{cord}{n.}{电线；绳索}
}

\SentenceBlock[0:20:46]{We should hide inspirational handbook quotes}{我们应该把鼓舞人心的手册语录}{%
  \Word{inspirational}{adj.}{鼓舞人心的}
}

\SentenceBlock[0:20:54]{She just needs to start earning perks, dude.}{她只是需要开始赢得员工奖励 哥们}{%
  \Word{perk}{n.}{额外津贴；好处}
}

\SentenceBlock[0:21:24]{and verbally encourage her to forgo further suicide attempts.}{并用语言鼓励她放弃未来自杀的念头}{%
  \Word{forgo}{v.}{放弃；弃绝}
}

\SentenceBlock[0:22:11]{No. I'm peachy.}{不 我很开心}{%
  \Word{peachy}{adj.}{极好的；很棒的（口语）}
}

\SentenceBlock[0:23:35]{And I'd like to seek Burt's counsel.}{我想咨询一下伯特}{%
  \Word{counsel}{n.}{建议；法律顾问}
}

\SentenceBlock[0:25:00]{It's proof. It is ironclad proof.}{这是证据 是铁证}{%
  \Word{ironclad}{adj.}{坚不可摧的；无懈可击的}
}

\SentenceBlock[0:25:23]{How do we know what else he isn't being kosher about?}{我们怎么知道他还隐瞒了什么事}{%
  \Word{kosher}{adj.}{正当的；合乎规定的（尤指犹太教规）}
}

\SentenceBlock[0:25:51]{I thought it might dissuade him from spending so much time with Burt G.}{我认为这会阻止他 花那么多时间和伯特G待在一起}{%
  \Word{dissuade}{v.}{劝阻}
}

\SentenceBlock[0:26:20]{"The light of discovery shines truer upon a virgin meadow than a beaten path."}{“发现之光照耀在一片处女地上 比在一条破旧的小路上更真实”}{%
  \Word{truer}{adj.}{更真实的（true 的比较级）}
  \Word{virgin}{adj.}{未开发的；未被破坏的}
  \Word{beaten}{adj.}{被踩踏的；常走的（beaten path）}
}

\SentenceBlock[0:30:20]{Yeah. Since you've been gone, I've been trying to recreate it on my lunch breaks.}{对 你离开后 我在午餐休息时 一直在尝试把它重新画出来}{%
  \Word{recreate}{v.}{重新创造；再现}
}

\SentenceBlock[0:32:01]{You want to get disemboweled today?}{你今天想被开膛破肚吗}{%
  \Word{disembowel}{v.}{剖腹；取出内脏}
}

\SentenceBlock[0:32:03]{Hey, where's your friends? Plural.}{嘿 你的朋友们呢 复数的}{%
  \Word{plural}{adj.}{复数的}
}

\SentenceBlock[0:33:19]{- If I could just explain-- - Save it, marauder.}{- 让我解释… - 省省吧 侵略者}{%
  \Word{marauder}{n.}{掠夺者；侵略者}
}

\SentenceBlock[0:34:28]{It's literally silly. Like, they say you all have pouches.}{真的很蠢 比如他们说你们都有育儿袋}{%
  \Word{pouch}{n.}{育儿袋；小袋}
}

\SentenceBlock[0:34:32]{- Pouches? Like to carry young? - Yes.}{- 育儿袋 装小孩子用的  - 对}{%
  \Word{pouch}{n.}{育儿袋；小袋}
}

\SentenceBlock[0:34:36]{According to some, you each have a larval offspring}{有些人还说你们每个人都有一个幼虫后代}{%
  \Word{larval}{adj.}{幼虫的}
}

\SentenceBlock[0:34:43]{That's fucking psycho.}{这真是疯了}{%
  \Word{psycho}{adj.}{疯狂的；精神病的}
}

\SentenceBlock[0:34:50]{- Yeah. - Though, I'd be remiss not to say}{- 是 - 不过我有责任要说}{%
  \Word{remiss}{adj.}{疏忽的；懈怠的}
}

\SentenceBlock[0:34:53]{that in this theory, the larva eventually eats and replaces you.}{在这个理论中 幼虫最终会将你们吃掉 取而代之}{%
  \Word{larva}{n.}{幼虫}
}

\SentenceBlock[0:35:33]{This guy's O and goddamn D, who are duplicitous snakes to a one.}{这人来自光学与设计部 他们部门的人都很奸诈}{%
  \Word{duplicitous}{adj.}{奸诈的；口是心非的}
}

\SentenceBlock[0:36:55]{"The Grim Barbarity of Optics and Design "?}{“光学与设计部可怕的暴行”}{%
  \Word{barbarity}{n.}{暴行；野蛮}
}

\SentenceBlock[0:37:03]{What kind of barbarities were we enacting?}{我们到底有什么暴行啊}{%
  \Word{barbarity}{n.}{暴行；残忍}
}

\SentenceBlock[0:37:09]{I mean, I'll have to confer with my larva, of course.}{当然了 我必须咨询一下我的幼虫}{%
  \Word{larva}{n.}{幼虫}
}

\SentenceBlock[0:37:25]{relationships beyond the platonic are frowned upon anyway.}{超越柏拉图式的关系反正是会遭到反对的}{%
  \Word{platonic}{adj.}{柏拉图式的；非肉体关系的}
  \Word{frown}{v.}{反对；皱眉}
}

\SentenceBlock[0:38:10]{The Courtship of Kier and Imogene.}{《基尔和伊莫金的求爱》}{%
  \Word{courtship}{n.}{求爱；恋爱期}
}

\SentenceBlock[0:38:14]{He met his wife while a stewman in an ether factory.}{他是在一家乙醚工厂 当工人时认识他妻子的}{%
  \Word{ether}{n.}{乙醚；醚类化合物}
}

\SentenceBlock[0:38:23]{She was a swab girl.}{她是个清洁工}{%
  \Word{swab}{n.}{清洁工；拖把}
}

\SentenceBlock[0:39:05]{Look at the badges the raiders are wearing.}{看那些突袭者佩戴的胸卡}{%
  \Word{raider}{n.}{袭击者；侵入者}
}

\SentenceBlock[0:39:17]{It's called "The Macrodata Refinement Calamity."}{这幅画名叫“宏观数据精检部的灾难”}{%
  \Word{calamity}{n.}{灾难；大祸}
}

\SentenceBlock[0:41:07]{The surest way to tame a prisoner is to let him believe he's free.}{驯服一个囚犯的最可靠方法 是让他相信自己是自由的}{%
  \Word{tame}{v.}{驯服；制服}
}





\end{document}
