\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S01E07: Defiant Jazz}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:01:57]{I hate that term, "innie." So infantilizing.}{我讨厌“公司里的自己”这个词 把人当婴儿看}{%
  \Word{infantilizing}{v.}{使幼稚化；把……当小孩看待}%
}
\SentenceBlock[0:02:36]{Maybe he dreams every day about clawing his way to the surface.}{也许他每天都梦想着能逃离那里}{%
  \Word{clawing}{v.}{费力地移动；用爪子抓}%
}
\SentenceBlock[0:10:48]{Maybe we should talk later over a nice hot cup of lavender tea?}{也许我们应该稍后一边喝美味的 热薰衣草茶 一边谈谈}{%
  \Word{lavender}{n.}{薰衣草}%
}
\SentenceBlock[0:10:59]{Jack Frost certainly needs some new dandruff shampoo.}{冬将军真的需要去屑洗发水}{%
  \Word{Frost}{n.}{霜；冬将军（拟人化的寒冷）}%
  \Word{dandruff}{n.}{头皮屑}%
}
\SentenceBlock[0:13:49]{What happened last night is called the overtime contingency.}{昨晚的事叫做紧急加班}{%
  \Word{contingency}{n.}{突发事件；意外情况}%
}
\SentenceBlock[0:14:44]{I'm gonna see about rustling you up some special perks.}{我会争取为你准备一些特殊奖励的}{%
  \Word{rustling}{v.}{迅速准备；发出沙沙声}%
  \Word{perks}{n.}{额外福利；特权}%
}
\SentenceBlock[0:16:03]{I'm here to escort you to your desk.}{我是来陪你去你的办公桌的}{%
  \Word{escort}{v.}{护送；陪同}%
}
\SentenceBlock[0:17:00]{These doors help us to ensure you all are tucked nicely in your work spaces.}{这道门帮助我们确保 你们都好好待在工作空间里}{%
  \Word{tucked}{v.}{藏起；安顿好}%
}
\SentenceBlock[0:18:10]{while cradling the top of the neck, just so.}{同时这样扶住脖子的上部}{%
  \Word{cradling}{v.}{轻托；抱着}%
}
\SentenceBlock[0:18:15]{Exhale softly. Just a whisper of a breeze.}{轻轻呼气 吹出一小缕微风就好}{%
  \Word{Exhale}{v.}{呼气}%
  \Word{breeze}{n.}{微风}%
}
\SentenceBlock[0:18:24]{Show the baby the areola, and we latch.}{给宝宝看乳晕 让宝宝咬住乳头}{%
  \Word{areola}{n.}{乳晕}%
  \Word{latch}{v.}{咬住；锁住}%
}
\SentenceBlock[0:18:52]{Baby sips, baby sips.}{宝宝吃奶…}{%
  \Word{sips}{v.}{小口喝}%
}
\SentenceBlock[0:19:14]{- Yes, like an angry fire hose. - Oh, no!}{- 对 像个愤怒的消防水管 - 不}{%
  \Word{hose}{n.}{软管；水管}%
}
\SentenceBlock[0:19:34]{Besides, it's not as if you have a fleet of nannies and manservants}{而且 你又没有一群保姆和男仆}{%
  \Word{manservants}{n.}{男仆}%
}
\SentenceBlock[0:19:45]{I met this rich woman at the birthing retreat.}{我在分娩中心认识了一位富婆}{%
  \Word{retreat}{n.}{静修地；疗养地}%
}
\SentenceBlock[0:19:59]{What a snoot.}{真是个势利眼}{%
  \Word{snoot}{n.}{势利眼的人；傲慢的人}%
}
\SentenceBlock[0:21:43]{Shouldn't there be labels on the soap dispensers saying, "soap"?}{皂液器上不是应该 有标签写着“洗手液”吗}{%
  \Word{dispensers}{n.}{分发器；自动取用装置}%
}
\SentenceBlock[0:22:56]{- Why for you? - And I thought a little frivolity,}{- 你为什么也难  - 我认为轻松一下}{%
  \Word{frivolity}{n.}{轻浮；嬉闹}%
}
\SentenceBlock[0:23:01]{Helly, please approach the MDE cart.}{赫莉 请靠近伴乐起舞体验推车}{%
  \Word{cart}{n.}{小推车}%
}
\SentenceBlock[0:23:06]{You may choose one genre and one accessory.}{你可以选择一种音乐类型和一个乐器}{%
  \Word{accessory}{n.}{配件；附属品}%
}
\SentenceBlock[0:23:15]{The maraca. Excellent choice.}{响葫芦 选得好}{%
  \Word{maraca}{n.}{响葫芦（打击乐器）}%
}
\SentenceBlock[0:23:18]{Should've gone for the castanets.}{应该选响板的}{%
  \Word{castanets}{n.}{响板（打击乐器）}%
}
\SentenceBlock[0:23:22]{I choose "Defiant Jazz."}{我选“叛逆的爵士乐”}{%
  \Word{Defiant}{adj.}{反抗的；叛逆的}%
}
\SentenceBlock[0:26:05]{He needs a full tetanus toxoid panel.}{他需要做全面的破伤风类毒素检查}{%
  \Word{tetanus}{n.}{破伤风}%
  \Word{toxoid}{n.}{类毒素}%
}
\SentenceBlock[0:26:52]{On the outside. It's called the overtime contingency.}{在公司外面 这叫紧急加班}{%
  \Word{contingency}{n.}{突发事件；应急情况}%
}
\SentenceBlock[0:27:56]{We can find whatever they use to control it and, you know, commandeer it.}{我们可以找到他们用来 控制唤醒的东西 然后夺过来}{%
  \Word{commandeer}{v.}{强行征用；夺取}%
}
\SentenceBlock[0:28:04]{But, Helly, forgive me, but that's perverse. We're innies.}{但是 赫莉 原谅我 这是错误的 我们是公司里的自己}{%
  \Word{perverse}{adj.}{反常的；不合常理的}%
}
\SentenceBlock[0:29:46]{No cavalry yet.}{还没有骑兵来救场}{%
  \Word{cavalry}{n.}{骑兵部队}%
}


\SentenceBlock[0:31:48]{What's the name of that thing? The oversight something?}{那东西叫什么 加班什么的}{%
  \Word{oversight}{n.}{监管；疏忽}%
}
\SentenceBlock[0:33:19]{without intermediaries.}{不靠中间人}{%
  \Word{intermediaries}{n.}{中间人；中介}%
}
\SentenceBlock[0:34:29]{So, no one is in there? That's lax as fuck.}{所以那里没人 这安保也太不严密了}{%
  \Word{lax}{adj.}{松懈的；不严格的}%
}
\SentenceBlock[0:34:45]{You just engage the trackball, type the code,}{只要激活跟踪球 键入号码}{%
  \Word{trackball}{n.}{轨迹球（电脑控制设备）}%
}
\SentenceBlock[0:35:18]{Yeah, see. There are two lever switches that you have to hold open}{对 你看 有两个杠杆开关 必须一直保持开启}{%
  \Word{lever}{n.}{杠杆；操纵杆}%
}
\SentenceBlock[0:37:18]{The impression you've left on me is indelible,}{你们给我留下的印象是不可磨灭的}{%
  \Word{indelible}{adj.}{难以去除的；无法忘记的}%
}
\SentenceBlock[0:37:22]{though I'm unaware of it on a conscious level, and…}{虽然我意识不到 并且…}{%
  \Word{unaware}{adj.}{未察觉的；不知道的}%
}
\SentenceBlock[0:37:30]{I have no recollection of actually ever meeting you,}{我没有和你们见面的记忆}{%
  \Word{recollection}{n.}{记忆；回忆}%
}
\SentenceBlock[0:37:53]{Bon voyage.}{一路顺风}{%
  \Word{Bon}{adj.}{（法语）好的，祝福的（常与voyage连用）}%
  \Word{voyage}{n.}{航行；旅行}%
}
\SentenceBlock[0:38:30]{You smug motherfucker.}{你这个自以为是的混蛋}{%
  \Word{smug}{adj.}{自鸣得意的；自以为是的}%
}
\SentenceBlock[0:38:42]{No one can rip them away from you, snuff them out.}{没人能把它们从你脑中夺走 摧毁}{%
  \Word{snuff}{v.}{熄灭；掐灭}%
}
\SentenceBlock[0:39:20]{the founder or his progeny.}{公司创始人及其后代受到羞辱}{%
  \Word{progeny}{n.}{子孙；后代}%
}
\SentenceBlock[0:40:47]{The shadows of misty yesteryears}{往昔那些朦胧的影子}{%
  \Word{misty}{adj.}{朦胧的；模糊的}%
  \Word{yesteryears}{n.}{往昔；过去的岁月}%
}
\SentenceBlock[0:41:12]{Reach back for the joy and the sorrow}{回顾欢乐与伤悲}{%
  \Word{sorrow}{n.}{悲伤；伤感}%
}
\SentenceBlock[0:47:21]{The children's carousel}{孩子们的旋转木马}{%
  \Word{carousel}{n.}{旋转木马；旋转平台}%
}
\SentenceBlock[0:47:28]{The chestnut tree}{那棵栗子树}{%
  \Word{chestnut}{n.}{栗子；栗树}%
}
\SentenceBlock[0:47:42]{My wife was allergic to nutmeg.}{我妻子对肉豆蔻过敏}{%
  \Word{nutmeg}{n.}{肉豆蔻（香料）}%
}
\SentenceBlock[0:47:49]{And when she sneezed, she always sneezed twice.}{她打喷嚏时总是会打两次}{%
  \Word{sneezed}{v.}{打喷嚏}%
}
\SentenceBlock[0:48:04]{My wife thought cardigans looked ridiculous.}{我妻子认为毛衣开衫看起来很可笑}{%
  \Word{cardigans}{n.}{毛衣开衫}%
}


\end{document}
