\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S01E09: The We We Are}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:00:34]{Yes. I'm sorry, I just-- I got a little woozy and then--}{是 抱歉 我只是 呃 刚才有点晕 呃…}{%
  \Word{woozy}{adj.}{头昏眼花的}
}

\SentenceBlock[0:01:36]{I don't know if I hate senators or congressmen more.}{我不知道 自己更讨厌参议员还是众议员}{%
  \Word{congressman}{n.}{众议员}
}

\SentenceBlock[0:01:44]{Good. We need you nimble. We gotta get down there. You're on in 20.}{很好 我们需要你思维机敏 我们必须下去了 你20分钟后上场}{%
  \Word{nimble}{adj.}{敏捷的；机敏的}
}

\SentenceBlock[0:04:46]{Mark. You okay, milady?}{马克 夫人 你没事吧}{%
  \Word{milady}{n.}{夫人；贵妇}
}

\SentenceBlock[0:07:19]{And I have some sores on the back of my head from my bird.}{我后脑勺上还有我家鸟啄的伤口}{%
  \Word{sore}{n.}{伤口；疮}
}

\SentenceBlock[0:07:52]{so if you'd all peacefully waft in the living room…}{所以请大家安静地到客厅来…}{%
  \Word{waft}{v.}{飘荡；漂浮}
}

\SentenceBlock[0:08:51]{I've gotta hop backstage.}{我要去后台了}{%
  \Word{hop}{v.}{跳跃；快速移动}
  \Word{backstage}{adv.}{在后台}
}

\SentenceBlock[0:09:05]{I mean, the idea that people would want to outlaw severance.}{我是说 人们居然有想取缔分离的想法}{%
  \Word{outlaw}{v.}{宣布为非法；取缔}
}

\SentenceBlock[0:10:43]{Sorry, you can't unring}{抱歉 显然无法关掉}{%
  \Word{unring}{v.}{（比喻）无法撤回或取消（某种行为或言语）}
}

\SentenceBlock[0:10:58]{that I would like to thank first and foremost.}{是我首要的感谢对象}{%
  \Word{foremost}{adv.}{首先；最重要地}
}

\SentenceBlock[0:11:01]{Family is both my bedrock and my inspiration.}{呃 家庭既是我的基石 也是我的灵感来源}{%
  \Word{bedrock}{n.}{基础；根基}
}

\SentenceBlock[0:11:06]{So I dedicate the reading to my firstborn daughter,}{所以我把这次读书献给我的第一个女儿}{%
  \Word{dedicate}{v.}{献给；致力于}
  \Word{firstborn}{adj.}{头胎的；第一个出生的}
}

\SentenceBlock[0:11:50]{I can crane.}{我可以伸长脖子看}{%
  \Word{crane}{v.}{伸长（脖子）}
}

\SentenceBlock[0:13:52]{to the cowering shrew,}{还是畏缩的鼩鼱}{%
  \Word{cower}{v.}{畏缩}
  \Word{shrew}{n.}{鼩鼱；泼妇}
}

\SentenceBlock[0:14:00]{Yet the cat eats the shrew, and we, like Schrödinger,}{然而猫吃鼩鼱 而我们就像薛定谔一样}{%
  \Word{shrew}{n.}{鼩鼱；泼妇}
}

\SentenceBlock[0:14:20]{Balf. Prepare the neti pot.}{呃 巴尔夫 准备洗鼻壶}{%
  \Word{neti}{adj.}{洗鼻的（源自瑜伽术语）}
}

\SentenceBlock[0:14:23]{It was transformative.}{这观点太具革命性了}{%
  \Word{transformative}{adj.}{有变革性的}
}

\SentenceBlock[0:14:27]{What a wordsmith. He seemed to have a little something in his throat.}{真是个语言大师 他喉咙里好像有什么东西}{%
  \Word{wordsmith}{n.}{语言大师；善于措辞的人}
}

\SentenceBlock[0:15:02]{prattling on about sauces.}{喋喋不休地谈论着酱料}{%
  \Word{prattle}{v.}{唠叨；喋喋不休}
}

\SentenceBlock[0:15:07]{Jesus, why do I ever open my buffoon mouth?}{天啊 我为什么要张开小丑一样的嘴}{%
  \Word{buffoon}{n.}{小丑；粗俗愚蠢的人}
}

\SentenceBlock[0:15:52]{and I found one of the four of us on the crest hike.}{我看到一张我们四人 在太平洋屋脊步道远足的照片}{%
  \Word{crest}{n.}{山顶；山脊}
}

\SentenceBlock[0:16:07]{Mark, I need to flush my sinuses.}{马克 我要洗一下鼻窦}{%
  \Word{sinus}{n.}{鼻窦}
}

\SentenceBlock[0:16:32]{you suddenly became tense. What was that?}{突然变得很紧张 怎么回事}{%
  \Word{tense}{adj.}{紧张的}
}

\SentenceBlock[0:18:00]{No, I know. I just have to deal with her. She's having a meltdown.}{是 我知道 我要先处理好她 她正情绪崩溃呢}{%
  \Word{meltdown}{n.}{情绪崩溃}
}

\SentenceBlock[0:19:13]{My dad used to make me recite the nine core principles before bed every night}{我爸爸以前要求我每晚睡觉前背诵九大核心原则}{%
  \Word{recite}{v.}{背诵；朗诵}
}

\SentenceBlock[0:19:44]{But I took a severed job because it sounds freaking awesome.}{但我接受记忆分离的工作 是因为这听起来太酷了}{%
  \Word{freaking}{adj.}{非常的（用于加强语气）}
}

\SentenceBlock[0:23:13]{The Grandfather would cherish what you've done.}{爷爷会珍惜你的所作所为的}{%
  \Word{cherish}{v.}{珍惜}
}

\SentenceBlock[0:23:17]{And one day you will sit with me at my revolving.}{将来有一天 你会在我的轮回仪式上坐在我的身旁}{%
  \Word{revolve}{v.}{旋转；（此处作名词用，虚构仪式）}
}

\SentenceBlock[0:25:00]{None may atone for my actions… but me.}{除了我 没有人可以为我的行为赎罪}{%
  \Word{atone}{v.}{赎罪；弥补}
}

\SentenceBlock[0:28:26]{He hoped you'd be spared from the pain.}{他希望你可以免受痛苦的折磨}{%
  \Word{spare}{v.}{使免受（伤害、痛苦等）}
}

\SentenceBlock[0:31:08]{Kind of a flowy, purple outfit, silver hair.}{有些飘逸的紫色服装 一头银发}{%
  \Word{flowy}{adj.}{飘逸的}
}

\SentenceBlock[0:31:58]{While most cultures view sex as ugly or foul,}{虽然在大部分文化里 性是丑陋或肮脏的}{%
  \Word{foul}{adj.}{肮脏的；令人不快的}
}

\SentenceBlock[0:33:04]{I can get you any perk you want, Dylan.}{我能给你任何想要的奖励 迪伦}{%
  \Word{perk}{n.}{额外待遇；福利}
}

\SentenceBlock[0:33:09]{There's paintball, there's coffee cozies.}{有…漆弹 有咖啡杯套}{%
  \Word{paintball}{n.}{彩弹射击游戏}
}

\SentenceBlock[0:34:25]{I'll tee you up. Just stick to the talking points.}{我会先介绍你一下 不要偏离演讲要点就好}{%
  \Word{tee}{v.}{为某人做准备；引介}
}

\SentenceBlock[0:35:56]{…improvements in morale,}{…士气的提高}{%
  \Word{morale}{n.}{士气}
}

\SentenceBlock[0:36:00]{As with any transformative technology, there have been setbacks.}{和任何变革性的科技一样 我们也遇到了挫折}{%
  \Word{setback}{n.}{挫折}
}

\SentenceBlock[0:36:04]{Bumps in the road.}{遇到了坎坷}{%
  \Word{bump}{n.}{障碍；困难}
}

\SentenceBlock[0:36:05]{But I'm here tonight to tell you that we are on the verge of a revolution.}{但我今晚要告诉大家 我们正处于革命的边缘}{%
  \Word{verge}{n.}{边缘}
}

\SentenceBlock[0:36:10]{A kind and empathetic revolution,}{善良而富有同情心的革命}{%
  \Word{empathetic}{adj.}{有同理心的；体恤的}
}


\end{document}
