\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S02E01: Hello, Ms. Cobel}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:04:21]{You can leave the balloons in the foyer by my old desk.}{你可以把气球放在我旧桌子边的门厅里。}{%
  \Word{foyer}{n.}{门厅；门廊}
}

\SentenceBlock[0:05:06]{Excuse the clutter.}{房间很乱，你别介意。}{%
  \Word{clutter}{n.}{凌乱；杂乱}
}

\SentenceBlock[0:05:50]{Shortly before your mutiny, we installed security doors}{你们叛变之后，我们安装了安全门。}{%
  \Word{mutiny}{n.}{叛变；暴动}
}

\SentenceBlock[0:05:55]{This accompanied a punitive rendition of the Kier hymn performed by Ms. Cobel.}{此外，科贝尔女士还会唱诵基尔圣歌的惩罚版本。}{%
  \Word{punitive}{adj.}{惩罚性的}
  \Word{rendition}{n.}{表演；演奏}
  \Word{hymn}{n.}{圣歌；赞美诗}
}

\SentenceBlock[0:06:20]{we've been asking how a sadist like Harmony Cobel,}{我们一直在自问，像哈蒙妮·科贝尔这样的虐待狂，}{%
  \Word{sadist}{n.}{施虐狂；虐待狂}
}

\SentenceBlock[0:06:23]{could take fertile root in Lumon soil.}{怎能在卢蒙的土壤上扎根和生长。}{%
  \Word{fertile}{adj.}{肥沃的；可繁殖的}
}

\SentenceBlock[0:06:40]{We believe she'd developed an erotic fixation on you,}{我们认为她对你产生了一种痴迷。}{%
  \Word{erotic}{adj.}{色情的；性欲的}
  \Word{fixation}{n.}{痴迷；迷恋}
}

\SentenceBlock[0:06:46]{in what might be termed "a throuple."}{希望你们成为“三人情侣”。}{%
  \Word{throuple}{n.}{三人情侣关系}
}

\SentenceBlock[0:08:23]{It's a little cramped compared to our old MDR,}{和原来的宏观数据精检比起来，这里有点狭小。}{%
  \Word{cramp}{adj.}{狭小的；拥挤的}
}

\SentenceBlock[0:08:27]{Ours was a crème brûlée and the keyboards were puce.}{我们的地毯是焦糖奶油色，键盘是紫红色的。}{%
  \Word{puce}{adj.}{紫红色的}
}

\SentenceBlock[0:08:31]{No. They were puce. I know because it makes me nauseous,}{不对，是紫红色。我知道，因为那颜色令我眩晕。}{%
  \Word{puce}{adj.}{紫红色的}
  \Word{nauseous}{adj.}{令人恶心的；感到恶心的}
}

\SentenceBlock[0:09:45]{Let's head to the kitchenette.}{我们去厨房吧。}{%
  \Word{kitchenette}{n.}{小厨房}
}

\SentenceBlock[0:13:38]{Ours were animatronic.}{我们的是机械人偶。}{%
  \Word{animatronic}{adj.}{仿真电子控制的}
}

\SentenceBlock[0:13:40]{They even did this little choreographed dance.}{它们甚至跳这种舞。}{%
  \Word{choreograph}{adj.}{编排好的；安排好的}
}

\SentenceBlock[0:13:45]{In my first perpetuity wing, the Eagans were brooms.}{在我的第一个永恒区，伊根们是扫帚做的。}{%
  \Word{broom}{n.}{扫帚}
}

\SentenceBlock[0:13:54]{Did you guys have the CPR dummies?}{你们有心肺复苏假人吗？}{%
  \Word{dummy}{n.}{假人；仿制品}
}

\SentenceBlock[0:14:30]{You know, my old team was a bunch of dirtbags.}{其实我之前的团队是一群混蛋。}{%
  \Word{dirtbag}{n.}{卑鄙小人（俚语）}
}

\SentenceBlock[0:15:43]{of the heinous conditions in the severed office,}{分离层办公室的环境险恶。}{%
  \Word{heinous}{adj.}{极其恶劣的；可憎的}
}

\SentenceBlock[0:15:48]{The branch is run by a shambolic rube who goes by Milkshake.}{这个分支的主管是一个没头脑的蠢人，他叫米奇。}{%
  \Word{shambolic}{adj.}{混乱的；杂乱无章的}
  \Word{rube}{n.}{乡巴佬；土包子}
}

\SentenceBlock[0:15:55]{A man whose stupidity is rivaled only by that of the nine core principles.}{能与其愚蠢程度相比的，只有九大核心原则。}{%
  \Word{stupidity}{n.}{愚蠢；愚笨}
}

\SentenceBlock[0:16:01]{If you must continue to send me here, please consider strapping a bomb to me,}{如果你必须继续让我来这里，请考虑给我绑上炸弹。}{%
  \Word{strap}{v.}{捆绑}
}

\SentenceBlock[0:16:11]{Wrathfully, your innie, Mark W.}{充满愤怒的你公司里的自己，马克W。}{%
  \Word{wrathfully}{adv.}{愤怒地；暴怒地}
}

\SentenceBlock[0:16:49]{You didn't even disguise your own handwriting.}{你甚至都没费心改变自己的笔迹。}{%
  \Word{disguise}{v.}{伪装；掩盖}
}

\SentenceBlock[0:17:24]{You will be relegated to the office,}{你将降职至办公室。}{%
  \Word{relegate}{v.}{降职；贬谪}
}

\SentenceBlock[0:19:14]{The Board does not converse with innies.}{董事会不会和公司里的记忆分离人交流。}{%
  \Word{converse}{v.}{交谈；谈话}
}

\SentenceBlock[0:21:13]{Kier pardons his betrayers?}{基尔宽恕背叛他的人？}{%
  \Word{pardon}{v.}{原谅；赦免}
}

\SentenceBlock[0:22:52]{Well, because I sort of sabotaged the new people.}{因为我对新来的人使坏。}{%
  \Word{sabotage}{v.}{蓄意破坏}
}


\SentenceBlock[0:26:32]{The name's a mouthful, or as I say, a "doorful."}{我的名字很拗口，或者应该说“很拗门”。}{%
  \Word{doorful}{n.}{（戏谑用法）难读或难说的词}
}

\SentenceBlock[0:27:05]{That tickles.}{好痒。}{%
  \Word{tickle}{v.}{发痒；使开心（笑）}
}

\SentenceBlock[0:27:21]{conspired to mount what Lumon historians will forever call,}{于是一起想出一个阴谋，卢蒙历史学家将称其为“宏观数起义”。}{%
  \Word{conspire}{v.}{密谋；共谋}
}

\SentenceBlock[0:27:25]{the Macrodat Uprising.}{这个问题因此也有了答案。}{%
  \Word{uprising}{n.}{起义；暴动}
}

\SentenceBlock[0:27:29]{Under my literal nose unfolded a human drama of danger and intrigue.}{就在我的鼻子下，上演了一出充满危险和阴谋的人类戏剧。}{%
  \Word{literal}{adj.}{字面上的；真实的}
  \Word{intrigue}{n.}{阴谋；诡计}
}

\SentenceBlock[0:27:36]{Righteous anger.}{正义的愤怒。}{%
  \Word{righteous}{adj.}{正义的；正直的}
}

\SentenceBlock[0:28:05]{The Macrodat Uprising yielded bounteous reforms.}{宏观数起义掀起了改革的新风。}{%
  \Word{uprising}{n.}{起义；暴动}
  \Word{bounteous}{adj.}{丰富的；慷慨的}
}

\SentenceBlock[0:28:15]{Christmas mints, and salsa.}{圣诞薄荷和莎莎酱。}{%
  \Word{salsa}{n.}{莎莎酱；一种拉丁美洲舞蹈或音乐}
}

\SentenceBlock[0:28:29]{and now range from hall passes to pineapple bobbing...}{现在加入了走廊通行证、咬菠萝游戏。}{%
  \Word{bob}{v.}{上下快速移动；参与咬浮物游戏}
}

\SentenceBlock[0:28:39]{to our brand-new playful mirror room.}{还有全新的哈哈镜屋。}{%
  \Word{playful}{adj.}{爱玩耍的；有趣的}
}

\SentenceBlock[0:28:46]{You know, it's funny. I've sat by this reflective pool my whole life,}{其实说来有趣，我一辈子都坐在这个倒影池旁。}{%
  \Word{reflective}{adj.}{反光的；沉思的}
}

\SentenceBlock[0:28:59]{They made quite a splash.}{他们“一石激起千层浪”。}{%
  \Word{splash}{n.}{引人注目的效果；水花飞溅}
}

\SentenceBlock[0:29:42]{And I don't wanna be your jailer.}{我不想成为你们的狱卒。}{%
  \Word{jailer}{n.}{狱卒；看守}
}

\SentenceBlock[0:30:03]{Maybe I'll even buy you a drink at a bistro one day.}{说不定有一天，我会在餐厅请你们喝一杯呢。}{%
  \Word{bistro}{n.}{小餐馆；小酒馆}
}

\SentenceBlock[0:30:19]{like so many sardines.}{而不是把它挤得像罐头沙丁鱼一样。}{%
  \Word{sardine}{n.}{沙丁鱼}
}

\SentenceBlock[0:32:46]{I was watching some nature show on TV, wearing sweatpants and a T-shirt.}{我在看某个电视节目，关于大自然的，我穿着运动裤和T恤衫。}{%
  \Word{sweatpants}{n.}{运动裤}
}

\SentenceBlock[0:32:56]{It was like a "save the gorillas" shirt.}{类似“救救大猩猩”的那种T恤。}{%
  \Word{gorilla}{n.}{大猩猩}
}

\SentenceBlock[0:36:51]{- Is that what it is? Mushy? Okay. - It's-- Yeah. Listen, Helly--}{- 是这样吗？复杂？好吧。 - 这...对。听我说，赫莉。}{%
  \Word{mushy}{adj.}{感情脆弱的；糊状的}
}

\SentenceBlock[0:39:16]{I was standing in front of some kind of easel.}{我站在某种画架前。}{%
  \Word{easel}{n.}{画架}
}

\SentenceBlock[0:39:54]{and I know because I encouraged the courtship.}{我知道，因为我鼓励你去追求他。}{%
  \Word{courtship}{n.}{求爱；追求}
}

\SentenceBlock[0:42:08]{- Well, I sympathize... - Mr. Milchick--}{- 我理解... - 米尔奇克先生。}{%
  \Word{sympathize}{v.}{同情；理解}
}

\SentenceBlock[0:43:30]{These are blueprints for a new renovation,}{这些是新装修工程的设计图。}{%
  \Word{renovation}{n.}{翻新；整修}
}

\SentenceBlock[0:43:58]{The holiest.}{可不是嘛。}{%
  \Word{holy}{adj.}{神圣的}
}

\SentenceBlock[0:44:07]{- Are you-- - ...only to avoid resentment.}{- 你是... - 只是为了避免嫉恨。}{%
  \Word{resentment}{n.}{怨恨；愤恨}
}



\end{document}