\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S02E05: Trojan's Horse}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:06:06]{We have decided to spare him knowledge of this contretemps.}{我们已决定不让他得知这次的挫折。}{%
  \Word{contretemps}{n.}{意外事故；尴尬事件}
}

\SentenceBlock[0:06:26]{Some residual trauma is to be expected after such an ordeal.}{经历了这样的折磨 一定是有一些遗留的创伤。}{%
  \Word{trauma}{n.}{创伤；心理创伤}
  \Word{ordeal}{n.}{严峻考验；磨难}
}

\SentenceBlock[0:06:32]{Perhaps we could arrange another obligement session this evening.}{也许我们今天傍晚可以再安排一个义务会。}{%
  \Word{obligement}{n.}{义务；责任（罕用词）}
}

\SentenceBlock[0:10:49]{Irving B's outie has departed on an elongated cruise voyage.}{欧文B外面的自己已踏上长期的邮轮之旅。}{%
  \Word{elongate}{adj.}{被拉长的；延长的}
}

\SentenceBlock[0:11:32]{In ancient times, the king of Sweden himself}{在远古时代 瑞典国王本人。}{%
  \Word{Sweden}{n.}{瑞典}
}

\SentenceBlock[0:11:34]{was known to go incognito amongst his people}{出了名地爱微服私访。}{%
  \Word{incognito}{adv.}{隐姓埋名地；微服私访地}
  \Word{among}{prep.}{在……之中}
}

\SentenceBlock[0:11:38]{in the hopes of learning their true grievances.}{希望借此了解百姓真实的忧虑。}{%
  \Word{grievance}{n.}{不满；怨愤}
}

\SentenceBlock[0:11:43]{He would don an old, gray robe, a Gråkappan,}{他会穿着老旧 灰色的 叫“格拉虚潘”的袍子。}{%
  \Word{don}{v.}{穿上；披上}
}

\SentenceBlock[0:11:51]{to disguise his royal vestments.}{用来伪装王室身份。}{%
  \Word{vestment}{n.}{法衣；礼服}
}

\SentenceBlock[0:11:56]{Kier Eagan himself was known to do so in his ether factories,}{基尔伊根在世时也会 伪装成百姓 去他的乙醚工厂。}{%
  \Word{ether}{n.}{乙醚；以太}
}

\SentenceBlock[0:12:10]{This smells like horseshit.}{感觉像是一派胡言。}{%
  \Word{horseshit}{n.}{胡说八道；废话}
}

\SentenceBlock[0:12:13]{Yeah. Swedish horseshit, and Irving is still dead.}{对 用瑞典语说的一派胡言 而且欧文就是死了。}{%
  \Word{horseshit}{n.}{胡说八道；废话}
}

\SentenceBlock[0:12:19]{As I said, Irving B's outie has departed on an elonga--}{正如我说 欧文外面的自己已踏上长期...。}{%
  \Word{elongate}{v.}{拉长；延长}
}

\SentenceBlock[0:13:10]{and help reacclimate you to your work environment.}{帮助你们重新熟悉工作环境。}{%
  \Word{reacclimate}{v.}{重新适应}
}

\SentenceBlock[0:13:31]{What in the abominable fuck?}{搞什么。}{%
  \Word{abominable}{adj.}{令人憎恶的；极坏的}
}

\SentenceBlock[0:14:28]{I'd hate to rescind certain privileges.}{我不希望撤销某些优待权利。}{%
  \Word{rescind}{v.}{废除；撤销}
}

\SentenceBlock[0:16:01]{Miss Huang, we need to ready a bereavement kit for MDR.}{黄小姐 我们需要为宏观数据精检 准备哀悼用具。}{%
  \Word{bereavement}{n.}{丧失；丧亲之痛}
}

\SentenceBlock[0:17:24]{It's not my fault that my outie hijacked me.}{我外面的自己 劫持了我的身体 这不是我的错。}{%
  \Word{hijack}{v.}{劫持}
}

\SentenceBlock[0:18:25]{It will help the others to grieve.}{这能帮助其他员工处理哀悼情绪。}{%
  \Word{grieve}{v.}{悲伤；哀悼}
}

\SentenceBlock[0:18:53]{Unsolicited.}{而且我没有征询你的意见。}{%
  \Word{unsolicited}{adj.}{未经请求的；擅自提供的}
}

\SentenceBlock[0:19:27]{You focus on the mournful signage.}{你专心印悼念标语就好。}{%
  \Word{mournful}{adj.}{悲哀的；忧伤的}
  \Word{signage}{n.}{标识；标志系统}
}

\SentenceBlock[0:19:52]{But given the sudden and frigid events which brought us here,}{但考虑到令我们聚集在这里的 突然而令人心寒的事件。}{%
  \Word{frigid}{adj.}{寒冷的；冷淡的}
}

\SentenceBlock[0:20:16]{We will now have a eulogy from Dylan G.}{接下来 迪伦G将为我们发表悼词。}{%
  \Word{eulogy}{n.}{悼词；颂词}
}

\SentenceBlock[0:20:36]{It's hard to pinpoint a favorite Irving story.}{要挑选我最爱的欧文回忆很难。}{%
  \Word{pinpoint}{v.}{精确定位；准确指出}
}

\SentenceBlock[0:20:50]{One time, he was pissed at me for watering down the toner,}{有一次 他气我给墨盒兑水。}{%
  \Word{piss}{v.}{使生气}
  \Word{toner}{n.}{墨粉；色粉}
}

\SentenceBlock[0:21:56]{You may now briefly partake in Irving's fruit head,}{你们可以尝一尝欧文的水果头。}{%
  \Word{partake}{v.}{参与；分享；品尝}
}

\SentenceBlock[0:22:29]{Yes, well, I feel the theremin works best in moderation.}{是 我感觉泰勒明音乐还是适度比较好。}{%
  \Word{theremin}{n.}{泰勒明（电子乐器）}
  \Word{moderation}{n.}{适度；节制}
}

\SentenceBlock[0:28:43]{depending on the number of atonements and approbations required.}{取决于所需的忏悔和认可数量。}{%
  \Word{atonement}{n.}{赎罪；补偿}
  \Word{approbation}{n.}{认可；赞许}
}

\SentenceBlock[0:29:16]{Your attendance and urinalysis are both in the excellent range.}{你的考勤和尿检得分都属于极佳范围。}{%
  \Word{urinalysis}{n.}{尿液分析；尿检}
}

\SentenceBlock[0:29:38]{Well, perchance I may colloquially employ a--}{也许我在口头语方面应该运用...。}{%
  \Word{perchance}{adv.}{或许；偶然}
  \Word{colloquially}{adv.}{口语地；通俗地}
}

\SentenceBlock[0:30:03]{But the bulk of our day will revolve around the following.}{但我们今天的主要内容是以下。}{%
  \Word{revolve}{v.}{围绕；旋转}
}

\SentenceBlock[0:30:12]{which failed to coalesce.}{但团队未能和谐共事。}{%
  \Word{coalesce}{v.}{联合；合并}
}

\SentenceBlock[0:30:23]{deterred curiosity or idling by the team once they returned.}{阻止团队回归后到处打探和游荡。}{%
  \Word{deter}{v.}{阻止；使打消念头}
  \Word{idle}{v.}{闲逛；无所事事}
}

\SentenceBlock[0:31:11]{It will take place under your stewardship.}{它将在你的监管下发生。}{%
  \Word{stewardship}{n.}{管理；监管}
}

\SentenceBlock[0:32:30]{I'm tightening the leash.}{我要加强监管了。}{%
  \Word{leash}{n.}{皮带；束缚}
}

\SentenceBlock[0:33:28]{The Bullshit Gazette?}{《谎话连篇公报》。}{%
  \Word{gazette}{n.}{公报；报纸}
}

\SentenceBlock[0:33:33]{Hopefully, now we can put all this grief and tumult behind us}{希望从现在起我们可以 放下这些哀悼和混乱。}{%
  \Word{tumult}{n.}{骚乱；混乱}
}

\SentenceBlock[0:34:51]{The workers were diligent,}{工人们兢兢业业。}{%
  \Word{diligent}{adj.}{勤奋的；用功的}
}

\SentenceBlock[0:35:06]{just hands and numbers and cogs and purpose.}{这里只有指针 数字 齿轮和使命。}{%
  \Word{cog}{n.}{齿轮；小职员（比喻）}
}

\SentenceBlock[0:35:10]{Your sovereign boss may own the clock that greets you from the wall,}{虽然墙上的时钟属于你最大的上司。}{%
  \Word{sovereign}{adj.}{至高无上的；独立的}
}

\SentenceBlock[0:35:56]{it might beget a revolution.}{那也许能掀起革命。}{%
  \Word{beget}{v.}{引起；产生}
}

\SentenceBlock[0:36:24]{this is a fiscal and creative opportunity}{这是一个经济和创意的机会。}{%
  \Word{fiscal}{adj.}{财政的；财务的}
}

\SentenceBlock[0:38:33]{Call it a quirk.}{算是个怪癖吧。}{%
  \Word{quirk}{n.}{怪癖；奇事}
}

\SentenceBlock[0:39:05]{they said my innie had an unsanctioned, erotic entanglement with another worker.}{他们说 我公司里的自己 和另一个员工有违规的情感关系。}{%
  \Word{unsanctioned}{adj.}{未经批准的；非法的}
  \Word{erotic}{adj.}{色情的；性爱的}
  \Word{entanglement}{n.}{纠葛；复杂关系}
}

\SentenceBlock[0:41:19]{Sorry there wasn't any eggnog.}{抱歉 没有蛋酒。}{%
  \Word{eggnog}{n.}{蛋酒}
}

\SentenceBlock[0:41:27]{I needed some pressure points. Things to rattle your memories.}{我需要一些压力点 用来激活你的记忆。}{%
  \Word{rattle}{v.}{使慌乱；激起}
}

\SentenceBlock[0:41:30]{Knitting?}{针织。}{%
  \Word{knit}{v.}{编织；针织}
}

\SentenceBlock[0:42:00]{They know people at the morgue.}{他们在停尸房有熟人。}{%
  \Word{morgue}{n.}{停尸房}
}

\SentenceBlock[0:42:02]{On the payroll, like everywhere else in Kier.}{是他们的员工 就像基尔一贯的作风。}{%
  \Word{payroll}{n.}{工资单；雇员名单}
}


\end{document}