\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S02E02: Goodbye, Mrs. Selvig}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:01:12]{- Okay. - ...need help with this diaper.}{- 好的 - ...帮我弄弄尿布。}{%
  \Word{diaper}{n.}{尿布}  
}

\SentenceBlock[0:02:15]{Fetid moppet.}{恶心的娃。}{%
  \Word{fetid}{adj.}{恶臭的}  
  \Word{moppet}{n.}{小孩（常用于昵称）}  
}

\SentenceBlock[0:02:33]{We'll have someone from the floor liaise with the outies.}{我们会派分离层的人员与员工外面的自己联络。}{%
  \Word{liaise}{v.}{联络；联系}  
}

\SentenceBlock[0:04:23]{We've commandeered the footage taken by guests.}{我们已没收宾客拍摄的视频。}{%
  \Word{commandeer}{v.}{强行征用；没收}  
}

\SentenceBlock[0:04:25]{Natalie is already doing outreach to media.}{娜塔莉已经开始与媒体沟通。}{%
  \Word{outreach}{n.}{外联活动；宣传推广}  
}

\SentenceBlock[0:05:56]{I welcome your contrition.}{我接受你的道歉。}{%
  \Word{contrition}{n.}{悔罪；懊悔}  
}

\SentenceBlock[0:06:10]{I recommend we start by scouring the feed,}{我建议从源头开始着手调查。}{%
  \Word{scour}{v.}{彻底搜索；仔细查找}  
}

\SentenceBlock[0:06:31]{Severance Advisory Council.}{分离顾问委员会。}{%
  \Word{advisory}{adj.}{顾问的；咨询的}  
}

\SentenceBlock[0:06:48]{It's a brand-new initiative. You'd be spearheading its formation.}{这是全新的安排，你将领头创建这一委员会。}{%
  \Word{initiative}{n.}{新措施；倡议}  
  \Word{spearhead}{v.}{领导；率先进行}  
}

\SentenceBlock[0:07:44]{And if we didn't hold you in such high esteem,}{正因为我们如此看重你。}{%
  \Word{esteem}{n.}{尊重；敬重}  
}

\SentenceBlock[0:09:04]{while on a non-Lumon medication for an arm rash.}{且此前因为手臂起红疹曾服用非卢蒙制的药物。}{%
  \Word{rash}{n.}{皮疹}  
}

\SentenceBlock[0:09:08]{This had an inebriating effect,}{这导致我陷入酩酊状态。}{%
  \Word{inebriate}{v.}{使醉；使陶醉}  
}

\SentenceBlock[0:09:52]{But in the hours since this outburst,}{但在鲁莽的发言之后。}{%
  \Word{outburst}{n.}{（情感）爆发；突发言论}  
}

\SentenceBlock[0:10:28]{When Lumon falters,}{卢蒙遇到问题时。}{%
  \Word{falter}{v.}{动摇；衰退}  
}

\SentenceBlock[0:10:29]{it's our cherished workers and their families who suffer first.}{总是我们最珍惜的员工和他们的家人首当其冲受伤害。}{%
  \Word{cherish}{v.}{珍视；珍爱}  
}

\SentenceBlock[0:10:34]{So for the fear and insecurity this has caused, I must sincerely atone.}{对于这所造成的恐惧和不安，我深切致歉。}{%
  \Word{atone}{v.}{赎罪；弥补}  
}

\SentenceBlock[0:10:39]{You were involved in a physical altercation,}{你在今天傍晚。}{%
  \Word{altercation}{n.}{争吵；争执}  
}

\SentenceBlock[0:10:45]{And I regret to say that you were the aggressor.}{很遗憾，你是施暴者。}{%
  \Word{aggressor}{n.}{侵略者；挑衅者}  
}

\SentenceBlock[0:10:54]{Distrust of Lumon has been sadly endemic since its founding.}{令人难过的是，对卢蒙的不信任自从公司初创以来就广泛存在。}{%
  \Word{distrust}{n.}{不信任；怀疑}  
  \Word{endemic}{adj.}{普遍存在的；地方性的}  
}

\SentenceBlock[0:10:58]{My words provided more fuel for a pernicious hate and derision.}{我的言论滋长了恶毒的仇恨和嘲笑。}{%
  \Word{pernicious}{adj.}{有害的；恶毒的}  
  \Word{derision}{n.}{嘲笑；嘲弄}  
}

\SentenceBlock[0:14:15]{So let's Occam's razor this shit.}{我们来将整件事剥丝抽茧吧。}{%
  \Word{razor}{n.}{剃刀；（比喻）简化原则（奥卡姆剃刀）}  
}

\SentenceBlock[0:14:41]{Perhaps "Cobelvig" would be a helpful nomenclature.}{我建议叫她“科贝尔维格”。}{%
  \Word{nomenclature}{n.}{命名法；术语系统}  
}

\SentenceBlock[0:15:12]{He found great meaning in it. Profundity.}{他在书中找到了巨大的意义，深刻。}{%
  \Word{profundity}{n.}{深刻；深奥}  
}

\SentenceBlock[0:16:34]{What happened tonight is what we call the "overtime contingency."}{今晚的事是我们所说的“紧急加班”。}{%
  \Word{contingency}{n.}{意外事件；应急情况}  
}

\SentenceBlock[0:16:39]{if we ever need to access your work personage off company grounds.}{用于处理需在公司外的地方联络到你工作人格的情况。}{%
  \Word{personage}{n.}{人物；身份（尤指重要人物）}  
}

\SentenceBlock[0:16:50]{It seems the tech was commandeered by one of your office mates,}{似乎你的一位同事操控了公司中的技术。}{%
  \Word{commandeer}{v.}{强行征用；夺取}  
}

\SentenceBlock[0:17:31]{for your managers to commit fucking lactation fraud,}{管理人员冒充母乳专家干涉员工家庭。}{%
  \Word{lactation}{n.}{哺乳；泌乳}  
}

\SentenceBlock[0:18:03]{Nor bedevil you out here any further.}{也不会再在公司外为你带来更多损害。}{%
  \Word{bedevil}{v.}{困扰；折磨}  
}

\SentenceBlock[0:19:11]{I'd hate to reward his courage with nonexistence.}{我不希望他的勇气换来的是被抹杀。}{%
  \Word{nonexistence}{n.}{不存在；虚无}  
}

\SentenceBlock[0:21:32]{That'd be a hoot.}{那就太有趣了。}{%
  \Word{hoot}{n.}{有趣的事；笑料}  
}

\SentenceBlock[0:25:35]{Just tuck yourself away.}{默默滑走。}{%
  \Word{tuck}{v.}{藏起；收起}  
}

\SentenceBlock[0:26:23]{It's fucking hubris.}{真够自大的。}{%
  \Word{hubris}{n.}{傲慢；狂妄自大}  
}

\SentenceBlock[0:27:04]{- What? - You want to circumcise your brain,}{- 什么 - 你想做大脑包皮切割术。}{%
  \Word{circumcise}{v.}{割礼；切除包皮}  
}

\SentenceBlock[0:27:07]{But it doesn't mean I have to hire you. And personally, I think it's abhorrent.}{但那不意味着我必须雇用你。我个人对分离厌恶至极。}{%
  \Word{abhorrent}{adj.}{令人厌恶的；可憎的}  
}

\SentenceBlock[0:27:50]{Hey, do we need more baby wipeys?}{嘿，家里还有没有宝宝湿巾？}{%
  \Word{wipey}{n.}{湿巾（非正式用法）}  
}

\SentenceBlock[0:29:51]{This is obscene.}{你的话太荒唐了。}{%
  \Word{obscene}{adj.}{淫秽的；荒唐的}  
}

\SentenceBlock[0:32:30]{Compliments of the company.}{公司的礼物。}{%
  \Word{compliment}{n.}{赠品（常作复数使用）；敬意}  
}

\SentenceBlock[0:33:17]{I ask because our endearment to you is such that a 20\% bump is on the table,}{这么问是因为如果你决定回公司。}{%
  \Word{endearment}{n.}{亲爱；钟爱}  
  \Word{bump}{n.}{增加；提升（如薪资）}  
}

\SentenceBlock[0:33:22]{should you return.}{我们愿考虑加薪20\%。}{%
}

\SentenceBlock[0:34:00]{you cited her death as a primary motivator for severing.}{你提到她的死是你选择分离的主要原因。}{%
  \Word{motivator}{n.}{动因；激励因素}  
}

\SentenceBlock[0:34:17]{That you felt like you were choking on her ghost.}{你觉得她的死让你一直如鲠在喉。}{%
  \Word{choke}{v.}{窒息；哽咽}  
}

\SentenceBlock[0:34:58]{The solace you have given him down there will make its way to you.}{你让他在地下寻找到慰藉，最终那也会反馈到你身上的。}{%
  \Word{solace}{n.}{安慰；慰藉}  
}

\SentenceBlock[0:36:17]{The sister seems more uppity than he is.}{他妹妹看起来比他傲慢。}{%
  \Word{uppity}{adj.}{傲慢的；自负的}  
}

\SentenceBlock[0:36:24]{I've got a floater from overseas and a pair who were laid off from 5X.}{我有一个从海外调来的灵活调配员工，还有两个被5X裁员的。}{%
  \Word{floater}{n.}{临时工；流动员工}  
}

\SentenceBlock[0:39:16]{This is unheard of.}{这种事闻所未闻。}{%
  \Word{unheard}{adj.}{从未听过的；前所未有的}  
}

\SentenceBlock[0:43:17]{You're so easy to sway.}{你真好哄。}{%
  \Word{sway}{v.}{影响；左右}  
}


\end{document}