\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S02E04: Woe's Hollow}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:04:38]{outdoor retreat and team-building occurrence.}{…户外团建活动}{%
  \Word{retreat}{n.}{静修；团建活动}%
}
\SentenceBlock[0:04:56]{thickets, brambles and brooks that make up the Dieter Eagan National Forest.}{欣赏这里的草地 灌丛 荆棘和溪流}{%
  \Word{thicket}{n.}{灌丛}%
  \Word{bramble}{n.}{荆棘}%
  \Word{brook}{n.}{小溪}%
}
\SentenceBlock[0:05:10]{Some of you may be quietly yearning to learn more.}{你们中的一些人可能正默默好奇 渴望了解更多}{%
  \Word{yearn}{v.}{渴望；向往}%
}
\SentenceBlock[0:05:23]{a text of such sanctity that it is forbidden upon the severed floor.}{由于内容过于神圣 其在分离层被禁止}{%
  \Word{sanctity}{n.}{神圣；尊严}%
}
\SentenceBlock[0:05:33]{the very same grotto,}{正是在那个洞窟中}{%
  \Word{grotto}{n.}{洞穴；岩洞}%
}
\SentenceBlock[0:05:34]{where Kier Eagan tamed the four tempers for the very first time.}{基尔伊根第一次驯服了四脾气}{%
  \Word{tame}{v.}{驯服；使顺从}%
}
\SentenceBlock[0:05:42]{“Stray not from Kier's path, lest you roil nature's wrath.”}{“务必追循基尔之道 反之即受自然之怒”}{%
  \Word{stray}{v.}{偏离；走失}%
  \Word{lest}{conj.}{以免；唯恐}%
  \Word{roil}{v.}{激怒；搅浑}%
  \Word{wrath}{n.}{愤怒；怒火}%
}
\SentenceBlock[0:06:50]{Not even televisually.}{就算是电视版本的也不信}{%
  \Word{televisual}{adj.}{电视的；通过电视的}%
}
\SentenceBlock[0:10:39]{The lodgings of my mother's womb I shared with another,}{我与另一个人曾同处于母亲的腹中}{%
  \Word{lodging}{n.}{住所；寄宿处}%
  \Word{womb}{n.}{子宫}%
}
\SentenceBlock[0:10:55]{“In infancy, he was my bosom friend. But as we blossomed into boyhood,}{“在婴孩时期 他是我的密友 但随着我们成长为少年，}{%
  \Word{infancy}{n.}{婴儿期}%
  \Word{bosom}{adj.}{亲密的；亲爱的}%
  \Word{boyhood}{n.}{童年；少年时期}%
}
\SentenceBlock[0:11:00]{he beseeched me to take to the wood with him to live as paupers.}{他恳求我和他一起到树林中 过贫民的日子}{%
  \Word{beseech}{v.}{恳求；请求}%
  \Word{pauper}{n.}{贫民；穷人}%
}
\SentenceBlock[0:11:08]{I acceded, and we ventured into the wood towards...}{我应允了 于是我们进入树林 向着…}{%
  \Word{accede}{v.}{同意；应允}%
}
\SentenceBlock[0:11:33]{“He always crept like this at this hour.}{“在这个时间 他总是这样蹑手蹑脚}{%
  \Word{creep}{v.}{蹑手蹑脚地走；缓慢移动}%
}
\SentenceBlock[0:11:37]{- Once concealed by flora, my brother... - ...flora, my brother}{- 在花草的掩护下 我的兄弟… - …掩护下 我的兄弟}{%
  \Word{conceal}{v.}{隐藏；掩盖}%
  \Word{flora}{n.}{植物群；植物区系}%
}
\SentenceBlock[0:11:41]{unfastened himself.}{解放了自我}{%
  \Word{unfasten}{v.}{解开；松开}%
}
\SentenceBlock[0:11:43]{The din of his fervor fell strangely into concert with the music of the wood.}{他的狂热莫名与树林的音乐产生了共鸣}{%
  \Word{din}{n.}{喧嚣；嘈杂声}%
  \Word{fervor}{n.}{热情；狂热}%
}
\SentenceBlock[0:11:51]{His every thrust found rhythm,}{他的每一次猛推…}{%
  \Word{thrust}{n.}{猛推；猛刺}%
}
\SentenceBlock[0:11:54]{- with the trill of the crickets... - ...“trill of the crickets”...}{- 与蟋蟀的颤鸣… - “颤鸣”…}{%
  \Word{trill}{n.}{颤音；颤鸣}%
  \Word{cricket}{n.}{蟋蟀}%
}
\SentenceBlock[0:11:57]{- ...and the moaning of the wind... - ...“and the moaning of the wind”…}{- 和风的低吟… - “和风的低吟”…}{%
  \Word{moan}{n.}{呻吟；呜咽声}%
}
\SentenceBlock[0:12:00]{- ...and the snowfall's yearly thaw. - ...“and the snowfall's yearly thaw.”}{- 和瑞雪融化的节拍同步 - “和瑞雪融化的节拍同步”}{%
  \Word{thaw}{n.}{融化；解冻}%
}
\SentenceBlock[0:12:09]{- ...and nature played Dieter... - “and nature played Dieter with elegance.}{- 而大自然… - “而大自然优雅地演奏着迪特，}{%
  \Word{elegance}{n.}{优雅；高雅}%
}
\SentenceBlock[0:12:16]{as he spilt his lineage upon the soil.”}{他将自己的血脉洒在土壤上”}{%
  \Word{lineage}{n.}{血统；家系}%
}

\SentenceBlock[0:17:52]{I thought the waterfall's grandeur would satiate you.}{我以为瀑布的壮阔美景 已经能让你们感到充实了}{%
  \Word{grandeur}{n.}{宏伟；壮丽}%
  \Word{satiate}{v.}{使满足；使厌腻}%
}
\SentenceBlock[0:19:06]{Miss Huang has been readying the grill for which we brought in copious luxury meats.}{黄小姐已经在准备烧烤架 我们送来了丰富的高级肉类}{%
  \Word{grill}{n.}{烧烤架}%
  \Word{copious}{adj.}{大量的；丰富的}%
}
\SentenceBlock[0:19:14]{The fire will be used for marshmallows and a recital later.}{篝火将用于稍后的烤棉花糖和诵诗会}{%
  \Word{recital}{n.}{朗诵；独奏会}%
}
\SentenceBlock[0:20:38]{I suppose it sounded alarmist and paranoid.}{感觉是在制造恐慌和被害妄想}{%
  \Word{alarmist}{adj.}{危言耸听的}%
  \Word{paranoid}{adj.}{多疑的；偏执的}%
}
\SentenceBlock[0:20:43]{Irrational.}{不理智}{%
  \Word{irrational}{adj.}{不理性的；无理性的}%
}
\SentenceBlock[0:22:06]{“Dieter lay unwashed in his bedroll,}{“迪特没有清洗身体 躺在床铺上，}{%
  \Word{bedroll}{n.}{睡袋；铺盖卷}%
}
\SentenceBlock[0:22:09]{though the hollow's pool was primed for bathing.}{虽然悲哀谷的池子是理想的盥洗地点}{%
  \Word{prime}{v.}{使准备好}%
}
\SentenceBlock[0:22:13]{We ate of the hare we'd caught,}{我们吃了之前捕猎到的野兔}{%
  \Word{hare}{n.}{野兔}%
}
\SentenceBlock[0:22:15]{and told each other rhyming jokes till our gullets ached.}{并说着押韵的玩笑话 直到喉咙沙哑}{%
  \Word{rhyme}{v.}{押韵}%
  \Word{gullet}{n.}{喉咙；食道}%
  \Word{ache}{v.}{疼痛；发酸}%
}
\SentenceBlock[0:22:20]{But at last, the thought tickling my mouth emerged.}{但最终我还是说出了一直在嘴边的话}{%
  \Word{tickle}{v.}{使发痒；使高兴}%
}
\SentenceBlock[0:22:30]{'But I promise to look after you in the ether mill.'}{‘但我保证会在乙醚厂保护你’}{%
  \Word{ether}{n.}{乙醚；以太}%
}
\SentenceBlock[0:22:34]{When at last a sound came from him, it was a bewailing whimper.}{他嘴里最后发出的声音是一声低低的哀嚎}{%
  \Word{bewail}{v.}{哀悼；悲叹}%
  \Word{whimper}{n.}{呜咽；啜泣}%
}
\SentenceBlock[0:22:39]{He believed, I suppose, that we'd be woodland paupers forever.}{我想 他以为我们会永远在野外流浪}{%
  \Word{woodland}{n.}{林地；森林地带}%
  \Word{pauper}{n.}{贫民；穷人}%
}
\SentenceBlock[0:22:54]{driven by a sudden torrent of pus from his skull.}{是被他头颅中突然涌出的脓水推出来的}{%
  \Word{torrent}{n.}{洪流；急流}%
  \Word{pus}{n.}{脓}%
}
\SentenceBlock[0:23:04]{which was suddenly moss that tore easily from his bleeding scalp.”}{头发蓦然变成了青苔 轻易地从淌血的头皮上被扯下来”}{%
  \Word{moss}{n.}{苔藓}%
  \Word{scalp}{n.}{头皮}%
}
\SentenceBlock[0:23:11]{“And as the pus from his eye thickened into sap,}{“他眼窝中的脓水慢慢凝固，}{%
  \Word{thicken}{v.}{变浓；凝结}%
  \Word{sap}{n.}{树液；汁液}%
}
\SentenceBlock[0:23:15]{I turned from my gargling brother and walked to the pool of the hollow,}{我离开喉咙中汩汩作响的兄弟 走向悲哀谷的池子}{%
  \Word{gargle}{v.}{漱口；喉中作响}%
}
\SentenceBlock[0:23:36]{a gaunt bride, half the height of a natural woman.}{她是一个憔悴的新娘 身高是普通女人的一半}{%
  \Word{gaunt}{adj.}{憔悴的；枯瘦的}%
}
\SentenceBlock[0:24:08]{You suffered his wantonness.}{你纵容他的放荡任为}{%
  \Word{wantonness}{n.}{放荡；荒淫}%
}
\SentenceBlock[0:24:15]{Only chaos's whore.'”}{他只是混乱身边的妓女’”}{%
  \Word{whore}{n.}{妓女}%
}
\SentenceBlock[0:24:44]{Creepy.}{好惊悚}{%
  \Word{creepy}{adj.}{令人毛骨悚然的；怪异的}%
}
\SentenceBlock[0:25:23]{He turned into the forest because he masturbated.}{他变成了森林的一部分 就因为他手淫}{%
  \Word{masturbate}{v.}{手淫}%
}
\SentenceBlock[0:28:14]{- A luminescent vest? Tell us... - Okay.}{- 夜光背心 告诉我们... - 好}{%
  \Word{luminescent}{adj.}{发光的；夜光的}%
}
\SentenceBlock[0:28:25]{while your outie's wife rots away somewhere.}{而你外面自己的老婆 此刻正在某个地方腐烂}{%
  \Word{rot}{v.}{腐烂；腐败}%
}
\SentenceBlock[0:44:53]{She's a fucking mole!}{她是个间谍！}{%
  \Word{mole}{n.}{间谍；内奸}%
}
\SentenceBlock[0:46:26]{You have threatened collegial murder in the pond of Woe's Hollow.}{你在悲哀谷的池子里威胁要杀害同事}{%
  \Word{collegial}{adj.}{同事间的；同僚的}%
}
\SentenceBlock[0:46:35]{There shall be no formal valediction, catered or otherwise.}{将不会安排有餐饮或无餐饮的 正式离职送别会}{%
  \Word{valediction}{n.}{告别；告别辞}%
}
\SentenceBlock[0:46:40]{Your outie will be notified forthwith.}{你外面的自己将立即接获通知}{%
  \Word{forthwith}{adv.}{立刻；马上}%
}
\SentenceBlock[0:47:03]{Please refrain from any further speech,}{请不要继续发表任何言论}{%
  \Word{refrain}{v.}{克制；避免}%
}
\SentenceBlock[0:47:05]{as you are no longer authorized to consort with any severed employee,}{因为你已失去与任何分离层员工 交流的权限}{%
  \Word{consort}{v.}{结交；交往}%
}


\end{document}