\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S02E06: Attila}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip
\SentenceBlock[0:00:31]{I mean, why is she rattling off a bunch of facts?}{她为什么连续说一串事实}{%
  \Word{rattle}{v.}{快速说出}
}

\SentenceBlock[0:05:48]{you cannot graduate from this fellowship}{你从这个奖学金项目毕业的前提}{%
  \Word{fellowship}{n.}{奖学金项目}
}

\SentenceBlock[0:06:03]{and eradicating from your essence childish folly.}{根除你幼稚无知的本质}{%
  \Word{eradicate}{v.}{根除}
  \Word{essence}{n.}{本质}
  \Word{childish}{adj.}{幼稚的}
  \Word{folly}{n.}{愚蠢}
}

\SentenceBlock[0:06:18]{I trust you can steward the floor in my stead?}{我相信你会代我管理好分离楼层}{%
  \Word{stead}{n.}{代替}
}

\SentenceBlock[0:06:52]{They're trying to intimidate us.}{他们想恐吓我们}{%
  \Word{intimidate}{v.}{恐吓}
}

\SentenceBlock[0:08:29]{Something to drive a wedge between us.}{用来离间我们的感情}{%
  \Word{wedge}{n.}{楔子；分裂的导火索}
}

\SentenceBlock[0:10:09]{Though you did take scuba lessons last year.}{不过你去年的确上过水肺潜水课}{%
  \Word{scuba}{n.}{水肺潜水}
}

\SentenceBlock[0:10:34]{Maybe I'm trying to find something I excel in up there, like I do down here.}{也许我是想在地上的世界找到自己杰出的领域，像地下的自己一样}{%
  \Word{excel}{v.}{擅长}
}

\SentenceBlock[0:21:50]{Do you have a deviated septum?}{你有鼻中隔偏曲吗}{%
  \Word{deviate}{v.}{偏离}
  \Word{septum}{n.}{隔膜；中隔}
}

\SentenceBlock[0:21:55]{Would you like me to put petroleum jelly in your nostrils?}{需要我给你的鼻孔里抹凡士林吗}{%
  \Word{petroleum}{n.}{石油}
  \Word{nostril}{n.}{鼻孔}
}

\SentenceBlock[0:22:02]{Any auras or hallucinations?}{有先兆头痛或幻觉吗}{%
  \Word{aura}{n.}{预兆；先兆}
}

\SentenceBlock[0:23:12]{That was another crossover memory.}{又是一个交叉记忆}{%
  \Word{crossover}{n.}{交叉；融合}
}

\SentenceBlock[0:23:31]{There's a slight chance of hemorrhage.}{有小概率会出血}{%
  \Word{hemorrhage}{n.}{出血}
}

\SentenceBlock[0:25:13]{I hope you like a cumin glaze.}{希望你喜欢孜然汁}{%
  \Word{glaze}{n.}{釉料；光亮涂层}
}

\SentenceBlock[0:25:40]{What your innie ever saw in this Philistine is beyond me.}{我真搞不懂你公司里的自己看上这大老粗的哪一点}{%
  \Word{Philistine}{n.}{庸俗之人；外行}
}

\SentenceBlock[0:26:01]{I'm sure that felt quite invasive.}{你们一定感觉隐私被侵犯了}{%
  \Word{invasive}{adj.}{侵入性的；侵犯的}
}

\SentenceBlock[0:27:02]{And I should mention that I'd been what you might call a scoundrel in my younger days.}{另外提一下 在我年轻时 我可以说是一个人渣}{%
  \Word{scoundrel}{n.}{无赖；恶棍}
}

\SentenceBlock[0:27:27]{To which I replied, "What am I supposed to do up there for eternity all by myself?"}{对此我的回应是“那我自己在上面 待到永恒 怎么消磨时光 ”}{%
  \Word{eternity}{n.}{永恒}
}

\SentenceBlock[0:27:33]{- I see. - So we hop on the train to church,}{- 了解 - 所以我们搭火车去教堂}{%
  \Word{hop}{v.}{跳上；快速搭乘}
}

\SentenceBlock[0:27:36]{and it so happens the sermon that day is about severance...}{那天的布道主题恰恰是分离...}{%
  \Word{sermon}{n.}{布道；讲道}
}

\SentenceBlock[0:27:48]{he said the church's stance is that innies are, you know,}{他说教会的立场是 公司里的自己是}{%
  \Word{stance}{n.}{立场；态度}
}

\SentenceBlock[0:28:16]{We're not zealots, I swear.}{我发誓 我们不是宗教狂热分子}{%
  \Word{zealot}{n.}{狂热分子}
}

\SentenceBlock[0:34:30]{Traumatic, even.}{甚至是创伤性的}{%
  \Word{traumatic}{adj.}{创伤性的}
}

\SentenceBlock[0:37:42]{Quite startled him.}{吓了他一跳}{%
  \Word{startle}{v.}{使吃惊}
}

\SentenceBlock[0:38:21]{Can we not just be pragmatic adults about this?}{我们不能成熟点 就事论事吗}{%
  \Word{pragmatic}{adj.}{务实的}
}

\SentenceBlock[0:38:42]{Are you done humiliating our guest?}{你还要继续羞辱我们的客人吗}{%
  \Word{humiliate}{v.}{羞辱}
}

\SentenceBlock[0:43:56]{Well, you can't not pick up when we're doing corporate espionage shit.}{我们在进行企业间谍行动期间 你别不接电话啊}{%
  \Word{espionage}{n.}{间谍活动}
}

\SentenceBlock[0:43:59]{The floodlight thing was a bust, right?}{泛光灯那招完全失败了 对吗}{%
  \Word{floodlight}{n.}{泛光灯}
  \Word{bust}{n.}{失败}
}

\end{document}