\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S02E08: Sweet Vitriol}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip

\SentenceBlock[0:04:23]{You hear about that clusterfuck up on North Pine?}{你听说北松那件破事了吗}{
    \Word{clusterfuck}{n.}{一团糟}
}
\SentenceBlock[0:04:28]{How the fuck do you flip a two-ton snow plow?}{到底是怎么把2吨重的铲雪机弄翻的}{
    \Word{plow}{n.}{铲雪机}
}
\SentenceBlock[0:04:33]{The apple don't fall far from the gutter.}{有其父必有其子}{
    \Word{gutter}{n.}{贫民窟}
}
\SentenceBlock[0:04:57]{Très chic.}{非常时髦}{
    \Word{chic}{adj.}{时髦的}
}
\SentenceBlock[0:06:09]{Well, flip my toboggan.}{我的老天}{
    \Word{toboggan}{n.}{雪橇}
}
\SentenceBlock[0:06:51]{Frailer.}{更破败}{
    \Word{frail}{adj.}{虚弱的}
}
\SentenceBlock[0:06:58]{and the fluctuating interest rates,}{利率波动}{
    \Word{fluctuate}{v.}{波动}
}
\SentenceBlock[0:07:00]{there was a retrenchment from some of the core infrastructure investments.}{一些核心的基建投资被缩减了}{
    \Word{retrenchment}{n.}{削减}
}
\SentenceBlock[0:10:49]{Then you know she's a fucking pariah here.}{那你就知道她是这里的边缘人}{
    \Word{pariah}{n.}{被社会遗弃者}
}
\SentenceBlock[0:11:13]{We were once chums.}{我们曾经是密友}{
    \Word{chum}{n.}{密友}
}
\SentenceBlock[0:11:53]{Pathetic.}{真可悲}{
    \Word{pathetic}{adj.}{可悲的}
}
\SentenceBlock[0:12:00]{But I'll not be the punching dummy for your resentments.}{但我不会当你仇恨的出气筒}{
    \Word{resentment}{n.}{怨恨}
}
\SentenceBlock[0:13:56]{You're higher than a bearded vulture.}{你嗑药嗑得已经云里雾里了}{
    \Word{bearded}{adj.}{长胡子的}
    \Word{vulture}{n.}{秃鹫}
}
\SentenceBlock[0:14:24]{This is trespass.}{你这是私闯民宅}{
    \Word{trespass}{n.}{非法侵入}
}
\SentenceBlock[0:14:31]{I do not want that huff peddler on my property.}{我不要那个吸白粉的进入我的地盘}{
    \Word{huff}{v.}{吸毒}
    \Word{peddler}{n.}{毒贩}
}
\SentenceBlock[0:14:35]{You gave him his thirst for it.}{他上瘾都是因为你}{
    \Word{thirst}{n.}{渴望}
}
\SentenceBlock[0:16:22]{I will not have this quarrel.}{我不跟你吵}{
    \Word{quarrel}{n.}{争吵}
}
\SentenceBlock[0:16:41]{She said nothing after you pulled the tube from her gullet.}{你拔掉管子后 她什么都没说}{
    \Word{gullet}{n.}{食道}
}
\SentenceBlock[0:17:14]{Perhaps she would have found solace in the nine.}{也许她就会在九项原则中找到慰藉}{
    \Word{solace}{n.}{安慰}
}
\SentenceBlock[0:17:33]{You didn't have to listen to her wheezing as I did, day after day.}{你不用像我一样日复一日听着她的喘息}{
    \Word{wheeze}{v.}{喘息}
}
\SentenceBlock[0:18:14]{Even at the factory, no apprentice was more industrious than you.}{就算是在工厂时 你也是最勤恳努力的见习生}{
    \Word{apprentice}{n.}{学徒}
    \Word{industrious}{adj.}{勤奋的}
}
\SentenceBlock[0:18:39]{Return and plead forgiveness, child.}{回去乞求原谅吧 孩子}{
    \Word{forgiveness}{n.}{宽恕}
}
\SentenceBlock[0:24:07]{Get your harpy hands off me.}{把你的脏手拿开}{
    \Word{harpy}{n.}{凶残的女人}
}
\SentenceBlock[0:24:09]{You've no salutation here, you blighted snuff slave.}{这里不欢迎你 低贱的毒品奴}{
    \Word{salutation}{n.}{问候}
    \Word{blighted}{adj.}{枯萎的；毁灭的}
    \Word{snuff}{n.}{鼻烟；毒品}
}
\SentenceBlock[0:24:13]{All right, I missed you too. You smell like crow skin.}{好吧 我也很想你 你身上一股腐朽味}{
    \Word{crow}{n.}{乌鸦}
}
\SentenceBlock[0:24:16]{Yeah, call everyone. We'll have a fucking kegger.}{是 把大家都叫来 我们可以开场派对}{
    \Word{kegger}{n.}{啤酒派对}
}
\SentenceBlock[0:27:41]{You ready to man the vat for ten hours?}{你准备好看守大罐十小时吗}{
    \Word{vat}{n.}{大桶}
}
\SentenceBlock[0:31:31]{I would never bear falsity to a steward of the Eagans.}{我绝不会对伊根家族的管家说假话}{
    \Word{falsity}{n.}{虚假}
}
\SentenceBlock[0:31:52]{Everything that you have, you owe back to the Eagans as fealty.}{你所拥有的一切 都是伊根家族的恩赐 你必须以效忠回报}{
    \Word{fealty}{n.}{忠诚}
}
\SentenceBlock[0:32:22]{Jame Eagan was the inventor.}{杰姆伊根是发明者}{
    \Word{inventor}{n.}{发明者}
}
\SentenceBlock[0:33:00]{That if I sought credit, I would be banished.}{如果我要求将功劳归于自己 就会被放逐}{
    \Word{banish}{v.}{放逐}
}
\SentenceBlock[0:33:32]{Your mother was a coward.}{你母亲是个胆小鬼}{
    \Word{coward}{n.}{懦夫}
}
\SentenceBlock[0:33:39]{Filled with malice and resentment.}{充满恶意和仇恨}{
    \Word{malice}{n.}{恶意}
    \Word{resentment}{n.}{怨恨}
}


\end{document}