\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S02E09: The After Hours}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip
\SentenceBlock[0:01:20]{A momentous day.}{真是具有里程碑意义的一天}{
    \Word{momentous}{adj.}{重大的}
}
\SentenceBlock[0:06:02]{I have chosen your ring toss game as a proper totem.}{我选择了你的掷环游戏机作为合适的象征}{
    \Word{totem}{n.}{象征}
}
\SentenceBlock[0:08:07]{You've been adrift.}{你的心一直不定}{
    \Word{adrift}{adj.}{漂泊的}
}
\SentenceBlock[0:08:20]{I'm gonna go to work and earn a paycheck to feed our children.}{我去上班了 要赚钱养我们的孩子}{
    \Word{paycheck}{n.}{薪水}
}
\SentenceBlock[0:09:33]{to several recent disappearances or deaths.}{近期几起失踪或死亡案相关}{
    \Word{disappearance}{n.}{失踪}
}
\SentenceBlock[0:09:44]{as a low-level Lumon enforcer or goon.}{卢蒙低层的打手或小喽啰参与其中}{
    \Word{enforcer}{n.}{执行者}
    \Word{goon}{n.}{暴徒}
}
\SentenceBlock[0:09:52]{Lumon goon. That stings.}{“卢蒙的小喽啰” 真伤人}{
    \Word{sting}{v.}{刺痛（情感上）}
}
\SentenceBlock[0:12:28]{Tragically, you're you.}{很可惜 你是你自己}{
    \Word{tragically}{adv.}{悲惨地}
}
\SentenceBlock[0:12:43]{I'm sorry. The wind was whistling.}{抱歉 风穿过}{
    \Word{whistle}{v.}{呼啸}
}
\SentenceBlock[0:14:20]{Nondisclosure policy forbids.}{保密政策禁止透漏}{
    \Word{nondisclosure}{n.}{保密}
}
\SentenceBlock[0:15:01]{You are my subordinate and this behavior constitutes insubordination.}{你是我的下属 你的此举属于不服从上级命令}{
    \Word{subordinate}{n.}{下属}
    \Word{insubordination}{n.}{不服从}
}
\SentenceBlock[0:21:14]{Even under the cover of dark, it's perilous.}{就算有天黑作掩护 也很危险}{
    \Word{perilous}{adj.}{危险的}
}
\SentenceBlock[0:22:42]{If he smells chicanery, he'll lock you out of the building.}{如果他起了疑心 他会把你锁在楼外}{
    \Word{chicanery}{n.}{欺骗}
}
\SentenceBlock[0:25:55]{I'm sure you know this is very disappointing and reeks of ingratitude.}{你一定清楚这非常令人失望 且表现出你的毫不感恩}{
    \Word{reek}{v.}{充满（令人不快的气息）}
    \Word{ingratitude}{n.}{忘恩负义}
}
\SentenceBlock[0:27:00]{So this is ``tightening the leash''?}{这就是你所谓的“加强监管”}{
    \Word{leash}{n.}{束缚}
}
\SentenceBlock[0:27:25]{but I thank you for your remonstration.}{但多谢您对我的谆谆鞭笞}{
    \Word{remonstration}{n.}{抗议；规劝}
}
\SentenceBlock[0:27:30]{A needlessly complex word for a simple idea.}{一个简单的概念非要用这么复杂的词}{
    \Word{needlessly}{adv.}{不必要地}
}
\SentenceBlock[0:28:18]{Devour feculence.}{噬粪}{
    \Word{feculence}{n.}{污秽}
}
\SentenceBlock[0:28:56]{To put that monosyllabically,}{言简意赅地说}{
    \Word{monosyllabically}{adv.}{用单音节词地；简洁地}
}
\SentenceBlock[0:41:20]{Specialties Department.}{特别事务部}{
    \Word{specialty}{n.}{专长；特别项目}
}
\SentenceBlock[0:41:24]{I'm looking for a gold thimble.}{我在找金针}{
    \Word{thimble}{n.}{顶针}
}

\end{document}