\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S02E03: Who Is Alive?}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip
\SentenceBlock[0:04:48]{Yeah. I'm in a good groove here, but don't worry about it. I'll get to it.}{是 我工作状态正佳 但别担心 我会去办的}{%
  \Word{groove}{n.}{最佳状态；工作节奏}%
}

\SentenceBlock[0:05:21]{Well, be discreet.}{我们会低调点的}{%
  \Word{discreet}{adj.}{谨慎的；低调的}%
}

\SentenceBlock[0:08:33]{Or maybe you go yourself, like, for stealth, you know?}{或者你可以自己找  这样更容易隐藏踪迹 对吧}{%
  \Word{stealth}{n.}{秘密行动；隐匿}%
}

\SentenceBlock[0:09:48]{Hello. I want to thank the Board humbly for my recent betterment.}{你好 我想先为最近的晋升 向董事会致以谢意}{%
  \Word{humble}{adv.}{谦逊地}%
  \Word{betterment}{n.}{改善；进步；晋升}%
}

\SentenceBlock[0:10:03]{The Board is jubilant at your ascendance.}{董事会对于你的升职感到喜悦}{%
  \Word{jubilant}{adj.}{欣喜的；欢腾的}%
  \Word{ascendance}{n.}{上升；支配地位}%
}

\SentenceBlock[0:10:17]{The Board austerely desires for you to feel connected to Lumon's history.}{董事会非常郑重地表达 其希望你感到卢蒙的历史与你息息相关}{%
  \Word{austere}{adv.}{严肃地；庄重地}%
}

\SentenceBlock[0:10:26]{please accept from the Board these inclusively re-canonicalized paintings}{请接受董事会赠予你的 这些经重新规范化的画作}{%
  \Word{inclusive}{adv.}{全面地；包容地}%
  \Word{canonicalize}{v.}{使规范化；使标准化}%
}

\SentenceBlock[0:16:34]{Mammalians Nurturable.}{哺乳动物培育部}{%
  \Word{mammalian}{n.}{哺乳动物}%
  \Word{nurturable}{adj.}{可培养的；可养育的}%
}

\SentenceBlock[0:18:48]{we don't abide such fripperies here.}{本部不允许这种无用小事的存在}{%
  \Word{abide}{v.}{容忍；接受}%
  \Word{frippery}{n.}{无用的小玩意；华而不实的装饰}%
}

\SentenceBlock[0:20:21]{I don't mean to impugn. It's just like, are you okay, you know?}{我无意冒犯 但就想确定 你是安全的吧}{%
  \Word{impugn}{v.}{质疑；指责}%
}

\SentenceBlock[0:23:13]{Please refrain from sharing information that may be privileged or sensitive.}{请避免分享可能机密或敏感的信息}{%
  \Word{refrain}{v.}{克制；避免}%
}

\SentenceBlock[0:25:34]{And we live on a cattle ranch?}{我们住在牧场}{%
  \Word{ranch}{n.}{牧场}%
}

\SentenceBlock[0:25:57]{I ca... My God, he was fearless.}{我真...天啊 他天不怕地不怕}{%
  \Word{fearless}{adj.}{无畏的；大胆的}%
}

\SentenceBlock[0:29:03]{She used to come do her sessions in our husbandry tanks.}{她以前会来我们的饲养箱里 进行她的治疗谈话}{%
  \Word{husbandry}{n.}{畜牧业；饲养}%
}

\SentenceBlock[0:29:15]{She said my outie excels at stargazing.}{她说我外面的自己拥有高超的观星技术}{%
  \Word{excel}{v.}{擅长；胜过}%
  \Word{stargazing}{n.}{观星；幻想}%
}

\SentenceBlock[0:29:35]{But if you suspect otherwise, we won't hinder your search.}{但如果你怀疑另有隐情 我们不会阻碍你们的调查}{%
  \Word{hinder}{v.}{阻碍；妨碍}%
}

\SentenceBlock[0:30:29]{See? Pouchless.}{瞧 没有囊袋}{%
  \Word{pouchless}{adj.}{无袋的；没有囊袋的}%
}

\SentenceBlock[0:33:29]{But surely beer and juleps cannot fill the void left by love.}{但啤酒和薄荷茱莉普 显然无法填补爱留下的空洞}{%
  \Word{julep}{n.}{薄荷酒（尤指薄荷茱莉普鸡尾酒）}%
}

\SentenceBlock[0:33:39]{which is why sadness is among the most recurrent issues facing the poor.}{因此悲伤是穷人最常见的问题之一}{%
  \Word{recurrent}{adj.}{反复发生的；周期性的}%
}

\SentenceBlock[0:33:44]{Remarkable. So astute.}{写得真好 观察敏锐}{%
  \Word{astute}{adj.}{敏锐的；精明的}%
}

\SentenceBlock[0:35:05]{There's a certain verbiage to which innies respond more favorably.}{公司里的自己更偏好某一种措辞方式}{%
  \Word{verbiage}{n.}{措辞；冗词}%
  \Word{favorably}{adv.}{赞同地；顺利地}%
}

\SentenceBlock[0:35:09]{If we just tweak it here and there.}{所以能调整一下用词会更好}{%
  \Word{tweak}{v.}{略作调整；微调}%
}

\SentenceBlock[0:36:35]{As well as your kindergarten teacher.}{你的幼儿园老师也是}{%
  \Word{kindergarten}{n.}{幼儿园}%
}

\SentenceBlock[0:36:42]{Yeah. Fuck, I gotta skedaddle.}{好的 该死 我得走了}{%
  \Word{skedaddle}{v.}{赶紧离开；溜走}%
}

\SentenceBlock[0:41:11]{hubris...}{狂妄}{%
  \Word{hubris}{n.}{傲慢自大；狂妄}%
}

\SentenceBlock[0:41:14]{arrogance.}{傲慢}{%
  \Word{arrogance}{n.}{傲慢；自负}%
}

\SentenceBlock[0:44:54]{Are you trying to burn a message to your innie into your retinas}{你是想将讯息刻在视网膜上 给公司里的自己传信吗}{%
  \Word{retina}{n.}{视网膜}%
}

\SentenceBlock[0:45:17]{- No shit. - The switch briefly dilates the pupils.}{- 也不奇怪 - 那个开关只会短暂散瞳}{%
  \Word{dilate}{v.}{使扩张；使扩大}%
}

\SentenceBlock[0:45:20]{Clean slate.}{只是重启}{%
  \Word{slate}{n.}{初始状态；清白记录}%
}

\SentenceBlock[0:47:55]{I can sew together a version of you that loves her with a version of you that can--}{我可以将那个爱她的版本 与另一个版本的你缝合...}{%
  \Word{sew}{v.}{缝合；缝制}%
}

\SentenceBlock[0:49:12]{One frequency, two waves per oscilloscope.}{每个示波器一个频率 两种脑波}{%
  \Word{oscilloscope}{n.}{示波器}%
}

\end{document}