\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S02E07: Chikhai Bardo}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip
\SentenceBlock[0:01:13]{Oh, my God. Spoiler alert, please.}{天啊 剧透了}{%
  \Word{Spoiler}{n.}{剧透}
}

\SentenceBlock[0:01:22]{All Quiet on the Western Blunt:}{西线无瘾士}{%
  \Word{Blunt}{n.}{钝器；大麻烟卷}
}

\SentenceBlock[0:01:25]{Drug Use by Enlisted Soldiers during World War I.}{一战士兵的毒品使用}{%
  \Word{Enlist}{v.}{应征入伍}
}

\SentenceBlock[0:01:31]{Kid's a genius. You should flunk every other child.}{这孩子是个天才 你应该让其他人都不及格}{%
  \Word{flunk}{v.}{不及格；让…不及格}
}

\SentenceBlock[0:03:54]{We'll need some equipment from downstairs. Are you clumsy?}{我们需要楼下的一些设备 你手脚灵活吗}{%
  \Word{clumsy}{adj.}{笨拙的}
}

\SentenceBlock[0:04:10]{but if you give one solitary thought to messing with my brother again,}{如果你哪怕有一丝一毫的念头 要再去搞我哥哥}{%
  \Word{solitary}{adj.}{单独的；唯一的}
}

\SentenceBlock[0:06:55]{Calisthenics?}{健身操}{%
  \Word{Calisthenics}{n.}{健美操；徒手健身}
}

\SentenceBlock[0:07:04]{If you were caught in a mudslide,}{如果你在泥石流期间被困}{%
  \Word{mudslide}{n.}{泥石流}
}

\SentenceBlock[0:07:06]{would you be more afraid of suffocating or drowning?}{你更担心窒息而亡还是溺亡}{%
  \Word{suffocate}{v.}{使窒息}
}

\SentenceBlock[0:14:21]{- What? How dare you. - Handsy.}{- 什么 怎么可以这么说 - 是毛手毛脚}{%
  \Word{Handsy}{adj.}{毛手毛脚的}
}

\SentenceBlock[0:15:34]{For you. That's 'cause you can scale walls like a gecko.}{对你来说是 因为你能像壁虎一样爬墙}{%
  \Word{gecko}{n.}{壁虎}
}

\SentenceBlock[0:15:43]{Boulders? Babe, come on. It was like the death zone of Everest.}{岩石 宝贝 拜托 那看起来就像珠穆朗玛峰的死亡区}{%
  \Word{boulder}{n.}{大圆石，巨石}
  \Word{Everest}{n.}{珠穆朗玛峰}
}

\SentenceBlock[0:15:56]{Hey, I belayed my first couloir in middle school.}{嘿 我第一次系上攀岩带是中学时}{%
  \Word{belay}{v.}{保护（登山用语）}
  \Word{couloir}{n.}{狭道，雪沟（登山术语）}
}

\SentenceBlock[0:16:04]{Outdoorsmanship courses through my veins.}{我体内流淌着户外探险的血}{%
  \Word{Outdoorsmanship}{n.}{野外生存技能}
}

\SentenceBlock[0:16:09]{- I scooted on my ass. - Are there photos of that?}{- 我是屁股蹭着慢慢下去 - 有照片吗}{%
  \Word{scoot}{v.}{迅速移动}
}

\SentenceBlock[0:16:16]{You and I will ramble together someday. The two of us.}{你我以后会一起探险 我们俩}{%
  \Word{ramble}{v.}{漫步；闲逛}
}

\SentenceBlock[0:18:42]{and verbally encourage her to forgo further suicide attempts.}{并用语言鼓励她放弃未来自杀的念头}{%
  \Word{forgo}{v.}{放弃}
}

\SentenceBlock[0:24:41]{Did you exit any of the rooms feeling despair?}{你在走出任何房间的时候有感觉绝望吗}{%
  \Word{despair}{n.}{绝望}
}

\SentenceBlock[0:24:46]{Fervor? Gaiety?}{狂喜 欢乐}{%
  \Word{fervor}{n.}{狂热；热情}
  \Word{gaiety}{n.}{欢乐；庆祝}
}

\SentenceBlock[0:29:12]{Chikhai bardo?}{临终中阴}{%
  \Word{Chikhai}{n.}{（藏传佛教术语）中阴初时}
  \Word{bardo}{n.}{（藏传佛教术语）中阴状态}
}

\SentenceBlock[0:29:18]{No, it's the same guy fighting himself, defeating his own psyche. Ego death.}{不 是同一个人 他的自我挣扎 击败自己的精神 自我之死}{%
  \Word{psyche}{n.}{心灵；精神}
}

\SentenceBlock[0:33:21]{an electric grouter.}{电动灌浆机}{%
  \Word{grouter}{n.}{灌浆工人；灌浆机}
}

\SentenceBlock[0:38:50]{Do you feel yourself gravitating towards one room or another?}{你感觉自己特别喜欢某一个房间吗}{%
  \Word{gravitate}{v.}{被吸引}
}

\SentenceBlock[0:41:26]{- It's charades. - That's gonna be, like, 20 minutes of it.}{- 就是打哑谜游戏 - 那就只是玩20分钟而已}{%
  \Word{charade}{n.}{你来比划我来猜（游戏）}
}

\end{document}