\documentclass[11pt,a4paper]{article}
\usepackage{aiwordbook}

\title{\Huge\bfseries Severance\\\Large S02E10: Cold Harbor}
\date{}
\author{}

\begin{document}

\maketitle
\bigskip
\SentenceBlock[0:04:07]{I sired others in the shadows.}{我还有很多私生子}{
    \Word{sire}{v.}{生育}
}
\SentenceBlock[0:05:28]{Your chip is only attuned to your floor.}{你的芯片只有你那一层的记忆}{
    \Word{attune}{v.}{使适应}
}
\SentenceBlock[0:09:04]{It's horrific what they've done to you.}{他们对你做的事是令人发指的}{
    \Word{horrific}{adj.}{可怕的}
}
\SentenceBlock[0:12:34]{It's a way to recouple memories so we can be one person.}{通过它 记忆重新连接 我们可以再次变成一个人}{
    \Word{recouple}{v.}{重新连接}
}
\SentenceBlock[0:13:29]{Like, my memories and yours, and my trauma and yours,}{我的记忆 你的记忆 我的创伤 你的创伤}{
    \Word{trauma}{n.}{创伤}
}
\SentenceBlock[0:14:33]{I mourned Gemma for two years.}{两年来 我都在哀悼珍玛}{
    \Word{mourn}{v.}{哀悼}
}
\SentenceBlock[0:18:46]{They're a doorway into the mind of your outie's wife, Gemma Scout.}{它们是进入珍玛斯科特大脑的通道 也就是你外面自己的妻子}{
    \Word{doorway}{n.}{通道}
}
\SentenceBlock[0:19:29]{Woe.}{悲哀}{
    \Word{woe}{n.}{悲哀}
}
\SentenceBlock[0:19:32]{Frolic.}{嬉笑}{
    \Word{frolic}{n.}{嬉戏}
}
\SentenceBlock[0:19:36]{Malice.}{恶意}{
    \Word{malice}{n.}{恶意}
}
\SentenceBlock[0:19:39]{Dread.}{恐惧}{
    \Word{dread}{n.}{恐惧}
}
\SentenceBlock[0:21:18]{There'll be no honeymoon ending for you and Helly R.}{你和赫莉R不会拥有好的结局}{
    \Word{honeymoon}{n.}{蜜月}
}
\SentenceBlock[0:21:39]{Then they'll discard you like a skin husk.}{然后他们会像对待废茧衣一样抛弃你}{
    \Word{husk}{n.}{外壳}
}
\SentenceBlock[0:25:12]{Goodly splendors await upon your victory. Love, Mr. Milchick.}{你的胜利将伴随着美好的辉煌 米尔奇克先生上}{
    \Word{splendor}{n.}{辉煌}
}
\SentenceBlock[0:26:06]{He said some cryptic shit about the fire of Kier being in me,}{他说了一些神神秘秘的话 什么在我身上看到基尔之火}{
    \Word{cryptic}{adj.}{神秘的}
}
\SentenceBlock[0:30:47]{and as I'm duly swamped,}{也由于我有多个要务在身}{
    \Word{duly}{adv.}{按时地；适当地}
    \Word{swamped}{adj.}{忙得不可开交}
}
\SentenceBlock[0:30:49]{I shall leave you to read it in solitude.}{我将让你独自阅读}{
    \Word{solitude}{n.}{孤独}
}
\SentenceBlock[0:31:36]{and your actions with her were deeply fucking indecorous.}{你对她做的举动纯属毫不知耻}{
    \Word{indecorous}{adj.}{不得体的}
}
\SentenceBlock[0:31:50]{She's perfect, and given our shared physiology, it tracks that you'd agree.}{她很完美 鉴于你我生理机能一样 你一定也同意}{
    \Word{physiology}{n.}{生理}
}
\SentenceBlock[0:32:16]{It stung.}{我挺受伤的}{
    \Word{sting}{v.}{刺痛}
}
\SentenceBlock[0:33:00]{Sincerest regards, Your outie.}{真诚敬上 你外面的自己}{
    \Word{sincere}{adj.}{真诚的}
}
\SentenceBlock[0:34:16]{The Equator?}{赤道}{
    \Word{equator}{n.}{赤道}
}
\SentenceBlock[0:37:36]{you have drawn my grand agendum nearer to fulfillment,}{我的宏伟计划更接近实现}{
    \Word{agendum}{n.}{议题}
}
\SentenceBlock[0:37:52]{Revel now in the fruit of your labors,}{请享受你兢兢业业的成果}{
    \Word{revel}{v.}{尽情享受}
}
\SentenceBlock[0:37:57]{and hail your earthbound steward,}{并致敬你在尘世的管理者}{
    \Word{earthbound}{adj.}{尘世的}
}
\SentenceBlock[0:38:36]{Probity?}{诚实}{
    \Word{probity}{n.}{正直}
}
\SentenceBlock[0:38:44]{Well, it's truly special to host a man so illustrious,}{我实感荣幸 能招待如此杰出}{
    \Word{illustrious}{adj.}{杰出的}
}
\SentenceBlock[0:38:50]{so sapient, so magnanimous--}{如此睿智 如此宽宏...}{
    \Word{sapient}{adj.}{睿智的}
    \Word{magnanimous}{adj.}{宽宏大量的}
}
\SentenceBlock[0:39:13]{It's an honor to receive your barbs, Mr. Eagan.}{很荣幸能被您打趣 伊根先生}{
    \Word{barb}{n.}{讽刺}
}
\SentenceBlock[0:39:18]{The legacy you've left behind is truly and irrefutably larger than life.}{您留给后世的传承 真真正正 无可置疑地超越尘世}{
    \Word{irrefutably}{adv.}{无可辩驳地}
}
\SentenceBlock[0:40:07]{may I introduce Choreography and Merriment!}{有请舞蹈和娱乐部}{
    \Word{choreography}{n.}{舞蹈编排}
    \Word{merriment}{n.}{欢乐}
}
\SentenceBlock[0:41:53]{The efficacy test will begin shortly.}{效用测试将很快开始}{
    \Word{efficacy}{n.}{功效}
}
\SentenceBlock[0:42:10]{...with the Ballad of Ambrose}{请欣赏安布罗斯}{
    \Word{ballad}{n.}{民谣}
}
\SentenceBlock[0:49:15]{Has it verve?}{有活力吗}{
    \Word{verve}{n.}{活力}
}
\SentenceBlock[0:49:22]{Wiles?}{狡黠}{
    \Word{wile}{n.}{诡计}
}
\SentenceBlock[0:49:26]{The most of its flock.}{是它这一群中最狡黠的}{
    \Word{flock}{n.}{群体}
}
\SentenceBlock[0:49:54]{This beast will be entombed with a cherished woman,}{这只野兽将与一位可贵的女人埋葬在一起}{
    \Word{entomb}{v.}{埋葬}
}
\SentenceBlock[0:59:36]{Those instruments are property of Choreography and Merriment.}{这是舞蹈和娱乐部的乐器}{
    \Word{choreography}{n.}{舞蹈编排}
    \Word{merriment}{n.}{欢乐}
}

\end{document}